### 2024-02-12 paper/paper.qmd
Updated paper qmd
Updated quarto file

---
title: "School Closures during the COVID-19 Pandemic [fix title]"
author: "Krishiv Jain, Julia Kim, Abbass Sleiman"
thanks: "Code and data are available at: https://github.com/AbbassSleiman/COVID-19; Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1447/index?step=1 (temporary link)"
date: "February 15, 2024"
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1.2in
    abstract: "...."
    number-sections: true
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes
nocite: '@*'
bibliography: references.bib
---

```{r setup}
#| echo: false
#| message: false
#| warning: false
library(here) 
library(tidyverse)
library(knitr)
library(janitor)
library(kableExtra)
library(DiagrammeR)
```

# Introduction

On March 11, 2020, the World Health Organisation (WHO) declared the COVID-19 outbreak a global pandemic, urging all countries take action in detecting infection and limiting spread [@WHO]. Shortly after the announcement, many countries began to implement measures to reduce COVID-19 contagion and transmission. In spite of the general effectiveness of such measures in saving lives [@effectiveness], they imposed severe disruptions to the lives of children and adolescents. These included delayed healthcare provision, decreased contact with peers and relatives, routine modification, and diminished sense of well-being [@impact_covid]. Among the most significant disruptions, and the topic of this paper, was the closure of schools in favour of virtual learning.

Before the pandemic, there was a modestly-sized economic literature on the impact of school closures on learning, with data generally drawn from short-term episodes such as teacher strikes [@Jack_Oster_2023]. It was widely observed that time outside of school caused loss of literacy and numeracy skills, more so among the marginalised, and widened student achievement gaps [@pastresearch]. These findings are certainly suggestive of the possible effects of COVID-19 school closures on student learning. However, as the pandemic's disruptions typically surpassed previous episodes of school closures, the scope for inference from earlier works is limited [@Jack_Oster_2023]. A paper by Jack and Oster, "COVID-19, School Closures, and Outcomes" [-@Jack_Oster_2023] published in American Economic Association's *Journal of Economic Perspectives*, sought to address this gap, by focusing on emerging short-term evidence of the impact of COVID-19 school closures on academic performance.

In studying the scope of school closures across the United States, they reported that the country experienced, on average, one of the highest number of days of school closed between January 2020 to December 2021 worldwide [@Jack_Oster_2023]. Jack and Oster [-@Jack_Oster_2023] also found that the duration of school closures varies with local demographic characteristics, with more disadvantaged districts facing more prolonged closures. The study population was grade 3 to 8 students across 11 major American states, being Colorado (CO), Connecticut (CT), Massachusetts (MA), Minnesota (MN), Mississippi (MI), Ohio (OH), Rhode Island (RI), Virginia (VA), Wisconsin (WI), West Virginia (WV) and Wyoming (WY). The estimand was the impact of COVID-19 closures on academic performance. They found considerable declines in test scores during the 2020-2021 academic year, with declines larger in school districts with less in-person instruction [@Jack_Oster_2023]. On average, pass rates fell from 2019 to 2021 by an average of 12.8 percentage points in mathematics and 6.8 in English Language Arts (ELA) [@Jack_Oster_2023].

Our paper seeks to assess the robustness and generalisability of Jack and Oster's work. We successfully replicate and extend three of its major research claims:

(1) With respect to the world, the United States faced second highest number of days of school closed between January 2020 to December 2021.

(2) Access to in-person education was unequal across various demographic characteristics, being significantly correlated with an area's ethnic composition, broadband usage and unemployment rates. In general, more disadvantaged districts spent more of the school year in virtual schooling.

(3) School closures contributed significantly to the decline in students' pass rates in mathematics and ELA in the 2020-2021 school year. Changes in ELA scores were smaller than mathematics scores, but significantly larger in districts with larger populations of students who are Black, Hispanic, English Language Learners (ELL) or eligible for free and reduced price lunch (FRPL).

We also apply a Dutch-facing lens, examining the extent of school closures and the impact on student learning, in a country whose pandemic circumstances were regarded as most favourable for students [@engzell]. In spite of a short lockdown, equitable school funding and high degree of technological preparedness, we discuss how Dutch students still suffered a loss of the equivalent of one-fifth of a year of education and how the effects were distributed unequally according to student demographics. Throughout, our investigation is conducted using the open-source statistical programming language `R` [@R], with functionalities from `tidyverse` [@tidyverse], `janitor` [@janitor], `knitr` [@knitr], `here` [@here], `kableExtra` [@kableExtra] and `DiagrammeR` [@DiagrammeR].

This paper is structured, as follows. In Section 2, we address the sources of the datasets in the original paper, the methodologies used to collect them, and highlight key features. In Section 3, we conduct a replication of the original study to confirm its internal validity and to design scientific figures that permit a more effective visualisation of the data. In Section 4, we assess the degree of the external validity of these findings, by applying them to countries in sub-Saharan Africa. We compliment this discussion by addressing ethical implications and limitations of the original research, and by giving directions for future analysis.

# Data

## Source

The original paper used for replication is Jack and Oster's "COVID-19, School Closures, and Outcomes" [-@Jack_Oster_2023], published in the American Economic Association's *Journal of Economic Perspectives*. To investigate the degree of school closures in the United States, and their attendant effects on children, they pose the following three questions:

(1) Relative to the global picture, what is the extent of school closures in the United States?

(2) What are the demographic patterns underlying these closures? Namely, how are the number of days of school closed correlated with ethnicity, unemployment rate and political leanings at the district- or county-level?

(3) What is the short-term impact of school closures on student academic performance and learning inequalities?

## Methodology

-   address collection / measurement
-   For Krishiv: for research question #1, we actually want data about the rest of the world. We should supplement the data given in the package to see where exactly the United States falls with respect to the rest of the world in terms of \# of days closed, rather than
-   For Abbass: for research question #2, we want to show that significant variation exists in the average number of days spent in virtual school by demographics, specifically, by race, unemployment rates, and political leanings of the area. Ignore school mode with little variation.
-   For Abbass: please extend the pass rate figure by incorporating data from the replication package of the other paper, in order to stratify by race, percent in-person, FRPL and ELL (for example). You can see the figure here: <https://www.aeaweb.org/research/charts/pandemic-schooling-test-scores-us> Ignore state, probably

## Features

-   rigorously define variables in a neat way
-   e.g., define "school closures" rigorously (e.g., a closure is identified as Tracker score of 2 or 3... what is a Tracker score?)

# Results

-   again, the 2023 student paper is very good as a reference

# Discussion

## Findings

The analysis by Jack and Oster seeks to define the scope of COVID-19 school closures in the United States with respect to the global picture, and explore the correlation between the number of days of school closed with various demographic characteristics of eleven of its major states. The authors also compare the average change in pass rates in mathematics and ELA with the number of days of in-person schooling in Spring 2021 versus Spring 2018-2019. Our paper has successfully replicated and extended an important part of three of their major findings:

(1) Between January 2020 and December 2021, the United States experienced the second-highest number of days of school closed worldwide, with an average of 667 days. In fact, it falls second only to Azerjiban, which recorded an average of 669 days.
(2) Access to in-person education was unequal by demographic characteristics. More disadvantaged districts, *i.e.*, those with higher proportions of racial minorities, lower broadband usage, and lower employment rate, spent more days in virtual schooling.
(3) During the 2020-2021 school year, students' pass rates on standardised assessments declined by 12.8 percentage points in mathematics and 6.8 in ELA. Declines were more severe in more disadvantaged districts, *i.e.*, those with higher proportions of racial minorities, English language learners, and lower socioeconomic status.

As noted by Jack and Oster [-@Jack_Oster_2023], it can be seen that the equity impacts are two-fold. First, schools (and students) with lower resources are less likely to have access to in-person instruction. Second, for such groups, the consequences of a lack of in-person instruction are more severe. This may be due to a smaller investment by such schools in effective remote learning programs or due to the challenges disadvantages students face at home, such as less reliable Internet connection or fewer community resources. Accordingly, while COVID-19 school closures imposed learning loss costs on students as a whole, they affected most negatively those who were already most vulnerable. This exacerbates the already large inequality gap.

Having replicated their work, we now turn to examine its relevance to the Netherlands. We hope to gain insights into the extent of school closures in the Netherlands and its effect on student performance, with an especial focus on students from disadvantaged homes.

## Relevance to the Netherlands: a Case Study 
Efforts have been made worldwide to study the impacts of school closures on student learning, typically revealing significant test-score losses [@Jack_Oster_2023]. The Netherlands is interesting as a "best-case" scenario for students, with a short lockdown of 8 weeks, equitable school funding and world-leading rates of broadband access [@engzell]. According to the Organisation for Economic Cooperation and Development (OECD) [-@OECD], the Dutch government also entered the pandemic with strong public finances, extending generous support measures for individuals and families. The Netherlands also scores close to the OECD average in school reading and places among its top performers in mathematics [@schleicher2018pisa]. For these reasons, the Netherlands may likely provide a lower bound on student learning loss elsewhere in Europe and the world [@engzell].

Between January 2020 and December 2021, the Netherlands faced 55 days of school closed [@hatch], considerably shorter than the global average (362 days) and the United States (677 days). Key to our discussion is that the Dutch school system provides compulsory standardised assessments in mathematics, spelling and reading twice a year: halfway into to the school year in January and at the end of the school year in June. In 2020, these testing dates occurred just before and after nationwide school closures. Access to biannual test scores of 15% ($n \approx 350,000$) Dutch students between grades 4 to 7 from 2017 to 2020, published by the The Student Monitoring System (LVS), thus provides a natural benchmark against which to assess learning loss. To study the data, Engzell, Frey, and Verhagen [-@engzell] transform these test scores into percentiles by imposing a uniform distribution separately by subject, grade and testing occasion for each of the years 2017 to 2020. In adjusting for sample composition, their results reveal a learning loss of about 3.1, 3.0 and 3.3 percentile points in mathematics, spelling and reading. The effect is equivalent to a loss of one-fifth of a school year, the same period that Dutch schools remained closed. By contrast, declines in test scores of American students between grades 3 to 8 are equivalent to a loss of about one year of learning [@PBS].

The LVS also collects data on student demographics and school characteristics, as part of the national system of weighted student funding [@sanoma2024lvs]. In comparing this data with test scores, Engzell, Frey, and Verhagen [-@engzell] find learning losses to be up to 60% larger among students from less-educated homes, confirming the unequal costs of the pandemic on children. Moreover, they report learning losses vary considerably by school, with some schools seeing a loss of 10 percentiles or more, and some recording no loss or small gains. However, they discover a concentration of these losses in schools with a high proportion students who are socioeconomically disadvantaged or of non-Western immigrant background. These patterns are consistent with those observed in the United States, where learning loss was also more pronounced among students of more vulnerable groups. Whether in the Netherlands or in the United States, school closures appear to have caused socioeconomic gaps to widen.

Despite favourable conditions, the Netherlands appears to have made little to no progress in learning from home. However, the impact on student learning appears to be milder than that in the United States, with Dutch students losing the equivalent of one-fifth rather than a full year of learning. These findings by Engzell, Frey, and Verhagen [-@engzell] suggest learning losses even larger in countries with weaker infrastructure or longer lockdowns. Efforts should be made to investigate the impact of school closures on learning outcomes in these countries. Moreover, to remediate consequences on student learning, social investment strategies should be designed and implemented to enhance resilience and equity in education.

## Ethical Concerns

There are ethical concerns with the collection of race, employment, socioeconomic and COVID-19 data in surveys, including data sensitivity and security. Collecting personally-identifying information (PII) may rouse feelings of anxiety and distrust, and raise important concerns about privacy and confidentiality [@OHRC2009]. Individuals from vulnerable populations are particularly susceptible to such feelings of distrust in researchers [@corbiesmith]: anxiety about the research protocol, stigma, fear of disclosure, historical exploitation may be some reasons motivating a hesitancy to participate.

Moreover, stratifying test assessment scores by district-level race, ELL and FRPL shares may be problematic. The underperformance of vulnerable populations in relation to more privileged populations may reinforce discriminatory notions about their intellectual ability. These notions are harmful, having been found to impair even further the academic performance of minority groups [@steele]. Indeed, Steele and Aronson [-@steele] have found that, when an individual is conscious of the negative stereotypes of their group, they face *stereotype threat*, becoming fearful of confirming or being judged by those stereotypes through their actions or performance. This may lead to increased self-doubt and anxiety, and thus poorer performance on assessments.

## Accounting for Bias

Perhaps the most important threat to the validity of the results is the "endogeneity in schooling mode": this is the concern that districts with more days of school closed were more affected by other pandemic-related stressors [@Jack2]. For instance, more school closures in an area may arise in response to higher COVID-19 rates, and higher COVID-19 rates may in turn worsen the health and, thus, academic performance of students. The directed acyclic graph in Figure \ref{fig-dag-quarto} demonstrates this phenomenon, whereby COVID-19 rates serve as a confounding variable, creating a possibly spurious relationship between school closures and academic performance. However, the number of school closures were shown to have very low correlation with COVID-19 rates [@Jack_Oster_2023]. This shows that COVID-19 rates may not be as significant of a confounding variable a initially presumed.

```{dot}
//| label: fig-dag-quarto
//| fig-cap: "COVID-19 rates as a confounder, affecting the relationship between school closures and academic performance."
//| fig-width: 4
# code referenced from https://tellingstorieswithdata.com/04-writing_research.html 
digraph D {

  node [shape=plaintext, fontname = "Latin Modern Roman"];

  a [label = "School Closures"];
  b [label = "Academic Performance"];
  c [label = "COVID-19 Rates"];

  { rank=same a b};

  a->b;
  c->{a, b};
}
```

It is also possible that other types of lockdowns --- such as the closure of counselling services or after-school activities --- might have impacted student learning. This considerable difficulty of separating the effect of school closures from other pandemic-related stressors may bias the results and so affect their validity. One way in which we have helped disentangle these factors is to stratify the test assessments data by race, ELL and FRPL shares per district. By means of this "restriction" technique, we could compare test scores between more homogeneous demographic subgroups and better control for racial and demographic differences that may have impacted student learning outcomes.

Important sources of bias may have also arisen from the demographic datasets obtained from the US Department of Education's Common Core of Data [@irwin2022report], the US Bureau of Labour Statistics [@bls2021county] and the US Broadband Usage Percentages dataset [@kahan2020usbroadband]. In particular, there are various errors that may exist in census data, collected to determine district-level race shares and county-level unemployment rates across the United States. These include *coverage errors*, when a respondent is missed or counted more than once, *non-response errors*, when some information about a respondent is missing, *response errors*, where a question is misunderstood or misreported by a respondent and *processing errors*, when data is incorrectly processed [@censusErrors]. On the other hand, the US Broadband Usage Percentages dataset determines broadband usage by combining data from Microsoft services [@kahan2020usbroadband]. In failing to account for other popular forms of internet services, such those provided by Google, Facebook, Amazon and Apple, this dataset may skew the representation of broadband usage patterns in the United States.

## Limitations

Being a reproduction, much of the limitations of our analysis arise from those in the original work of Jack and Oster [@Jack_Oster_2023]. In particular, the correlations of school closures to local demographic variables, while insightful, are not comprehensive. For instance, it would have been beneficial to determine the average number of days spent in virtual school, weighted by district enrollment, and the share of the school population that is of other ethnicities --- namely, Whites, Asians and Native Americans --- so that comparisons can be made across all major ethnic classes. Other demographic variables might include the share of students experiencing homelessness, who have limited English proficiency or who are of low socioeconomic status. Determining such correlations would more rigorously test the claim that social inequity existed in the distribution of school closures.

What is more, Jack et al.'s [-@Jack2] standardised assessments data excludes information about the corresponding broadband usage and unemployment rates by district. It instead includes data of the corresponding shares of ELL and FRPL students by district. This discrepancy prevents us from telling a full story as to how the pass rates of schools located in districts with lower broadband usage and employment rates, known to face more days of school closed than the national average, were affected. We also question whether the shares of FRPL students are a good estimator of the shares of students with low socioeconomic status. Though FRPL enrollment are widely used in education research as an indicator of student poverty, there is emerging literature that it serves as a poor proxy for poverty [@Fazlul2023]. In fact, using multiple data sources external to the American school system, Fazlul et al. [-@Fazlul2023] show that FRPL rates greatly exceed what would be expected from stated income thresholds for program participation by 35 to 50%. This suggests that the shares of FRPL students per district may not be the most optimal estimator of student poverty, and that more insightful conclusions could have been obtained in examining instead, for instance, the shares of students in low-income households per district.

Lastly, the state-level assessment data is obtained from only eleven states of the United States, for which district-level data is available. This dataset may not be representative of the academic performance of American students as a whole for two reasons. First, state-standardised assessments remain controversial, with critics questioning whether they accurate indicate academic ability [@yang]. Certainly, they cannot capture the ways in which students learned that were not directly given in the assessment. Second, the sample of eleven states may be too small to be generalisable. Indeed, Parolin and Kee [-@parolin] showed that wide geographic disparities existed in school closures across the country: those concentrated on the West Coast faced declines of \>75% in-person visits to schools, whereas those in the Midwest faced declines of \<25%. Both of these factors put into question the validity and generalisability of the state-assessment data, and could present a valuable direction for future work.

## Future Research

Reports of poor mental health (MH) in youth have been on the rise in the United States for the past decade [@nlm2022]. The COVID-19 pandemic appears to have exacerbated this trend, in significantly disrupting the lives of youth in one of their most critical periods of psycho-social development [@nlm2022]. However, the evidence on the impact of school closures --- as opposed to other pandemic-related stressors --- on student MH in the short- and long-term remains mixed, limited or else unknown [@Jack_Oster_2023]. For instance, Bacher-Hicks et al. [-@bacherhicks] used internet search data to track in-person bullying and cyberbullying patterns as COVID-19 shifted to remote learning in Spring 2020. Surprisingly, they reported that *both* forms of bullying dropped by 30-35%, citing transitions to virtual learning to be likely a major explanation for these trends. In contrast, Cingel et al. [-@Cingel] used online survey data, in which over 1,000 American adolescents aged 14-16 reported their classroom learning experiences and MH symptoms during the 2020-2021 school year. In this data, virtual as opposed to in-person learning was associated with reduced MH, with those online reporting less satisfaction and social connection than those in-person. In particular, problems were particularly pronounced for students identifying as transgender or gender non-conforming.

Much more research remains to understand the full impacts of the pandemic, and of school closures, in particular, on youth MH. Whilst collecting data on MH, and differentiating between the effects of school closures and other pandemic stressors on MH, are notoriously difficult, these issues remain crucial to investigate. Findings of future search will help guide policy to remediate the consequences and provide more tailored support for affected youth that promote their well-being.

\clearpage

# References {.unnumbered}

### 2024-02-13 scripts/00-simulate_data.R
Add files via upload

@@ -1,19 +1,59 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates various data sets 
+# Author: Krishiv Jain, Julia Kim, Abbass Sleiman
+# Date: 12 February 2024
+# Contact: 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
 
 #### Workspace setup ####
 library(tidyverse)
 # [...UPDATE THIS...]
 
-#### Simulate data ####
-# [...ADD CODE HERE...]
+#### SIMULATE DATA ####
+
+set.seed(555) #random seed
+
+## DATASET 1 ##
+
+
+
+
+
+
+## DATASET 2 - local characteristics for districts ##
+
+simulated_data2 <-  
+  tibble(
+    state = paste("State", rep(1:50, each = 5)),
+    district = paste("District", rep(1:5, times = 50)),    
+    virtual_days = round(runif(250, min = 0, max = 180)),
+    white_students = round(runif(250, min = 0, max = 5000)),
+    black_students = round(runif(250, min = 0, max = 5000)), 
+    broadband_usage = runif(250, min = 0, max = 1))
+
+### TESTS ###
+
+##Check the minimum number is equal, or greater than, 0 ##
+#Based on: https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html#simulate
+simulated_data2$virtual_days |> min() >= 0
+simulated_data2$white_students |> min() >= 0
+simulated_data2$black_students |> min() >= 0
+simulated_data2$broadband_usage |> min() >= 0
+
+##Check the class of the column is numeric##
+simulated_data2$virtual_days |> class() == "numeric"
+simulated_data2$white_students |> class() == "numeric"
+simulated_data2$black_students |> class() == "numeric"
+simulated_data2$broadband_usage |> class() == "numeric"
+
+## Check that first and third columns only have whole numbers ##
+#Based on: https://stackoverflow.com/q/3476782/23271634
+is.wholenumber <- function(x, tol = .Machine$double.eps^0.5) abs(x - round(x)) < tol
[…]

### 2024-02-13 scripts/01-download_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
+# Author: Krishiv Jain, Julia Kim, Abbass Sleiman
+# Date: 12 February 2024
 # Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
@@ -9,18 +9,49 @@
 
 
 #### Workspace setup ####
-library(opendatatoronto)
+library(haven)
 library(tidyverse)
-# [...UPDATE THIS...]
-
-#### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
 
 
+#### DATASETS FOR FIGURE 2 ####
 
-#### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+## Download Data sets ##
+
+zip_file <- "data/raw_data/output_data.csv.zip"
+# Unzip the file
+data <- unzip(zip_file)
+race_data <- read_csv(data[1], col_types = cols())
+
+broadband_data <-
+  read_csv(
+    file = "data/raw_data/broadband_data_2020October.csv",
+    show_col_types = FALSE
+  )
+
+shares_data <-
+  read_csv(
+    file = "data/raw_data/District_Overall_Shares.csv",
+    show_col_types = FALSE
+  )
+
+county_district_data <-
+  read_dta(
+    file = "data/raw_data/nces_district_directory_2018.dta",
+  )
+
+## Save Data sets ##
+
+write_csv(race_data, "data/analysis_data/race_data.csv")
+write_csv(broadband_data, "data/analysis_data/broadband_data.csv")
+write_csv(shares_data, "data/analysis_data/shares_data.csv")
+write_csv(county_district_data, "data/analysis_data/county_district_data.csv")
+
+#### DATASETS FOR FIGURE 3 ####
+
+## Download Data ##
+test_scores_data <- read_dta(here::here("data/raw_data/scores_lm_demographics.dta"))
+
+## Save data ##
+write_csv(test_scores_data, "data/raw_data/scores_lm_demographics.csv") #ANALYSIS_DATA?
 
          

### 2024-02-13 scripts/02-data_cleaning.R

@@ -9,36 +9,57 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(data.table)
 
-#### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+#### Clean region data ####
+raw_region_data <- read_csv("data/raw_data/region_data.csv")
+country_region_data <- read_csv("data/raw_data/country_region.csv")
 
-cleaned_data <-
-  raw_data |>
+cleaned_region_data <-
+  raw_region_data |>
   janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
+  rename(
+    covid_score = c1m_school_closing 
   ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
+  mutate(date = ymd(date)) |>
+  filter(year(date) != 2022) |>
+  select(
+    country_name,
+    region_name,
+    date,
+    covid_score
   ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+  mutate(
+    country_name = gsub("Faeroe Islands", "Faroe Islands", country_name)
+  )
+
+cleaned_region_data <- as.data.table(cleaned_region_data)
+country_region_data <- as.data.table(country_region_data)
+
+# Set keys for merging
+setkey(cleaned_region_data, country_name)
+setkey(country_region_data, country_name)
+
+# Perform left join
+cleaned_region_data <- country_region_data[cleaned_region_data, on = "country_name", nomatch = 0]
+
+cleaned_region_data <- as.data.frame(cleaned_region_data)
+
+
+#### Clean test score data ####
[…]

### 2024-02-13 scripts/99-replications.R

@@ -1,19 +1,149 @@
 #### Preamble ####
 # Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Author: Krishiv Jain, Julia Kim, Abbass Sleiman
+# Date: 12 February 2024 
+# Contact: 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
 
-#### Load data ####
-# [...ADD CODE HERE...]
+#### FIGURE 1 ####
 
+data <- read_excel("/cloud/project/data/raw_data/Tracker-of-national-education-response-to-COVID-19_-21May2020.xlsx", 
+                   sheet = "Continuity of Learning")
 
+master_data <- data[30:36, c(1) ]
 
+master_data <- data[30:36, c(1, 3) ]
+master_data$...3 <- as.numeric(master_data$...3) * 100
+master_data$new_column <- "Digital Platforms"
+
+tv_data <- data[95:101, c(1, 3)]
+tv_data$...3 <- as.numeric(tv_data$...3) * 100
+tv_data$new_column <- "TV Programming"
+master_data <- rbind(master_data, tv_data)
+
+radio_data <- data[107:113, c(1, 3)]
+radio_data$...3 <- as.numeric(radio_data$...3) * 100
+radio_data$new_column <- "Radio Programming"
+master_data <- rbind(master_data, radio_data)
+
+printed_data <- data[119:125, c(1, 3)]
+printed_data$...3 <- as.numeric(printed_data$...3) * 100
+printed_data$new_column <- "Printed take-home resouces"
+master_data <- rbind(master_data, printed_data)
+
+one_data <- data[17:23, c(1, 3)]
+one_data$...3 <- (1 - as.numeric(one_data$...3)) * 100
+one_data$new_column <- "Any/at least one method"
+master_data <- rbind(master_data, one_data)
+
+colnames(master_data) <- c("Region", 
+                           "Percentage", 
+                           "Thing")
+
[…]

### 2024-02-13 paper/paper.qmd
Update paper.qmd

@@
 ---
-title: "School Closures during the COVID-19 Pandemic [fix title]"
+title: "Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students: A replication analysis using data from the United States and a case study on the Netherlands"
 author: "Krishiv Jain, Julia Kim, Abbass Sleiman"
-thanks: "Code and data are available at: https://github.com/AbbassSleiman/COVID-19; Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1447/index?step=1 (temporary link)"
+thanks: "Code and data are available at: https://github.com/AbbassSleiman/COVID19-US-School-Closures; Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1616/index?step=0"
 date: "February 15, 2024"
@@
     geometry: margin = 1.2in
-    abstract: "...."
+    abstract: "School closures due to the COVID-19 pandemic have raised significant concerns about the consequences on student learning and achievement gaps.
+This paper replicates a data analysis of the scope of school closures in the United States in the 2020-2021 school year, the inequitable distribution of such closures by demographic characteristics and the resultant declines in pass rates on standardised tests in mathematics and English Language Arts (ELA) of students in grades 3-8 across 11 states.
+We apply secondary research regarding the scope of school closures in the Netherlands in same year and the declines in national examination scores in reading, spelling and mathematics of Dutch students in grades 4-7.
+Although the Netherlands is regarded as 'best-case' scenario, with a short lockdown, equitable school funding, and high degree of technological preparedness, we find that Dutch students still experienced a significant learning loss, equivalent to one-fifth of that of the United States, with a disproportionate impact on vulnerable students.
+These findings suggest that COVID-19 school closures imposed significant costs of learning loss and widened inequality gaps in the United States and the Netherlands, with impacts likely larger in countries disenfranchised by weaker infrastructure or longer closures."
     number-sections: true
@@
 
-(1) With respect to the world, the United States faced second highest number of days of school closed between January 2020 to December 2021.
+(1) With respect to the world, the United States faced second highest number of days of school closed between January 2020 to December 2021, with a mean number of days of 667.
 
-(2) Access to in-person education was unequal across various demographic characteristics, being significantly correlated with an area's ethnic composition, broadband usage and unemployment rates.
+(2) Access to in-person education was unequal across various demographic characteristics, being significantly correlated with an area's ethnic composition and broadband usage.
 In general, more disadvantaged districts spent more of the school year in virtual schooling.
@@
 In Section 2, we address the sources of the datasets in the original paper, the methodologies used to collect them, and highlight key features.
-In Section 3, we conduct a replication of the original study to confirm its internal validity and to design scientific figures that permit a more effective visualisation of the data.
-In Section 4, we assess the degree of the external validity of these findings, by applying them to countries in sub-Saharan Africa.
+In Section 3, we conduct a replication of the original study to confirm the robustness of its findings and to design scientific figures that permit a more effective data visualisation.
+In Section 4, we assess the relevance of these findings to the Netherlands.
 We compliment this discussion by addressing ethical implications and limitations of the original research, and by giving directions for future analysis.
@@
 
-The analysis by Jack and Oster seeks to define the scope of COVID-19 school closures in the United States with respect to the global picture, and explore the correlation between the number of days of school closed with various demographic characteristics of eleven of its major states.
+The analysis by Jack and Oster seeks to define the scope of COVID-19 school closures in the United States with respect to the global picture, and explore the correlation between the number of days of school closed with various demographic characteristics of 11 of its major states.
 The authors also compare the average change in pass rates in mathematics and ELA with the number of days of in-person schooling in Spring 2021 versus Spring 2018-2019.
@@
 (2) Access to in-person education was unequal by demographic characteristics.
-More disadvantaged districts, *i.e.*, those with higher proportions of racial minorities, lower broadband usage, and lower employment rate, spent more days in virtual schooling.
+More disadvantaged districts, *i.e.*, those with higher proportions of racial minorities and lower broadband usage spent more days in virtual schooling.
 (3) During the 2020-2021 school year, students' pass rates on standardised assessments declined by 12.8 percentage points in mathematics and 6.8 in ELA.
-Declines were more severe in more disadvantaged districts, *i.e.*, those with higher proportions of racial minorities, English language learners, and lower socioeconomic status.
+Declines were more severe in more disadvantaged districts, *i.e.*, those with higher proportions of racial minorities, ELL and FRPL students.
 
@@
 
-Between January 2020 and December 2021, the Netherlands faced 55 days of school closed [@hatch], considerably shorter than the global average (362 days) and the United States (677 days).
+Between January 2020 and December 2021, the Netherlands faced 55 days of school closed, considerably shorter than the global average (362 days) and the United States (677 days) [@Jack_Oster_2023].
 Key to our discussion is that the Dutch school system provides compulsory standardised assessments in mathematics, spelling and reading twice a year: halfway into to the school year in January and at the end of the school year in June.
 In 2020, these testing dates occurred just before and after nationwide school closures.
-Access to biannual test scores of 15% ($n \approx 350,000$) Dutch students between grades 4 to 7 from 2017 to 2020, published by the The Student Monitoring System (LVS), thus provides a natural benchmark against which to assess learning loss.
-To study the data, Engzell, Frey, and Verhagen [-@engzell] transform these test scores into percentiles by imposing a uniform distribution separately by subject, grade and testing occasion for each of the years 2017 to 2020.
-In adjusting for sample composition, their results reveal a learning loss of about 3.1, 3.0 and 3.3 percentile points in mathematics, spelling and reading.
-The effect is equivalent to a loss of one-fifth of a school year, the same period that Dutch schools remained closed.
-By contrast, declines in test scores of American students between grades 3 to 8 are equivalent to a loss of about one year of learning [@PBS].
+Access to biannual test scores of 15% ($n \approx 350,000$) Dutch students between grades 4 to 7 from 2017 to 2020, published by the Student Monitoring System (LVS), thus provides a natural benchmark against which to assess learning loss.
+To study the data, Engzell, Frey, and Verhagen [-@engzell] transformed these test scores into percentiles by imposing a uniform distribution separately by subject, grade and testing occasion for each of the years 2017 to 2020.
+In adjusting for sample composition, their results revealed a learning loss of about 3.1, 3.0 and 3.3 percentile points in mathematics, spelling and reading, respectively.
+The effect was equivalent to a loss of one-fifth of a school year, the same period that Dutch schools remained closed.
+By contrast, declines in test scores of American students between grades 3 to 8 were equivalent to a loss of about one year of learning [@PBS].
 
 The LVS also collects data on student demographics and school characteristics, as part of the national system of weighted student funding [@sanoma2024lvs].
-In comparing this data with test scores, Engzell, Frey, and Verhagen [-@engzell] find learning losses to be up to 60% larger among students from less-educated homes, confirming the unequal costs of the pandemic on children.
+In comparing this data with test scores, Engzell, Frey, and Verhagen [-@engzell] found learning losses to be up to 60% larger among students from less-educated homes, confirming the unequal costs of the pandemic on children.
 Moreover, they report learning losses vary considerably by school, with some schools seeing a loss of 10 percentiles or more, and some recording no loss or small gains.
-However, they discover a concentration of these losses in schools with a high proportion students who are socioeconomically disadvantaged or of non-Western immigrant background.
+However, they discovered a concentration of these losses in schools with a high proportion students who are socioeconomically disadvantaged or of non-Western immigrant background.
 These patterns are consistent with those observed in the United States, where learning loss was also more pronounced among students of more vulnerable groups.
@@
 
-Despite favourable conditions, the Netherlands appears to have made little to no progress in learning from home.
+In short, despite favourable conditions, the Netherlands appeared to have made little to no progress in learning from home.
 However, the impact on student learning appears to be milder than that in the United States, with Dutch students losing the equivalent of one-fifth rather than a full year of learning.
@@
 
-There are ethical concerns with the collection of race, employment, socioeconomic and COVID-19 data in surveys, including data sensitivity and security.
+There are ethical concerns with the collection of data on racial identity, socioeconomic status and COVID-19 cases in surveys, including data sensitivity and security.
 Collecting personally-identifying information (PII) may rouse feelings of anxiety and distrust, and raise important concerns about privacy and confidentiality [@OHRC2009].
@@
 However, the number of school closures were shown to have very low correlation with COVID-19 rates [@Jack_Oster_2023].
-This shows that COVID-19 rates may not be as significant of a confounding variable a initially presumed.
+This shows that COVID-19 rates may not be as significant of a confounding variable as initially presumed.
 
@@
 Important sources of bias may have also arisen from the demographic datasets obtained from the US Department of Education's Common Core of Data [@irwin2022report], the US Bureau of Labour Statistics [@bls2021county] and the US Broadband Usage Percentages dataset [@kahan2020usbroadband].
-In particular, there are various errors that may exist in census data, collected to determine district-level race shares and county-level unemployment rates across the United States.
+In particular, there are various errors that may exist in census data, collected to determine district-level race shares across the United States.
 These include *coverage errors*, when a respondent is missed or counted more than once, *non-response errors*, when some information about a respondent is missing, *response errors*, where a question is misunderstood or misreported by a respondent and *processing errors*, when data is incorrectly processed [@censusErrors].
@@
 In particular, the correlations of school closures to local demographic variables, while insightful, are not comprehensive.
-For instance, it would have been beneficial to determine the average number of days spent in virtual school, weighted by district enrollment, and the share of the school population that is of other ethnicities --- namely, Whites, Asians and Native Americans --- so that comparisons can be made across all major ethnic classes.
+For instance, it would have been beneficial to determine the average number of days spent in virtual school, weighted by district enrollment, and the share of the school population that is of other ethnicities --- namely, Native Americans or Alaska Natives, and Pacific Islanders --- so that comparisons can be made across all important ethnic classes.
 Other demographic variables might include the share of students experiencing homelessness, who have limited English proficiency or who are of low socioeconomic status.

### 2024-02-13 scripts/00-simulate_data.R
test

@@ -52,8 +52,5 @@ is.wholenumber <- function(x, tol = .Machine$double.eps^0.5) abs(x - round(x)) <
 is.wholenumber(simulated_data2$white_students)
 is.wholenumber(simulated_data2$black_students)
 
-    
-
-
-
+print("hello")
 

### 2024-02-13 scripts/01-download_data.R
Updated download script

@@ -17,7 +17,7 @@ library(tidyverse)
 
 ## Download Data sets ##
 
-zip_file <- "data/raw_data/output_data.csv.zip"
+zip_file <- "data/raw_data/nces_district_enrollment_2018_2020.csv.zip"
 # Unzip the file
 data <- unzip(zip_file)
 race_data <- read_csv(data[1], col_types = cols())
@@ -53,5 +53,3 @@ test_scores_data <- read_dta(here::here("data/raw_data/scores_lm_demographics.dt
 
 ## Save data ##
 write_csv(test_scores_data, "data/raw_data/scores_lm_demographics.csv") #ANALYSIS_DATA?
-
-         

### 2024-02-13 scripts/01-download_data.R
Changes

@@ -11,6 +11,7 @@
 #### Workspace setup ####
 library(haven)
 library(tidyverse)
+library(arrow)
 
 
 #### DATASETS FOR FIGURE 2 ####
@@ -41,7 +42,7 @@ county_district_data <-
 
 ## Save Data sets ##
 
-write_csv(race_data, "data/analysis_data/race_data.csv")
+write_parquet(race_data, "data/analysis_data/race_data.parquet")
 write_csv(broadband_data, "data/analysis_data/broadband_data.csv")
 write_csv(shares_data, "data/analysis_data/shares_data.csv")
 write_csv(county_district_data, "data/analysis_data/county_district_data.csv")

### 2024-02-13 scripts/99-replications.R
Updated file path
Updated file path for excel data file to reflect new location

@@ -15,7 +15,7 @@ library(ggplot2)
 
 #### FIGURE 1 ####
 
-data <- read_excel("/cloud/project/data/raw_data/Tracker-of-national-education-response-to-COVID-19_-21May2020.xlsx", 
+data <- read_excel("data/raw_data/Tracker-of-national-education-response-to-COVID-19_-21May2020.xlsx", 
                    sheet = "Continuity of Learning")
 
 master_data <- data[30:36, c(1) ]

### 2024-02-13 scripts/01-download_data.R
Fixing Errors

@@ -42,10 +42,10 @@ county_district_data <-
 
 ## Save Data sets ##
 
-write_parquet(race_data, "data/analysis_data/race_data.parquet")
-write_csv(broadband_data, "data/analysis_data/broadband_data.csv")
-write_csv(shares_data, "data/analysis_data/shares_data.csv")
-write_csv(county_district_data, "data/analysis_data/county_district_data.csv")
+#write_parquet(race_data, "data/raw_data/race_data.parquet")
+write_csv(broadband_data, "data/raw_data/broadband_data.csv")
+write_csv(shares_data, "data/raw_data/shares_data.csv")
+write_csv(county_district_data, "data/raw_data/county_district_data.csv")
 
 #### DATASETS FOR FIGURE 3 ####
 

### 2024-02-13 scripts/01-download_data.R
Fixing Errors

@@ -42,7 +42,7 @@ county_district_data <-
 
 ## Save Data sets ##
 
-#write_parquet(race_data, "data/raw_data/race_data.parquet")
+write_parquet(race_data, "data/raw_data/race_data.parquet")
 write_csv(broadband_data, "data/raw_data/broadband_data.csv")
 write_csv(shares_data, "data/raw_data/shares_data.csv")
 write_csv(county_district_data, "data/raw_data/county_district_data.csv")

### 2024-02-13 scripts/02-data_cleaning.R
Updated cleaned data
Added more columns regarding the share of various races with regards to enrollment

@@ -57,7 +57,10 @@ cleaned_test_score_data <- raw_test_score_data |>
     change_2019_2021,
     change_2018_2019,
     change_2017_2018,
-    enrollment
+    enrollment,
+    share_enroll_white,
+    share_enroll_black,
+    share_enroll_hispanic
   )
 
 #### Save data ####

### 2024-02-13 paper/paper.qmd
New Stuff

@@
 
-The original paper used for replication is Jack and Oster's "COVID-19, School Closures, and Outcomes" [-@Jack_Oster_2023], published in the American Economic Association's *Journal of Economic Perspectives*.
+For this paper, the raw data from the “COVID-19, School Closures, and Outcomes” paper were used [-@Jack_Oster_2023], published in the American Economic Association's *Journal of Economic Perspectives* [@citeAEA].
 To investigate the degree of school closures in the United States, and their attendant effects on children, they pose the following three questions:
@@
 (3) What is the short-term impact of school closures on student academic performance and learning inequalities?
+
+Whilst the Jack and Oster’s paper uses a range of data files, we only use some of these files.
+The specific files that were used, including their sources and a description of how the data is collected is given below.
+
+### Abbass' Datasets
+
+### Average Virtual Days By Local Characteristics
+
+'District_Overall_Shares.csv'
+
+This dataset is available from the COVID-19 School Data Hub [@citeraw1], and provides information on the percentage of the school year that was spent in person, hybrid, or virtual.
+The data is given for each district, and includes the district’s NCESDistrictID and the state they are a part of.
 

### 2024-02-13 paper/paper.qmd
Added Stuff

@@
 
-'District_Overall_Shares.csv'
+`District_Overall_Shares.csv`
 
-This dataset is available from the COVID-19 School Data Hub [@citeraw1], and provides information on the percentage of the school year that was spent in person, hybrid, or virtual.
+This data set is available from the COVID-19 School Data Hub [@citeraw1], and provides information on the percentage of the school year that was spent in person, hybrid, or virtual.
 The data is given for each district, and includes the district’s NCESDistrictID and the state they are a part of.
+
+`nces_district_directory_2018.dta`
+This dataset is available from the National Center of Education Statistics [@citeraw2].
+This dataset provides a variety of metrics for each district, including the state they are a part of, and their NCES district ID.
+
+`nces_district_enrollment_2018_2020.csv.zip`
+This dataset is available from the National Center of Education Statistics [@citeraw2].
+This dataset provides a variety of metrics for each district in 2018, 2019, and 2020, including the state they are a part of, their NCES district ID, and the numer of students enrolled for the races: American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races.
+The original file was a Stata file, however, to reduce the size, data on 2018 and 2019 was removed since they were not required for our paper.
+Furthermore, the file was converted to a csv file, before then compressing it into a zip file.
+
+`broadband_data_2020October.csv`
+This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" Github Repository [@citeraw3].
+The data is for October 2020, and gives the broadband usage for each county in the United States, as well as the state that the county is a part of.
 

### 2024-02-13 paper/paper.qmd
Changes made

@@
 `nces_district_directory_2018.dta`
+
 This dataset is available from the National Center of Education Statistics [@citeraw2].
@@
 `nces_district_enrollment_2018_2020.csv.zip`
+
 This dataset is available from the National Center of Education Statistics [@citeraw2].
@@
 `broadband_data_2020October.csv`
-This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" Github Repository [@citeraw3].
+
+This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" Github Repository [@kahan2020usbroadband].
 The data is for October 2020, and gives the broadband usage for each county in the United States, as well as the state that the county is a part of.

### 2024-02-13 paper/paper.qmd
Paper

--- 2024-02-13 paper/paper.qmd
@@
 library(DiagrammeR)
+
+# Read data
+cleaned_test_score_data <- read_csv(here("data/analysis_data/cleaned_test_score_data.csv"))
+cleaned_region_data <- read_csv(here("data/analysis_data/cleaned_region_data.csv"))
 ```
@@
 This paper is structured, as follows.
-In Section 2, we address the sources of the datasets in the original paper, the methodologies used to collect them, and highlight key features.
+In Section 2, we address the sources of the data sets in the original paper, the methodologies used to collect them, and highlight key features.
 In Section 3, we conduct a replication of the original study to confirm the robustness of its findings and to design scientific figures that permit a more effective data visualisation.
@@
 
-### Abbass' Datasets
+### Abbass' data sets
 
@@
 
-'District_Overall_Shares.csv'
+`District_Overall_Shares.csv`
 
-This dataset is available from the COVID-19 School Data Hub [@citeraw1], and provides information on the percentage of the school year that was spent in person, hybrid, or virtual.
+This data set is available from the COVID-19 School Data Hub [@citeraw1], and provides information on the percentage of the school year that was spent in person, hybrid, or virtual.
 The data is given for each district, and includes the district’s NCESDistrictID and the state they are a part of.
+
+`nces_district_directory_2018.dta`
+
+This data set is available from the National Center of Education Statistics [@citeraw2].
+This data set provides a variety of metrics for each district, including the state they are a part of, and their NCES district ID.
+
+`nces_district_enrollment_2018_2020.csv.zip`
+
+This data set is available from the National Center of Education Statistics [@citeraw2].
+This data set provides a variety of metrics.
+For each district, the total number of students enrollment is reported and is split by the grade (ranging from Kindergarten to Grade 12), by the sex (Male and Female), and by the race (American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races).
+This information is reported for the years 2018, 2019, and 2020, and also includes the district's NCES district ID and the state that they are a part of.
+
+The original file was a Stata file, however, to reduce the size, data on 2018 and 2019 was first removed, since they were not required for our paper, before then converting the file to a csv file, and then compressing it into a zip file.
+This zip file was uploaded to the raw data folder.
+
+`broadband_data_2020October.csv`
+
+This data set is available from Microsoft’s “United States Broadband Usage Percentages Dataset" Github Repository [@kahan2020usbroadband].
+The data is for October 2020, and gives the broadband usage for each county in the United States, as well as the state that the county is a part of.
 
@@
 
--   address collection / measurement
--   For Krishiv: for research question #1, we actually want data about the rest of the world.
-We should supplement the data given in the package to see where exactly the United States falls with respect to the rest of the world in terms of \# of days closed, rather than
+### Datacleaning for Abbass' Figure 1
+
+### Average Virtual Days By Local Characteristics - Figure 2
+
+The purpose of [@figure2] is to explore the correlations between certain district and county characteristics, and the average number of virtual school days for the respective district or county.
+Specifically, we look at broandband usage by county, and the shares of four races (White, Black, Asian, Hispanic) by district.
+For each county or district, we assign "high" or "low" depending on if their level for the characteristics being explored is above or below their state's median, respectively.
+By doing so, we allow for the results to be driven by a variation within states, as opposed to variation across states.
+
+#### Figures on Race
+
+We start by using `nces_district_enrollment_2018_2020.csv.zip`.
+As previously mentioned, this data set splits the total enrollment into various categories.
+For our paper, we are concerned specifically with race.
+Thus, for each district, we calculate the total number of White, Black, Asian, and Hispanic students enrolled.
+Given the structure of the data, this is done by summing the total enrollment per race for Male and Female for each district.
+Next the total enrollment for the whole district was calculated, before then calculating the share of total enrollment that each race comprises.
+
+The data above was then separated into different tables for each race.
+For each race, we then classified the district as either "High" or "Low" depending on if their share was above or below their respective state's median.
+
+Only the required rows and columns are kept, and the certain columns are converted to the numeric class as appropriate.
+Some enrollment cells did not have a value, indicating that data was not collected for that specific metric.
+These occurred a handful of times for certain races within certain districts.
+These NAs were replaced with 0s.
+Next, total enrollment
+
 -   For Abbass: for research question #2, we want to show that significant variation exists in the average number of days spent in virtual school by demographics, specifically, by race, unemployment rates, and political leanings of the area.
@@
 # Results
+```{r}
+#| label: tbl-daysclosed
+#| echo: false
+#| tbl-cap: "Top 5 countries by number of school closures from Jan 2020 - Dec 2021"
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
 
+# Calculate the number of days schools were closed for each country
+days_closed_per_country <- cleaned_region_data |>
+  group_by(country_name) |>
+  summarize(days_closed = sum(covid_score > 1)) |>
+  arrange(desc(days_closed)) |>
+  select(country_name, days_closed)
+
+days_closed_per_country |>
+  slice(1:5) |>
+  kable(col.names = c("Country", "Days Closed"))
+```
+
+```{r}
+#| label: fig-testscoresbyonline
+#| echo: false
+#| fig-cap: "Test score by percent online (change)"
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
+
+# Calculate the total number of enrollments overall
+total_enrollment <- sum(cleaned_test_score_data$enrollment)
+
+# Filter for Math
+filtered_test_data <- cleaned_test_score_data |>
+  filter(subject == "Math")
+
+# Define in-person percent learning categories
+inperson_group <- c("0-25", "25-50", "50-75", "75-100")
+
+# Change data format into long format from wide format and categorize the in-person share
+long_filtered_test_data <- filtered_test_data |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  mutate(inperson_category = cut(share_inperson, breaks = c(-Inf, 0.25, 0.5, 0.75, Inf), labels = inperson_group))
+
+# Group by year and calculate summary statistics
+summary_test_data <- long_filtered_test_data |>
+  group_by(year_group, inperson_category) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup()
+
+# Calculate the overall weighted average pass rate change
+overall_summary_test_data <- long_filtered_test_data |>
+  group_by(year_group) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate,
+                                                     w = enrollment/total_enrollment,
+                                                     na.rm = TRUE),
+            inperson_category = "Overall")
+
+# Bind both sets of rows together
+summary_test_data <- bind_rows(summary_test_data, overall_summary_test_data)
+
+# Plot the resultant graph
+ggplot(summary_test_data, aes(x = weighted_avg_change_pass * 100, y = inperson_category, color = year_group)) +
+  geom_point(size = 3) + 
+  geom_vline(xintercept = 0, color = "darkgrey") +
+  scale_x_continuous(limits = c(-17, 3)) +
+  scale_y_discrete(limits = c("75-100", "50-75", "25-50", "0-25", "Overall")) +
+  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Percent In-Person",
+       title = "Average Change in Pass Rate by Year in Math") +
+  scale_color_discrete(labels = c("Spring 2018", "Spring 2019", "Spring 2021")) +
+  labs(color = "Year Category") +
+  theme_minimal()
+```
+
+```{r}
+#| label: fig-testscoresmath
+#| echo: false
+#| message: false
+#| fig-cap: "Update"
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
+library(patchwork)
+
+# Filter for Math
+filtered_test_data <- cleaned_test_score_data |>
+  filter(subject == "Math")
+
+# White Share
+white_share <- filtered_test_data |>
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_white, enrollment)
+
+# Black Share
+black_share <- filtered_test_data |>
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_black, enrollment)
+
+# Hispanic Share
+hispanic_share <- filtered_test_data |>
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_hispanic, enrollment)
+
+# Calculate the total number of enrollments overall
+total_enrollment <- sum(white_share$enrollment)
+
+# Define quantiles for white share
+white_share <- white_share |>
+  mutate(quantile = ntile(share_enroll_white, 3)) |>
+  mutate(quantile_level = case_when(
+    quantile == 1 ~ "Low",
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
+  ))
+
+# Define quantiles for black share
+black_share <- black_share |>
+  mutate(quantile = ntile(share_enroll_black, 3)) |>
+  mutate(quantile_level = case_when(
+    quantile == 1 ~ "Low",
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
+  ))
+
+# Define quantiles for hispanic share
+hispanic_share <- hispanic_share |>
+  mutate(quantile = ntile(share_enroll_hispanic, 3)) |>
+  mutate(quantile_level = case_when(
+    quantile == 1 ~ "Low",
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
+  ))
+
+# Group by year and quantile and calculate summary statistics for white share
+summary_white_test_data <- white_share |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  group_by(year_group, quantile_level) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup() |>
+  mutate(race = "White")
+
+# Group by year and quantile and calculate summary statistics for black share
+summary_black_test_data <- black_share |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  group_by(year_group, quantile_level) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup() |>
+  mutate(race = "Black")
+
+# Group by year and quantile and calculate summary statistics for hispanic share
+summary_hispanic_test_data <- hispanic_share |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  group_by(year_group, quantile_level) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup() |>
+  mutate(race = "Hispanic")
+
+# Combine all summary data
+combined_summary_data <- bind_rows(summary_white_test_data, summary_black_test_data, summary_hispanic_test_data)
+
+# Create a ggplot with combined data
+ggplot(combined_summary_data, aes(x = weighted_avg_change_pass * 100, y = quantile_level, color = year_group, shape = race)) +
+  geom_point(size = 2.85, position = position_jitter(height = 0.1)) + 
+  geom_vline(xintercept = 0, color = "darkgrey") +
+  scale_x_continuous(limits = c(-17, 3)) +
+  scale_y_discrete(limits = c("Low", "Middle", "High")) +
+  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Quantile Level",
+       title = "Average Change in Pass Rate by Race and Quantile") +
+  scale_color_discrete(labels = c("Spring 2018", "Spring 2019", "Spring 2021")) +
+  labs(color = "Year Category", shape = "Race") +
+  theme_minimal()
+```
+
+```{r}
+#| label: fig-testscoresmath
+#| echo: false
+#| message: false
+#| fig-cap: "Update"
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
+library(patchwork)
+
+# Filter for MaELAiltered_test_data <- cleaned_test_score_data |>
+  filter(subject == "ELLLA")
+
+# White Share
+white_share <- filtered_test_data |>
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_white, enrollment)
+
+# Black Share
+black_share <- filtered_test_data |>
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_black, enrollment)
+
+# Hispanic Share
+hispanic_share <- filtered_test_data |>
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_hispanic, enrollment)
+
+# Calculate the total number of enrollments overall
+total_enrollment <- sum(white_share$enrollment)
+
+# Define quantiles for white share
+white_share <- white_share |>
+  mutate(quantile = ntile(share_enroll_white, 3)) |>
+  mutate(quantile_level = case_when(
+    quantile == 1 ~ "Low",
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
+  ))
+
+# Define quantiles for black share
+black_share <- black_share |>
+  mutate(quantile = ntile(share_enroll_black, 3)) |>
+  mutate(quantile_level = case_when(
+    quantile == 1 ~ "Low",
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
+  ))
+
+# Define quantiles for hispanic share
+hispanic_share <- hispanic_share |>
+  mutate(quantile = ntile(share_enroll_hispanic, 3)) |>
+  mutate(quantile_level = case_when(
+    quantile == 1 ~ "Low",
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
+  ))
+
+# Group by year and quantile and calculate summary statistics for white share
+summary_white_test_data <- white_share |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  group_by(year_group, quantile_level) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup() |>
+  mutate(race = "White")
+
+# Group by year and quantile and calculate summary statistics for black share
+summary_black_test_data <- black_share |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  group_by(year_group, quantile_level) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup() |>
+  mutate(race = "Black")
+
+# Group by year and quantile and calculate summary statistics for hispanic share
+summary_hispanic_test_data <- hispanic_share |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  group_by(year_group, quantile_level) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup() |>
+  mutate(race = "Hispanic")
+
+# Combine all summary data
+combined_summary_data <- bind_rows(summary_white_test_data, summary_black_test_data, summary_hispanic_test_data)
+
+# Create a ggplot with combined data
+ggplot(combined_summary_data, aes(x = weighted_avg_change_pass * 100, y = quantile_level, color = year_group, shape = race)) +
+  geom_point(size = 2.85, position = position_jitter(height = 0.1)) + 
+  geom_vline(xintercept = 0, color = "darkgrey") +
+  scale_x_continuous(limits = c(-17, 3)) +
+  scale_y_discrete(limits = c("Low", "Middle", "High")) +
+  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Quantile Level",
+       title = "Average Change in Pass Rate by Race and Quantile") +
+  scale_color_discrete(labels = c("Spring 2018", "Spring 2019", "Spring 2021")) +
+  labs(color = "Year Category", shape = "Race") +
+  theme_minimal()
+```
 -   again, the 2023 student paper is very good as a reference
@@
 
-Important sources of bias may have also arisen from the demographic datasets obtained from the US Department of Education's Common Core of Data [@irwin2022report], the US Bureau of Labour Statistics [@bls2021county] and the US Broadband Usage Percentages dataset [@kahan2020usbroadband].
+Important sources of bias may have also arisen from the demographic data sets obtained from the US Department of Education's Common Core of Data [@irwin2022report], the US Bureau of Labour Statistics [@bls2021county] and the US Broadband Usage Percentages data set [@kahan2020usbroadband].
 In particular, there are various errors that may exist in census data, collected to determine district-level race shares across the United States.
 These include *coverage errors*, when a respondent is missed or counted more than once, *non-response errors*, when some information about a respondent is missing, *response errors*, where a question is misunderstood or misreported by a respondent and *processing errors*, when data is incorrectly processed [@censusErrors].
-On the other hand, the US Broadband Usage Percentages dataset determines broadband usage by combining data from Microsoft services [@kahan2020usbroadband].
-In failing to account for other popular forms of internet services, such those provided by Google, Facebook, Amazon and Apple, this dataset may skew the representation of broadband usage patterns in the United States.
+On the other hand, the US Broadband Usage Percentages data set determines broadband usage by combining data from Microsoft services [@kahan2020usbroadband].
+In failing to account for other popular forms of internet services, such those provided by Google, Facebook, Amazon and Apple, this data set may skew the representation of broadband usage patterns in the United States.
 
@@
 Lastly, the state-level assessment data is obtained from only eleven states of the United States, for which district-level data is available.
-This dataset may not be representative of the academic performance of American students as a whole for two reasons.
+This data set may not be representative of the academic performance of American students as a whole for two reasons.
 First, state-standardised assessments remain controversial, with critics questioning whether they accurate indicate academic ability [@yang].

### 2024-02-13 scripts/01-download_data.R
Download and Clean Data
Updated the scripts to download and clean the data for figure 2

@@ -40,13 +40,6 @@ county_district_data <-
     file = "data/raw_data/nces_district_directory_2018.dta",
   )
 
-## Save Data sets ##
-
-write_parquet(race_data, "data/raw_data/race_data.parquet")
-write_csv(broadband_data, "data/raw_data/broadband_data.csv")
-write_csv(shares_data, "data/raw_data/shares_data.csv")
-write_csv(county_district_data, "data/raw_data/county_district_data.csv")
-
 #### DATASETS FOR FIGURE 3 ####
 
 ## Download Data ##

### 2024-02-13 scripts/02-data_cleaning.R

@@ -10,6 +10,13 @@
 #### Workspace setup ####
 library(tidyverse)
 library(data.table)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(haven)
+library(labelled)
+
 
 #### Clean region data ####
 raw_region_data <- read_csv("data/raw_data/region_data.csv")
@@ -66,3 +73,213 @@ cleaned_test_score_data <- raw_test_score_data |>
 #### Save data ####
 fwrite(cleaned_region_data, "data/analysis_data/cleaned_region_data.csv", row.names = FALSE)
 write_csv(cleaned_test_score_data, "data/analysis_data/cleaned_test_score_data.csv")
+
+
+#### FIGURE 2 DATA CLEANING - AVERAGE VIRTUAL DAYS BY CHARACTERISTIC ####
+
+
+# CLEANING BROADBAND RAW DATA #
+
+broadband_data <-
+  read_csv(
+    file = "project/raw_data/broadband_data_2020October.csv",
+    show_col_types = FALSE
+  )
+
+broadband_data$`COUNTY ID` <- as.numeric(broadband_data$`COUNTY ID`)
+broadband_data$`BROADBAND AVAILABILITY PER FCC` <- NULL
+broadband_data$`BROADBAND USAGE` <- as.numeric(broadband_data$`BROADBAND USAGE`)
+
+## Removing Rows with no data on broadband usage
+broadband_data <- na.omit(broadband_data)
+
+## Creating Quantiles 
+broadband_data <- broadband_data |>
+  group_by(ST) |>
+  # Create a new column for quantiles of 'BROADBAND USAGE' variable
+  mutate(QUANTILE = ntile(`BROADBAND USAGE`, 2)) %>%
+  # Convert quantile groups to 'Low' and 'High'
+  mutate(QUANTILE_LABEL = ifelse(QUANTILE == 1, "Low", "High"))
+
+# CLEANING RACE SHARE RAW DATA #
+
+## Read in the raw data ##
+
+zip_file <- "data/raw_data/nces_district_enrollment_2018_2020.csv.zip"
+# Unzip the file
+data <- unzip(zip_file)
+race_data <- read_csv(data[1], col_types = cols())
+
+#Only keeping data on total for each race
+race_data$grade <- as_factor(race_data$grade)
+race_data$race <- as_factor(race_data$race)
+## The number 99 represents the value for Total
+race_data <- race_data[race_data$grade == "99", ] 
+race_data <- race_data[!race_data$race == "99", ]
[…]

### 2024-02-13 paper/paper.qmd
Added Figures

@@
 cleaned_region_data <- read_csv(here("data/analysis_data/cleaned_region_data.csv"))
+
+averaged_broadband <- read_csv(here("data/analysis_data/averaged_broadband.csv"))
 ```
@@
   kable(col.names = c("Country", "Days Closed"))
+```
+
+```{r}
+#| label: fig-broadband
+#| echo: false
+#| fig-cap: "BroadBand"
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
+
+ggplot(averaged_broadband, aes(x = QUANTILE_LABEL, y = average)) +
+  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
+  labs(x = "Quantile Label", y = "Average") +
+  ggtitle("Average Days Virtual by Quantile") +
+  geom_text(aes(label = sprintf("%.0f", average)), 
+            position = position_dodge(width = 0.9), 
+            vjust = -0.5, size = 3) +
+  labs(x = "Quantile", y = "Average Days Virtual") +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
 ```

### 2024-02-13 scripts/02-data_cleaning.R

@@ -82,7 +82,7 @@ write_csv(cleaned_test_score_data, "data/analysis_data/cleaned_test_score_data.c
 
 broadband_data <-
   read_csv(
-    file = "project/raw_data/broadband_data_2020October.csv",
+    file = "data/raw_data/broadband_data_2020October.csv",
     show_col_types = FALSE
   )
 
@@ -229,18 +229,6 @@ averaged_broadband <- final_broadband_data |>
   summarise(average = mean(average_share_virtual, na.rm = TRUE))
 
 write_csv(averaged_broadband, "data/analysis_data/averaged_broadband.csv")
-
-# AVERAGING POLITICAL DATA BASED ON QUANTILES #
-
-final_political_data <- inner_join(averaged_data, political_data, 
-                                   by = c("county_code" = "county_fips"))
-
-averaged_political <- final_political_data |>
-  group_by(QUANTILE_LABEL) |>
-  summarise(average = mean(average_share_virtual, na.rm = TRUE))
-
-write_csv(averaged_political, "data/analysis_data/averaged_political.csv")
-
 
 # AVERAGING RACE DATA BASED ON QUANTILES #
 

### 2024-02-13 paper/paper.qmd
Added Figures
Added the figures to the paper

@@
 averaged_broadband <- read_csv(here("data/analysis_data/averaged_broadband.csv"))
+averaged_white_share <- read_csv(here("data/analysis_data/averaged_white_share.csv"))
+averaged_black_share <- read_csv(here("data/analysis_data/averaged_black_share.csv"))
+averaged_asian_share <- read_csv(here("data/analysis_data/averaged_asian_share.csv"))
+averaged_hispanic_share <- read_csv(here("data/analysis_data/averaged_hispanic_share.csv"))
 ```
@@
 ggplot(averaged_broadband, aes(x = QUANTILE_LABEL, y = average)) +
+  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
+  labs(x = "Quantile Label", y = "Average") +
+  ggtitle("Average Days Virtual by Quantile") +
+  geom_text(aes(label = sprintf("%.0f", average)), 
+            position = position_dodge(width = 0.9), 
+            vjust = -0.5, size = 3) +
+  labs(x = "Quantile", y = "Average Days Virtual") +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+```
+
+```{r}
+#| label: fig-white
+#| echo: false
+#| fig-cap: "Share White"
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
+
+ggplot(averaged_white_share, aes(x = QUANTILE_LABEL, y = average)) +
+  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
+  labs(x = "Quantile Label", y = "Average") +
+  ggtitle("Average Days Virtual by Quantile") +
+  geom_text(aes(label = sprintf("%.0f", average)), 
+            position = position_dodge(width = 0.9), 
+            vjust = -0.5, size = 3) +
+  labs(x = "Quantile", y = "Average Days Virtual") +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+```
+
+```{r}
+#| label: fig-black
+#| echo: false
+#| fig-cap: "Share Black"
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
+
+ggplot(averaged_black_share, aes(x = QUANTILE_LABEL, y = average)) +
+  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
+  labs(x = "Quantile Label", y = "Average") +
+  ggtitle("Average Days Virtual by Quantile") +
+  geom_text(aes(label = sprintf("%.0f", average)), 
+            position = position_dodge(width = 0.9), 
+            vjust = -0.5, size = 3) +
+  labs(x = "Quantile", y = "Average Days Virtual") +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+```
+
+```{r}
+#| label: fig-asian
+#| echo: false
+#| fig-cap: "Share Asian"
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
+
+ggplot(averaged_asian_share, aes(x = QUANTILE_LABEL, y = average)) +
+  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
+  labs(x = "Quantile Label", y = "Average") +
+  ggtitle("Average Days Virtual by Quantile") +
+  geom_text(aes(label = sprintf("%.0f", average)), 
+            position = position_dodge(width = 0.9), 
+            vjust = -0.5, size = 3) +
+  labs(x = "Quantile", y = "Average Days Virtual") +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+```
+
+```{r}
+#| label: fig-hispanic
+#| echo: false
+#| fig-cap: "Share Hispanic"
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
+
+ggplot(averaged_hispanic_share, aes(x = QUANTILE_LABEL, y = average)) +
   geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
@@
 
-```{r}
-#| label: fig-testscoresmath
-#| echo: false
-#| message: false
-#| fig-cap: "Update"
-library(tidyverse)
-library(janitor)
-library(dplyr)
-library(knitr)
-library(here)
-library(readxl)
-library(ggplot2)
-library(patchwork)
-
-# Filter for MaELAiltered_test_data <- cleaned_test_score_data |>
-  filter(subject == "ELLLA")
-
-# White Share
-white_share <- filtered_test_data |>
-  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_white, enrollment)
-
-# Black Share
-black_share <- filtered_test_data |>
-  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_black, enrollment)
-
-# Hispanic Share
-hispanic_share <- filtered_test_data |>
-  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_hispanic, enrollment)
-
-# Calculate the total number of enrollments overall
-total_enrollment <- sum(white_share$enrollment)
-
-# Define quantiles for white share
-white_share <- white_share |>
-  mutate(quantile = ntile(share_enroll_white, 3)) |>
-  mutate(quantile_level = case_when(
-    quantile == 1 ~ "Low",
-    quantile == 2 ~ "Middle",
-    quantile == 3 ~ "High"
-  ))
-
-# Define quantiles for black share
-black_share <- black_share |>
-  mutate(quantile = ntile(share_enroll_black, 3)) |>
-  mutate(quantile_level = case_when(
-    quantile == 1 ~ "Low",
-    quantile == 2 ~ "Middle",
-    quantile == 3 ~ "High"
-  ))
-
-# Define quantiles for hispanic share
-hispanic_share <- hispanic_share |>
-  mutate(quantile = ntile(share_enroll_hispanic, 3)) |>
-  mutate(quantile_level = case_when(
-    quantile == 1 ~ "Low",
-    quantile == 2 ~ "Middle",
-    quantile == 3 ~ "High"
-  ))
-
-# Group by year and quantile and calculate summary statistics for white share
-summary_white_test_data <- white_share |>
-  pivot_longer(cols = starts_with("change_"),
-               names_to = "year_group",
-               values_to = "change_in_pass_rate") |>
-  group_by(year_group, quantile_level) |>
-  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
-                                                     w = enrollment/total_enrollment, 
-                                                     na.rm = TRUE)) |>
-  ungroup() |>
-  mutate(race = "White")
-
-# Group by year and quantile and calculate summary statistics for black share
-summary_black_test_data <- black_share |>
-  pivot_longer(cols = starts_with("change_"),
-               names_to = "year_group",
-               values_to = "change_in_pass_rate") |>
-  group_by(year_group, quantile_level) |>
-  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
-                                                     w = enrollment/total_enrollment, 
-                                                     na.rm = TRUE)) |>
-  ungroup() |>
-  mutate(race = "Black")
-
-# Group by year and quantile and calculate summary statistics for hispanic share
-summary_hispanic_test_data <- hispanic_share |>
-  pivot_longer(cols = starts_with("change_"),
-               names_to = "year_group",
-               values_to = "change_in_pass_rate") |>
-  group_by(year_group, quantile_level) |>
-  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
-                                                     w = enrollment/total_enrollment, 
-                                                     na.rm = TRUE)) |>
-  ungroup() |>
-  mutate(race = "Hispanic")
-
-# Combine all summary data
-combined_summary_data <- bind_rows(summary_white_test_data, summary_black_test_data, summary_hispanic_test_data)
-
-# Create a ggplot with combined data
-ggplot(combined_summary_data, aes(x = weighted_avg_change_pass * 100, y = quantile_level, color = year_group, shape = race)) +
-  geom_point(size = 2.85, position = position_jitter(height = 0.1)) + 
-  geom_vline(xintercept = 0, color = "darkgrey") +
-  scale_x_continuous(limits = c(-17, 3)) +
-  scale_y_discrete(limits = c("Low", "Middle", "High")) +
-  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Quantile Level",
-       title = "Average Change in Pass Rate by Race and Quantile") +
-  scale_color_discrete(labels = c("Spring 2018", "Spring 2019", "Spring 2021")) +
-  labs(color = "Year Category", shape = "Race") +
-  theme_minimal()
-```
--   again, the 2023 student paper is very good as a reference
-
 # Discussion

### 2024-02-13 scripts/02-data_cleaning.R

@@ -239,6 +239,9 @@ averaged_white_share <- white_share |>
   group_by(QUANTILE_LABEL) |>
   summarise(average = mean(share_virtual, na.rm = TRUE))
 
+averaged_white_share <- averaged_white_share |>
+  filter(QUANTILE_LABEL != "NA")
+
 write_csv(averaged_white_share, "data/analysis_data/averaged_white_share.csv")
 
 #Black
@@ -247,6 +250,9 @@ black_share <- inner_join(shares_data, black_share,
 averaged_black_share <- black_share |>
   group_by(QUANTILE_LABEL) |>
   summarise(average = mean(share_virtual, na.rm = TRUE))
+
+averaged_black_share <- averaged_black_share |>
+  filter(QUANTILE_LABEL != "NA")
 
 write_csv(averaged_black_share, "data/analysis_data/averaged_black_share.csv")
 
@@ -257,6 +263,9 @@ asian_share <- inner_join(shares_data, asian_share,
 averaged_asian_share <- asian_share |>
   group_by(QUANTILE_LABEL) |>
   summarise(average = mean(share_virtual, na.rm = TRUE))
+
+averaged_asian_share <- averaged_asian_share |>
+  filter(QUANTILE_LABEL != "NA")
 
 write_csv(averaged_asian_share, "data/analysis_data/averaged_asian_share.csv")
 

### 2024-02-13 scripts/01-download_data.R
Changes to Files

@@ -18,7 +18,7 @@ library(arrow)
 
 ## Download Data sets ##
 
-zip_file <- "data/raw_data/nces_district_enrollment_2018_2020.csv.zip"
+zip_file <- "/Users/krishiv/Documents/New Folder STA302/nces_district_enrollment_2018_2020.csv.zip"
 # Unzip the file
 data <- unzip(zip_file)
 race_data <- read_csv(data[1], col_types = cols())
@@ -46,4 +46,4 @@ county_district_data <-
 test_scores_data <- read_dta(here::here("data/raw_data/scores_lm_demographics.dta"))
 
 ## Save data ##
-write_csv(test_scores_data, "data/raw_data/scores_lm_demographics.csv") #ANALYSIS_DATA?
+write_csv(test_scores_data, "data/raw_data/scores_lm_demographics.csv")

### 2024-02-13 scripts/02-data_cleaning.R

@@ -105,7 +105,7 @@ broadband_data <- broadband_data |>
 
 ## Read in the raw data ##
 
-zip_file <- "data/raw_data/nces_district_enrollment_2018_2020.csv.zip"
+zip_file <- "/Users/krishiv/Documents/New Folder STA302/nces_district_enrollment_2018_2020.csv.zip"
 # Unzip the file
 data <- unzip(zip_file)
 race_data <- read_csv(data[1], col_types = cols())

### 2024-02-13 paper/paper.qmd
Updated quarto file
Made some changes to quarto file and added a new figure

@@
 
+```{r}
+#| label: fig-testscoresela
+#| echo: false
+#| message: false
+#| fig-cap: "Update"
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(knitr)
+library(here)
+library(readxl)
+library(ggplot2)
+library(patchwork)
+
+# Filter for Math
+filtered_test_data <- cleaned_test_score_data |>
+  filter(subject == "ELA")
+
+# White Share
+white_share <- filtered_test_data |>
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_white, enrollment)
+
+# Black Share
+black_share <- filtered_test_data |>
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_black, enrollment)
+
+# Hispanic Share
+hispanic_share <- filtered_test_data |>
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_hispanic, enrollment)
+
+# Calculate the total number of enrollments overall
+total_enrollment <- sum(white_share$enrollment)
+
+# Define quantiles for white share
+white_share <- white_share |>
+  mutate(quantile = ntile(share_enroll_white, 3)) |>
+  mutate(quantile_level = case_when(
+    quantile == 1 ~ "Low",
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
+  ))
+
+# Define quantiles for black share
+black_share <- black_share |>
+  mutate(quantile = ntile(share_enroll_black, 3)) |>
+  mutate(quantile_level = case_when(
+    quantile == 1 ~ "Low",
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
+  ))
+
+# Define quantiles for hispanic share
+hispanic_share <- hispanic_share |>
+  mutate(quantile = ntile(share_enroll_hispanic, 3)) |>
+  mutate(quantile_level = case_when(
+    quantile == 1 ~ "Low",
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
+  ))
+
+# Group by year and quantile and calculate summary statistics for white share
+summary_white_test_data <- white_share |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  group_by(year_group, quantile_level) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup() |>
+  mutate(race = "White")
+
+# Group by year and quantile and calculate summary statistics for black share
+summary_black_test_data <- black_share |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  group_by(year_group, quantile_level) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup() |>
+  mutate(race = "Black")
+
+# Group by year and quantile and calculate summary statistics for hispanic share
+summary_hispanic_test_data <- hispanic_share |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  group_by(year_group, quantile_level) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup() |>
+  mutate(race = "Hispanic")
+
+# Combine all summary data
+combined_summary_data <- bind_rows(summary_white_test_data, summary_black_test_data, summary_hispanic_test_data)
+
+# Create a ggplot with combined data
+ggplot(combined_summary_data, aes(x = weighted_avg_change_pass * 100, y = quantile_level, color = year_group, shape = race)) +
+  geom_point(size = 2.85, position = position_jitter(height = 0.1)) + 
+  geom_vline(xintercept = 0, color = "darkgrey") +
+  scale_x_continuous(limits = c(-17, 3)) +
+  scale_y_discrete(limits = c("Low", "Middle", "High")) +
+  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Quantile Level",
+       title = "Average Change in Pass Rate by Race and Quantile") +
+  scale_color_discrete(labels = c("Spring 2018", "Spring 2019", "Spring 2021")) +
+  labs(color = "Year Category", shape = "Race") +
+  theme_minimal()
+```
+
 # Discussion

### 2024-02-13 paper/paper.qmd
Writing

@@
 This data set is available from the National Center of Education Statistics [@citeraw2].
-This data set provides a variety of metrics for each district, including the state they are a part of, and their NCES district ID.
+This data set provides a variety of metrics for each district, including the state and county they are a part of, as well as their NCES district ID.
 
@@
 The original file was a Stata file, however, to reduce the size, data on 2018 and 2019 was first removed, since they were not required for our paper, before then converting the file to a csv file, and then compressing it into a zip file.
-This zip file was uploaded to the raw data folder.
+This file was then processed within R.
 
@@
 
-#### Figures on Race
-
 We start by using `nces_district_enrollment_2018_2020.csv.zip`.
 As previously mentioned, this data set splits the total enrollment into various categories.
+We start by converting the columns into the numeric class as appropriate.
+Some enrollment cells did not have a value, indicating that data was not collected for that specific metric.
+These occurred a handful of times for certain races within certain districts.
+These NAs were replaced with 0s.
 For our paper, we are concerned specifically with race.
@@
 For each race, we then classified the district as either "High" or "Low" depending on if their share was above or below their respective state's median.
+Using this data, we were now interested in the number of virtual days that each of these districts had.
+This information was available in the `District_Overall_Shares.csv` data set.
+Given that the US average number of school days per year is 180, the percentage for share_virtual was multiplied by 180 for each district.
 
-Only the required rows and columns are kept, and the certain columns are converted to the numeric class as appropriate.
-Some enrollment cells did not have a value, indicating that data was not collected for that specific metric.
-These occurred a handful of times for certain races within certain districts.
-These NAs were replaced with 0s.
-Next, total enrollment
+Next, the aforementioned data for each race that separated the districts into quantiles, and the data for the number of virtual days per district were merged.
+This results in some NAs being produced since the data set on race had more districts than the data on the number of virtual days.
+Given the lack of data, all NAs were droppped.
+Finally, the number of virtual days for the "High" quantile and the "Low" quantile were averaged.
+This results in four data sets, one for each race considered.
+
+To calculate the information regarding broadband, we started with the `broadband_data_2020October.csv` data set.
+Only columns that were necessary were kept, and the columns were converted to the numeric class as appropriate.
+Each county was then classified as either "High" or "Low" depending on if their share was above or below their respective state's median.
+A single county contains multiple districts, and since our data regarding the number of virtual days was based on district, the data was averaged across districts for each county.
+`nces_district_directory_2018.dta` provided information on which county each district belonged to, and was merged with the previous data that calculated the average number of virtual days for each district, before then calculating the average number of virtual days for each county.
+Finally, we average the number of virtual days for the counties labelled "High" and "Low."
 

### 2024-02-14 paper/paper.qmd
Add files via upload

@@
 author: "Krishiv Jain, Julia Kim, Abbass Sleiman"
-thanks: "Code and data are available at: https://github.com/AbbassSleiman/COVID19-US-School-Closures; Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1616/index?step=0"
+thanks: "Code and data are available at: [https://github.com/AbbassSleiman/COVID19-US-School-Closures](https://github.com/AbbassSleiman/COVID19-US-School-Closures); Replication on Social Science Reproduction platform available at: [https://www.socialsciencereproduction.org/reproductions/1616/index?step=0](https://www.socialsciencereproduction.org/reproductions/1616/index?step=0)"
 date: "February 15, 2024"
@@
 library(DiagrammeR)
+library(readxl)
+library(patchwork)
 
@@
 cleaned_region_data <- read_csv(here("data/analysis_data/cleaned_region_data.csv")) 
-
 averaged_broadband <- read_csv(here("data/analysis_data/averaged_broadband.csv"))
@@
 In spite of a short lockdown, equitable school funding and high degree of technological preparedness, we discuss how Dutch students still suffered a loss of the equivalent of one-fifth of a year of education and how the effects were distributed unequally according to student demographics.
-Throughout, our investigation is conducted using the open-source statistical programming language `R` [@R], with functionalities from `tidyverse` [@tidyverse], `janitor` [@janitor], `knitr` [@knitr], `here` [@here], `kableExtra` [@kableExtra] and `DiagrammeR` [@DiagrammeR].
+Throughout, our investigation is conducted using the open-source statistical programming language `R` [@R], with functionalities from `tidyverse` [@tidyverse], `janitor` [@janitor], `knitr` [@knitr], `here` [@here], `kableExtra` [@kableExtra], `DiagrammeR` [@DiagrammeR], `readxl` [@readxl] and `patchwork` [@patchwork].
 
@@
 #| tbl-cap: "Top 5 countries by number of school closures from Jan 2020 - Dec 2021"
-library(tidyverse)
-library(janitor)
-library(dplyr)
-library(knitr)
-library(here)
-library(readxl)
-library(ggplot2)
 
@@
 #| fig-cap: "BroadBand"
-library(tidyverse)
-library(janitor)
-library(dplyr)
-library(knitr)
-library(here)
-library(readxl)
-library(ggplot2)
-
 ggplot(averaged_broadband, aes(x = QUANTILE_LABEL, y = average)) +
@@
 #| fig-cap: "Share White"
-library(tidyverse)
-library(janitor)
-library(dplyr)
-library(knitr)
-library(here)
-library(readxl)
-library(ggplot2)
-
 ggplot(averaged_white_share, aes(x = QUANTILE_LABEL, y = average)) +
@@
 #| fig-cap: "Share Black"
-library(tidyverse)
-library(janitor)
-library(dplyr)
-library(knitr)
-library(here)
-library(readxl)
-library(ggplot2)
-
 ggplot(averaged_black_share, aes(x = QUANTILE_LABEL, y = average)) +
@@
 #| fig-cap: "Share Asian"
-library(tidyverse)
-library(janitor)
-library(dplyr)
-library(knitr)
-library(here)
-library(readxl)
-library(ggplot2)
-
 ggplot(averaged_asian_share, aes(x = QUANTILE_LABEL, y = average)) +
@@
 #| fig-cap: "Share Hispanic"
-library(tidyverse)
-library(janitor)
-library(dplyr)
-library(knitr)
-library(here)
-library(readxl)
-library(ggplot2)
-
 ggplot(averaged_hispanic_share, aes(x = QUANTILE_LABEL, y = average)) +
@@
 #| fig-cap: "Test score by percent online (change)"
-library(tidyverse)
-library(janitor)
-library(dplyr)
-library(knitr)
-library(here)
-library(readxl)
-library(ggplot2)
-
 # Calculate the total number of enrollments overall
@@
 #| fig-cap: "Update"
-library(tidyverse)
-library(janitor)
-library(dplyr)
-library(knitr)
-library(here)
-library(readxl)
-library(ggplot2)
-library(patchwork)
-
 # Filter for Math

### 2024-02-14 paper/paper.qmd
Add files via upload

@@
   bookdown::pdf_document2
-toc: false
+toc: true
 fig_caption: yes
@@
 
-For this paper, the raw data from the “COVID-19, School Closures, and Outcomes” paper were used [-@Jack_Oster_2023], published in the American Economic Association's *Journal of Economic Perspectives* [@citeAEA].
+The paper and raw data used for replication is obtained from “COVID-19, School Closures, and Outcomes” [@Jack_Oster_2023], published in the American Economic Association's *Journal of Economic Perspectives* [@citeAEA].
 To investigate the degree of school closures in the United States, and their attendant effects on children, they pose the following three questions:
 
-(1) Relative to the global picture, what is the extent of school closures in the United States?
+(1) Relative to the global picture, what was the extent of school closures in the United States in 2020-2021?
 
-(2) What are the demographic patterns underlying these closures?
-Namely, how are the number of days of school closed correlated with ethnicity, unemployment rate and political leanings at the district- or county-level?
+(2) What are the demographic patterns underlying these closures? Namely, how are the number of days of school closed correlated with ethnicity and broadband usage at the district- or county-level?
 
@@
 
-Whilst the Jack and Oster’s paper uses a range of data files, we only use some of these files.
-The specific files that were used, including their sources and a description of how the data is collected is given below.
+Whilst the work by Jack and Oster [-@Jack_Oster_2023] uses number of data files, we require only a subset of them.
+The specific files used to address each of the three major research questions, including their sources and method of data collection, is given below.
 
-### Abbass' data sets
+### Extent of School Closures in the United States and the World
 
-### Average Virtual Days By Local Characteristics
+### Average Number of School Closures by Local Demographic Characteristics
 
@@
 
-This data set is available from the COVID-19 School Data Hub [@citeraw1], and provides information on the percentage of the school year that was spent in person, hybrid, or virtual.
-The data is given for each district, and includes the district’s NCESDistrictID and the state they are a part of.
+This dataset is obtained from the COVID-19 School Data Hub (CSDH), a database created by Jack and Oster to understand how the COVID-19 pandemic shaped American students' modes of learning in 2020-2021 [@citeraw1].
+For each district in the United States, it provides information on the percentage of the school year spent in each type of schooling mode -- in-person, hybrid and virtual -- and the state of which they are a part.
+To collect such data, the CDSH team submitted data requests to state education agencies, asking for their record of learning models used by schools and districts in 2020-2021 [@citeraw1].
+They requested the data to be given at the school or district level and at the most frequent reporting interval available.
 
@@
 
-This data set is available from the National Center of Education Statistics [@citeraw2].
-This data set provides a variety of metrics for each district, including the state and county they are a part of, as well as their NCES district ID.
+This dataset is obtained from the National Center of Education Statistics [@citeraw2].
+For each district, it provides information as to the county and state to which they belong, and their NCES district ID.
 
@@
 
-This data set is available from the National Center of Education Statistics [@citeraw2].
-This data set provides a variety of metrics.
-For each district, the total number of students enrollment is reported and is split by the grade (ranging from Kindergarten to Grade 12), by the sex (Male and Female), and by the race (American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races).
-This information is reported for the years 2018, 2019, and 2020, and also includes the district's NCES district ID and the state that they are a part of.
+This dataset is obtained from the National Center of Education Statistics [@citeraw2].
+For each district and for each of the years 2018, 2019 and 2020, it reports the total student enrollment, split by grade (ranging from Kindergarten to Grade 12), sex (Male and Female), and ethnic class (American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races).
+The data is collected via surveys and supplied by state agencies to NCES [@USDeptCommerce].
 

### 2024-02-14 paper/paper.qmd
Improved Figure 2
Combined the 4 seperate race figures into 1 panel of data

@@
 library(patchwork)
+library(gridExtra)
 
@@
 #| echo: false
-#| fig-cap: "Share White"
-ggplot(averaged_white_share, aes(x = QUANTILE_LABEL, y = average)) +
+#| fig-cap: "Average Virtual School Days by Share of Race"
+
+whiteplot <- ggplot(averaged_white_share, aes(x = QUANTILE_LABEL, y = average)) +
   geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
-  labs(x = "Quantile Label", y = "Average") +
-  ggtitle("Average Days Virtual by Quantile") +
+  labs(x = "Quantile", y = "Average Days Virtual") +
+  ggtitle("White Share") +
+  geom_text(aes(label = sprintf("%.0f", average)), 
+            position = position_dodge(width = 0.9), 
+            vjust = -0.5, size = 3) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5, size = 10),
+                axis.title.x = element_text(size = 9),
+                axis.title.y = element_text(size = 9),
+        axis.text.y = element_text(size = 7.5)) +
+  ylim(0, 60)
+
+blackplot <- ggplot(averaged_black_share, aes(x = QUANTILE_LABEL, y = average)) +
+  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
+  labs(x = "Quantile", y = "Average Days Virtual") +
+  ggtitle("Black Share") +
+  geom_text(aes(label = sprintf("%.0f", average)), 
+            position = position_dodge(width = 0.9), 
+            vjust = -0.5, size = 3) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5, size = 10),
+                axis.title.x = element_text(size = 9),
+                axis.title.y = element_text(size = 9),
+        axis.text.y = element_text(size = 7.5)) +
+  ylim(0, 60)
+
+asianplot <- ggplot(averaged_asian_share, aes(x = QUANTILE_LABEL, y = average)) +
+  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
+  labs(x = "Quantile", y = "Average Days Virtual") +
+  ggtitle("Asian Share") +
   geom_text(aes(label = sprintf("%.0f", average)), 
@@
   theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-```
+  theme(plot.title = element_text(hjust = 0.5, size = 10),
+                axis.title.x = element_text(size = 9),
+                axis.title.y = element_text(size = 9),
+        axis.text.y = element_text(size = 7.5)) +
+  ylim(0, 60)
 
-```{r}
-#| label: fig-black
-#| echo: false
-#| fig-cap: "Share Black"
-ggplot(averaged_black_share, aes(x = QUANTILE_LABEL, y = average)) +
+hispanicplot <- ggplot(averaged_hispanic_share, aes(x = QUANTILE_LABEL, y = average)) +
   geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
-  labs(x = "Quantile Label", y = "Average") +
-  ggtitle("Average Days Virtual by Quantile") +
+  labs(x = "Quantile", y = "Average Days Virtual") +
+    ggtitle("Hispanic Share") +
   geom_text(aes(label = sprintf("%.0f", average)), 
@@
   theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-```
+  theme(plot.title = element_text(hjust = 0.5, size = 10),
+                axis.title.x = element_text(size = 9),
+                axis.title.y = element_text(size = 9),
+        axis.text.y = element_text(size = 7.5)) +
+  ylim(0, 60)
 
-```{r}
-#| label: fig-asian
-#| echo: false
-#| fig-cap: "Share Asian"
-ggplot(averaged_asian_share, aes(x = QUANTILE_LABEL, y = average)) +
-  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
-  labs(x = "Quantile Label", y = "Average") +
-  ggtitle("Average Days Virtual by Quantile") +
-  geom_text(aes(label = sprintf("%.0f", average)), 
-            position = position_dodge(width = 0.9), 
-            vjust = -0.5, size = 3) +
-  labs(x = "Quantile", y = "Average Days Virtual") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-```
+grid.arrange(
+  whiteplot, blackplot, asianplot, hispanicplot,
+  nrow = 2, 
+  heights = c(1, 1)
+)
 
-```{r}
-#| label: fig-hispanic
-#| echo: false
-#| fig-cap: "Share Hispanic"
-ggplot(averaged_hispanic_share, aes(x = QUANTILE_LABEL, y = average)) +
-  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
-  labs(x = "Quantile Label", y = "Average") +
-  ggtitle("Average Days Virtual by Quantile") +
-  geom_text(aes(label = sprintf("%.0f", average)), 
-            position = position_dodge(width = 0.9), 
-            vjust = -0.5, size = 3) +
-  labs(x = "Quantile", y = "Average Days Virtual") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
 ```

### 2024-02-14 paper/paper.qmd
Add files via upload

@@
 
-In studying the scope of school closures across the United States, they reported that the country experienced, on average, one of the highest number of days of school closed between January 2020 to December 2021 worldwide [@Jack_Oster_2023].
+In studying the scope of school closures across the United States (US), they reported that the country experienced, on average, one of the highest number of days of school closed between January 2020 to December 2021 worldwide [@Jack_Oster_2023].
 Jack and Oster [-@Jack_Oster_2023] also found that the duration of school closures varies with local demographic characteristics, with more disadvantaged districts facing more prolonged closures.
@@
 In spite of a short lockdown, equitable school funding and high degree of technological preparedness, we discuss how Dutch students still suffered a loss of the equivalent of one-fifth of a year of education and how the effects were distributed unequally according to student demographics.
-Throughout, our investigation is conducted using the open-source statistical programming language `R` [@R], with functionalities from `tidyverse` [@tidyverse], `janitor` [@janitor], `knitr` [@knitr], `here` [@here], `kableExtra` [@kableExtra], `DiagrammeR` [@DiagrammeR], `readxl` [@readxl] and `patchwork` [@patchwork].
+Throughout, our investigation is conducted using the open-source statistical programming language `R` [@R], with functionalities from `tidyverse` [@tidyverse], `janitor` [@janitor], `knitr` [@knitr], `here` [@here], `kableExtra` [@kableExtra], `DiagrammeR` [@DiagrammeR], `readxl` [@readxl], `patchwork` [@patchwork] and `gridExtra` [@gridExtra].
 
@@
 
+`region_data.csv`
+
+`county_region.csv`
+
+This dataset includes the country and region name
+
+country_name,region_name
+
 ### Average Number of School Closures by Local Demographic Characteristics
@@
 
-The original file was a Stata file, however, to reduce the size, data on 2018 and 2019 was first removed, since they were not required for our paper, before then converting the file to a csv file, and then compressing it into a zip file.
-This file was then processed within R.
+Note the original file was a `Stata` file of very large size.
+To reduce its size, 2018 and 2019 data were removed, being unnecessary for our paper.
+The file was then converted to a `.csv` file and compressed into a `.zip` file, before being processed in R for analysis.
 
@@
 
-This data set is available from Microsoft’s “United States Broadband Usage Percentages Dataset" Github Repository [@kahan2020usbroadband].
-The data is for October 2020, and gives the broadband usage for each county in the United States, as well as the state that the county is a part of.
+This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" GitHub Repository [@kahan2020usbroadband].
+The data consists of broadband usage percentages at the US county-level in October 2020, obtained from anonymised data Microsoft collects.
+In less technical terms, this means that every time a device receives an update from or connects to a Microsoft service, Microsoft servers make an estimate of its throughput speed and determine its location at the zip-code level [@kahan2020usbroadband].
+After making such measurements, noise is added to data aggregations, preventing leakage about specific individuals in the dataset and ensuring differential privacy.
+
+### Standardised Assessment Scores
+
+`scores_lm_demographics.csv`
 
 ## Methodology
+### Extent of School Closures in the United States and the World
 
-### Datacleaning for Abbass' Figure 1
-
-### Average Virtual Days By Local Characteristics - Figure 2
+### Average Number of School Closures by Local Demographic Characteristics
 
@@
 
--   For Abbass: for research question #2, we want to show that significant variation exists in the average number of days spent in virtual school by demographics, specifically, by race, unemployment rates, and political leanings of the area.
-Ignore school mode with little variation.
--   For Abbass: please extend the pass rate figure by incorporating data from the replication package of the other paper, in order to stratify by race, percent in-person, FRPL and ELL (for example).
-You can see the figure here: <https://www.aeaweb.org/research/charts/pandemic-schooling-test-scores-us> Ignore state, probably
-
-## Features
-
--   rigorously define variables in a neat way
--   e.g., define "school closures" rigorously (e.g., a closure is identified as Tracker score of 2 or 3... what is a Tracker score?)
+### Standardised Assessment Scores
 

### 2024-02-14 paper/paper.qmd
Add files via upload

@@
 author: "Krishiv Jain, Julia Kim, Abbass Sleiman"
-thanks: "Code and data are available at: [https://github.com/AbbassSleiman/COVID19-US-School-Closures](https://github.com/AbbassSleiman/COVID19-US-School-Closures); Replication on Social Science Reproduction platform available at: [https://www.socialsciencereproduction.org/reproductions/1616/index?step=0](https://www.socialsciencereproduction.org/reproductions/1616/index?step=0)"
+thanks: "Code and data are available at: [https://github.com/AbbassSleiman/COVID19-US-School-Closures](https://github.com/AbbassSleiman/COVID19-US-School-Closures); Replication on Social Science Reproduction platform available at: [https://www.socialsciencereproduction.org/reproductions/8aab4425-63ad-47bc-93ef-82076d6e49cc/index](https://www.socialsciencereproduction.org/reproductions/8aab4425-63ad-47bc-93ef-82076d6e49cc/index)"
 date: "February 15, 2024"
@@
 
-(1) With respect to the world, the United States faced second highest number of days of school closed between January 2020 to December 2021, with a mean number of days of 667.
+(1) With respect to the world, the United States faced the second highest number of days of schoolclosed between January 2020 to December 2021, with a mean number of days of 667.
 
@@
 
-`county_region.csv`
+This dataset is obtained from the Oxford COVID-19 Policy Tracker, a project that collected information on COVID-19 policy measures for the years 2020, 2021 and 2022 [@Hale].
+For 185 countries, the dataset assigns a daily Tracker score for each day between January 1st, 2020, and December 31st, 2022.
+Note that a Tracker score is defined as an integer value between 0 and 3, with a value of 2 or 3 denoting a school closure [@Jack_Oster_2023].
 
-This dataset includes the country and region name
+`country_region.csv`
 
-country_name,region_name
+This dataset was  by ourselves for the purpose of replicating "FIGURE 2" in `99-replications.R`.
+It includes the same countries found in `region_data.csv` as well as the region to which they correspond, as classified by the World Bank [@worldbank2023].
+These regions are sub-Saharan Africa, Europe and Central Asia, East Asia and Pacific, Middle East and North Africa, Latin America and Caribbean, South Asia and North America.
 
@@
 
-### Standardised Assessment Scores
+### Standardised Test Assessment Scores
 
 `scores_lm_demographics.csv`
+
+This dataset is obtained from the final dataset found in the data repository
+
+Standardised assessments were cancelled in 2020 due to the pandemic.
 
@@
 
+In an attempt to garner a deeper understanding of how the US compares to the world with regards to their explore how the US compares to the rest of the world with regards to the number @tbl-daysclosed provides a snippet of the top to nations by
+
 ### Average Number of School Closures by Local Demographic Characteristics
 
-The purpose of [@figure2] is to explore the correlations between certain district and county characteristics, and the average number of virtual school days for the respective district or county.
+The purpose of Figures \ref{fig-broadband} and \ref{fig-white} is to explore the correlations between certain district and county characteristics, and the average number of virtual school days for the respective district or county.
 Specifically, we look at broandband usage by county, and the shares of four races (White, Black, Asian, Hispanic) by district.
@@
 
-### Standardised Assessment Scores
+### Standardised Test Assessment Scores
 
 # Results
+Data from the Oxford COVID-19 Policy Tracker [@Hale] and World Bank [@worldbank2023] were used to determine the average number of school closures by regions worldwide between January 2020-December 2021.
+We reconstruct this result in Figure \ref{fig-daysclosed} and extract the top 5 countries with the highest average number of closures in Table \ref{tbl-daysclosed}.
+Figure \ref{fig-daysclosed} shows that North America had the highest at 535 days, which is around 73% of the two-year period, whilst sub-Saharan Africa had the least at 300 days, or around 38% of the two-year period.
+Thus, countries with the longest closures spent more than twice the amount of time in virtual schooling compared to those with the shortest closures.
+
+```{r}
+#| label: fig-daysclosed
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-cap: "Average number of days of school closed, by region, between January 2020–December 2021."
+# Calculate the number of days schools were closed for each country
+days_closed_per_country <- cleaned_region_data |>
+  group_by(region_name, country_name) |>
+  summarize(days_closed = sum(covid_score > 1))
+
+# Calculate the mean number of days closed for each region
+mean_days_closed_per_region <- days_closed_per_country |>
+  group_by(region_name) |>
+  summarize(mean_days_closed = mean(days_closed))
+
+# Sort regions in ascending order by mean_days_closed
+mean_days_closed_per_region <- mean_days_closed_per_region |>
+  arrange(mean_days_closed)
+
+# Create a bar chart
+ggplot(mean_days_closed_per_region, 
+       aes(x = reorder(region_name, mean_days_closed), y = mean_days_closed)) +
+  geom_bar(stat = "identity", fill = "skyblue") +
+  geom_text(aes(label = round(mean_days_closed)), vjust = -0.5, color = "black", size = 2.5) +
+  labs(x = "Region", y = "Mean Days Closed") +
+  scale_y_continuous(
+    limits = c(0, 600),
+    breaks = seq(0, 600, by = 100)
+  ) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+In studying individual countries, Table \ref{tbl-daysclosed} shows that the United States faced the second highest number of closures worldwide during this two-year period, with a mean number of 667 days.
+This is, in fact, significantly higher than the mean number of closures worldwide, determined to be $356 \pm 175$ days.
+Thus, relative to the global picture, the extent of school closures in North America and, in particular, the United States appears to be significantly more prolonged.
+
 ```{r}
@@
 #| echo: false
-#| tbl-cap: "Top 5 countries by number of school closures from Jan 2020 - Dec 2021"
+#| warning: false
+#| message: false
+#| tbl-cap: "Countries with Highest School Closures from Jan 2020-Dec 2021."
 
@@
 
+Moreover, data from CSDH [@citeraw1], NCES [@citeraw2] and Microsoft [@kahan2020usbroadband] were used to show correlations between school closures and demographic characteristics, both across and within US states.
+We reconstruct and extend a portion of the data used for this analysis in Figures \ref{fig-broadband} and \ref{fig-white}.
+In particular, we enrich the analysis on the average days in virtual school by race, by adding shares of White and Asian students.
+This is done so that more insightful comparisons can be made across important ethnic classes.
+
+Figure \ref{fig-broadband} shows correlations ...
+Altogether, school districts located in counties with lower broadband usage spent more of the 2020-2021 school year in virtual learning, consistent with the results obtained by Jack and Oster [-@Jack_Oster_2023].
+
 ```{r}
@@
 #| echo: false
-#| fig-cap: "BroadBand"
+#| warning: false
+#| message: false
+#| fig-cap: "Average days in virtual school by county broadband usage."
 ggplot(averaged_broadband, aes(x = QUANTILE_LABEL, y = average)) +
@@
   labs(x = "Quantile Label", y = "Average") +
-  ggtitle("Average Days Virtual by Quantile") +
   geom_text(aes(label = sprintf("%.0f", average)), 
@@
   theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
+  theme(plot.title = element_text(hjust = 0.5, size = 12))
 ```
+
+On the other hand, Figure \ref{fig-white} shows correlations [ADD DETAIL].
+In particular, within state, school districts with higher shares of Black and Hispanic students spent more of the 2020-2021 year in virtual schooling than those with lower shares of Black and Hispanics.
+Precisely the opposite trend is observed for white students.
+No significant variation in the days spent in virtual schooling is observed for Asian students.
+[ADD MORE DETAIL]
 
@@
 #| echo: false
-#| fig-cap: "Average Virtual School Days by Share of Race"
+#| warning: false
+#| message: false
+#| fig-cap: "Average days in virtual school by district-level race shares."
 
@@
 
+Taken together, in-person education was inequitably distributed across demographic characteristics, with more disadvantaged districts spending more time in virtual schooling [@Jack_Oster_2023].
+In particular, districts with less technological preparedness and higher shares of minorities -- especially Blacks and Hispanics -- were further disenfranchised by less access to in-person education.
+This pattern likely reinforced educational inequities between vulnerable and more privileged groups.
+
+Finally, data from ...
+was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021.
+We again reconstruct and extend the data...
+
+[ADD DETAIL].
+
+Panels A and B show the scores in mathematics and in ELA, respectively. [EXPLAIN FIGURE & SYMBOLS]
+
+Consistent with Jack and Oster [-@Jack_Oster_2023], our analysis shows a significant decline in pass rates from the 2018-2019 to the 2020-2021 school year.
+In particular, pass rates in mathematics and ELA declined by 12.8 and 6.8 percentage points, respectively.
+The discrepancy between these two subjects is consistent with much of the current economic literature, which shows mathematics scores to be more sensitive to schooling differences [@betts2011effect; @angrist].
+
+... Thus, we find that in-person learning has significantly higher benefits for districts with larger shares of Black and Hispanic students.
+
 ```{r}
@@
 #| echo: false
+#| message: false
+#| warning: false 
 #| fig-cap: "Test score by percent online (change)"

### 2024-02-14 paper/paper.qmd
Updated quarto file
Added new figure

@@
 ```{r}
-#| label: fig-testscoresbyonline
+#| label: fig-mathscoresbyonline
 #| echo: false
@@
 #| fig-cap: "Test score by percent online (change)"
+
 # Calculate the total number of enrollments overall
@@
   scale_y_discrete(limits = c("75-100", "50-75", "25-50", "0-25", "Overall")) +
-  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Percent In-Person",
-       title = "Average Change in Pass Rate by Year in Math") +
+  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Percent In-Person") +
   scale_color_discrete(labels = c("Spring 2018", "Spring 2019", "Spring 2021")) +
@@
 ```{r}
-#| label: fig-testscoresmath
+#| label: fig-elascoresbyonline
+#| echo: false
+#| message: false
+#| warning: false 
+#| fig-cap: "Test score by percent online (change)"
+# Calculate the total number of enrollments overall
+total_enrollment <- sum(cleaned_test_score_data$enrollment)
+
+# Filter for Math
+filtered_test_data <- cleaned_test_score_data |>
+  filter(subject == "ELA")
+
+# Define in-person percent learning categories
+inperson_group <- c("0-25", "25-50", "50-75", "75-100")
+
+# Change data format into long format from wide format and categorize the in-person share
+long_filtered_test_data <- filtered_test_data |>
+  pivot_longer(cols = starts_with("change_"),
+               names_to = "year_group",
+               values_to = "change_in_pass_rate") |>
+  mutate(inperson_category = cut(share_inperson, breaks = c(-Inf, 0.25, 0.5, 0.75, Inf), labels = inperson_group))
+
+# Group by year and calculate summary statistics
+summary_test_data <- long_filtered_test_data |>
+  group_by(year_group, inperson_category) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate, 
+                                                     w = enrollment/total_enrollment, 
+                                                     na.rm = TRUE)) |>
+  ungroup()
+
+# Calculate the overall weighted average pass rate change
+overall_summary_test_data <- long_filtered_test_data |>
+  group_by(year_group) |>
+  summarize(weighted_avg_change_pass = weighted.mean(change_in_pass_rate,
+                                                     w = enrollment/total_enrollment,
+                                                     na.rm = TRUE),
+            inperson_category = "Overall")
+
+# Bind both sets of rows together
+summary_test_data <- bind_rows(summary_test_data, overall_summary_test_data)
+
+# Plot the resultant graph
+ggplot(summary_test_data, aes(x = weighted_avg_change_pass * 100, 
+                                                 y = inperson_category, color = year_group)) +
+  geom_point(size = 3) + 
+  geom_vline(xintercept = 0, color = "darkgrey") +
+  scale_x_continuous(limits = c(-17, 3)) +
+  scale_y_discrete(limits = c("75-100", "50-75", "25-50", "0-25", "Overall")) +
+  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Percent In-Person") +
+  scale_color_discrete(labels = c("Spring 2018", "Spring 2019", "Spring 2021")) +
+  labs(color = "Year Category") +
+  theme_minimal()
+```
+
+```{r}
+#| label: fig-mathscoresrace
 #| echo: false
@@
 # Create a ggplot with combined data
-ggplot(combined_summary_data, aes(x = weighted_avg_change_pass * 100, y = quantile_level, color = year_group, shape = race)) +
+ggplot(combined_summary_data, aes(x = weighted_avg_change_pass * 100, 
+                                                    y = quantile_level, color = year_group, shape = race)) +
   geom_point(size = 2.85, position = position_jitter(height = 0.1)) + 
@@
 # Create a ggplot with combined data
-ggplot(combined_summary_data, aes(x = weighted_avg_change_pass * 100, y = quantile_level, color = year_group, shape = race)) +
+ggplot(combined_summary_data, aes(x = weighted_avg_change_pass * 100, 
+                                                   y = quantile_level, color = year_group, shape = race)) +
   geom_point(size = 2.85, position = position_jitter(height = 0.1)) + 

### 2024-02-14 paper/paper.qmd
Figure 2 Results

@@
 
-Whilst the work by Jack and Oster [-@Jack_Oster_2023] uses number of data files, we require only a subset of them.
+Whilst the work by Jack and Oster [@Jack_Oster_2023] uses number of data files, we require only a subset of them.
 The specific files used to address each of the three major research questions, including their sources and method of data collection, is given below.
@@
 
-This dataset was  by ourselves for the purpose of replicating "FIGURE 2" in `99-replications.R`.
+This dataset was  manually created by ourselves for the purpose of replicating "FIGURE 2" in `99-replications.R`.
 It includes the same countries found in `region_data.csv` as well as the region to which they correspond, as classified by the World Bank [@worldbank2023].
-These regions are sub-Saharan Africa, Europe and Central Asia, East Asia and Pacific, Middle East and North Africa, Latin America and Caribbean, South Asia and North America.
+These regions are sub-Saharan Africa, Europe and Central Asia, East Asia and Pacific, Middle East and North Africa, Latin America and Caribbean, South Asia, and North America.
 
@@
 
-This dataset is obtained from the final dataset found in the data repository
-
-Standardised assessments were cancelled in 2020 due to the pandemic.
+This dataset is a csv version of `scores_lm_demographics.dta` obtained from the final dataset found in the data repository for “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@TestScore].
+This dataset contains extensive information on various school districts across the aforementioned 11 states, including information on the shares of students by race, the share of schooling done in-person, and changes in average test scores in both Math and ELA from the previous year across the years 2018-2019 and 2021-2022 (no information is present regarding the year 2020 as all standardised assessments were cancelled due to the pandemic).
 
@@
 
-In an attempt to garner a deeper understanding of how the US compares to the world with regards to their explore how the US compares to the rest of the world with regards to the number @tbl-daysclosed provides a snippet of the top to nations by
+@fig-daysclosed depicts the average number of school closures by region, as defined by the World Bank, between the start of January 2020 and the end of December 2021.
+In particular, it employs data on 185 countries, each of which is assigned its particular region, and provides the average number of school closures for nations in each region between the aforementioned time frame.
 
-### Average Number of School Closures by Local Demographic Characteristics
+In order to achieve this, we first created the dataset `country_region.csv` which assigns each of the 185 countries present in the primary dataset, `region_data.csv`, its respective region.
+This was done since `region_data.csv` did not feature each nation's region, and as such, by creating the `country_region.csv` dataset we were able to 'merge' the two sets of information so that the final product featured all information regarding the Covid Tracker score of each country one each day, as well as the region the country is in.
 
-The purpose of Figures \ref{fig-broadband} and \ref{fig-white} is to explore the correlations between certain district and county characteristics, and the average number of virtual school days for the respective district or county.
+We initially cleaned the data in `region_data.csv` by omitting information from the year 2022 in a bid to replicate and examine the internal validity of the work by Jack and Oster who also omitted the year 2022 from their figure [@Jack_Oster_2023].
+From there, only the columns of interest were kept which detailed the country name, (empty) region name, date, and Covid Tracker score.
+We also found a minor spelling error of the Faroe Islands which were incorrectly spelled as Faeroe Islands which we also amended in the cleaning process.
+From here, we simply merged the cleaned `region_data.csv` with the regions listed in `country_region.csv` in order fill in the empty region names present in the original dataset.
+
+With the cleaned dataset, we were able to create the figure detailing the average days closed by region by first grouping the cleaned data by region name and country, then summing the number of instances where a Tracker score of 2 or 3 was present (as this defines a school closure as per Jack and Oster's work [@Jack_Oster_2023]).
+From there, we calculated the mean number of days closed by region by computing the average number of days closed for all nations in a given region.
+
+Then, in an attempt to garner a deeper understanding of how the US compares to other nations with regards to their COVID-19 schooling policies and measures, we employ @tbl-daysclosed which provides a snippet of the top 5 countries by number of school closures between the start of January 2020 and the end of December 2021.
+Due to the US featuring the second-highest number of school closures, @tbl-daysclosed specifically depicts the top 5 nations in an attempt to evidence the US’ large number of closures relative to the rest of the world.
+In order to generate this figure, we employed the same cleaned dataset
+
+### Average Number of School Closures by Local Demographic Characteristics {#sec-datacleaning2}
+
+The purpose of Figures \ref{fig-broadband} and \ref{fig-race} is to explore the correlations between certain district and county characteristics, and the average number of virtual school days for the respective district or county.
 Specifically, we look at broandband usage by county, and the shares of four races (White, Black, Asian, Hispanic) by district.
@@
 #| fig-cap: "Average number of days of school closed, by region, between January 2020–December 2021."
+#| fig-pos: H
+
 # Calculate the number of days schools were closed for each country
@@
 #| tbl-cap: "Countries with Highest School Closures from Jan 2020-Dec 2021."
+#| tbl-pos: H
 
@@
 
-Moreover, data from CSDH [@citeraw1], NCES [@citeraw2] and Microsoft [@kahan2020usbroadband] were used to show correlations between school closures and demographic characteristics, both across and within US states.
-We reconstruct and extend a portion of the data used for this analysis in Figures \ref{fig-broadband} and \ref{fig-white}.
-In particular, we enrich the analysis on the average days in virtual school by race, by adding shares of White and Asian students.
-This is done so that more insightful comparisons can be made across important ethnic classes.
+Moreover, data from CSDH [@citeraw1], NCES [@citeraw2] and Microsoft [@kahan2020usbroadband] were used to delve deeper and analyse correlations between the average number of virtual schools days, and certain demographic characteristics, and Figures \ref{fig-broadband} and \ref{fig-race} were created.
+As discussed previously, Figure \ref{fig-broadband} shows the average number of virtual days for counties that were classified as "Low" and those classified as "High," whilst Figure \ref{fig-race} shows the average for districts.
+The classification of districts and counties was explained in @sec-datacleaning2.
 
-Figure \ref{fig-broadband} shows correlations ...
-Altogether, school districts located in counties with lower broadband usage spent more of the 2020-2021 school year in virtual learning, consistent with the results obtained by Jack and Oster [-@Jack_Oster_2023].
+We built upon the research done by Jack and Oster [-@Jack_Oster_2023] in their paper by firstly utilising a different methodology.
+Jack and Oster had weighted their results by total district enrollment, thus, districts with larger enrollments will have a greater impact on the overall average than districts with smaller enrollments.
+In our paper, we do not weight it by enrollment, which allowed us to treat each district equally, regardless of its size.
+This offers a more balanced view of the educational landscape without overemphasising larger districts.
+We also enriched the analysis on the average virtual days by race by also considering the shares of White and Asian students, with the goal of better analysing the nuanced impact of racial demographics.
+Moreover, it is important to note that Jack and Oster did not mention their methodololgy for finding the virtual days for each county, given that data was only available for district.
+As previously mentioned, we found this metric by averaging across the districts found in each county.
 
@@
 #| message: false
-#| fig-cap: "Average days in virtual school by county broadband usage."
+#| fig-cap: "Average days in virtual school by county broadband usage"
+#| fig-pos: H
 ggplot(averaged_broadband, aes(x = QUANTILE_LABEL, y = average)) +
@@
 
-On the other hand, Figure \ref{fig-white} shows correlations [ADD DETAIL].
-In particular, within state, school districts with higher shares of Black and Hispanic students spent more of the 2020-2021 year in virtual schooling than those with lower shares of Black and Hispanics.
-Precisely the opposite trend is observed for white students.
-No significant variation in the days spent in virtual schooling is observed for Asian students.
-[ADD MORE DETAIL]
+Figure \ref{fig-broadband} shows that the average number of virtual days for counties that were on the lower end of broadband usage for their respective states was 20 days, whilst the average number of virtual days for the "High" counties was 24 days.
+This result is quite different from the one obtained by Jack and Oster [-@Jack_Oster_2023], whereby they found that the average for "Low" counties was 55 days, and "High" counties was 48 days.
+Thus, not only are the number of days for the quantitles different, but our analysis found that the counties with lower broadband had less virtual days.
+The discrepancy in data can arise due to numerous reasons.
+Firstly, we did not weight the data by enrollment.
+Secondly, we neglected the cells without any data, whereas Jack and Oster may have dealt with these in a different manner.
+Lastly, their method of finding average virtual days for a county may be different.
+The observed differences in virtual learning days between counties with varying broadband usage levels highlight potential disparities in access to and the usage of online education resources.
+This suggests that regions with lower broadband usage may face additional challenges in facilitating effective virtual learning experiences for students.
 
 ```{r}
-#| label: fig-white
+#| label: fig-race
 #| echo: false
@@
 #| message: false
-#| fig-cap: "Average days in virtual school by district-level race shares."
+#| fig-cap: "Average days in virtual school by district-level race shares"
+#| fig-pos: H
 
@@
 
+Figure \ref{fig-race} shows that the average number of virtual days for the districts classified as having a "High" share of black students spent 52 days in virtual schooling, and the "Low" districts spent 27 days.
+Jack and Oster [-@Jack_Oster_2023] found the number to be 56 days and 36 days respective.
+Our results for Hispanic students show that "High" districts had an average of 47 virtual days, and "Low" districts had an average of 30 virtual days.
+Jack and Oster found 53 days and 43 days respectively.
+Thus, our results are consistent with Jack and Oster in that we also observed that districts with a higher share of black students and a higher share of Hispanic students spent more days in virtual schooling.
+We find a larger discrepancy between "High" and "Low" district for both shares, primarily driven by the lower number of virtual days we calculated for the "Low" districts.
+
+We extended Jack and Oster's research by also looking at the shares of White and Asian students.
+We found that districts with "High" shares of white students had an average of 55 days virtual, whilst the "Low" districts had 23 virtual days.
+For Asian students, we found "High" districts had an average of 40 days virtual, whilst "Low" districts had an average of 38 days virtual.
+This variation can be considered insignificant.
+
 Taken together, in-person education was inequitably distributed across demographic characteristics, with more disadvantaged districts spending more time in virtual schooling [@Jack_Oster_2023].
-In particular, districts with less technological preparedness and higher shares of minorities -- especially Blacks and Hispanics -- were further disenfranchised by less access to in-person education.
+In particular, districts with less technological preparedness and higher shares of minorities  were further disenfranchised by less access to in-person education.
 This pattern likely reinforced educational inequities between vulnerable and more privileged groups.
@@
 First, schools (and students) with lower resources are less likely to have access to in-person instruction.
+The significant differences in virtual schooling days across districts categorized by racial demographics underscore systemic inequalities in access to in-person education.
+Our findings reveal that districts with higher proportions of Black and Hispanic students spent substantially more time in virtual schooling compared to those with lower proportions.
+This highlights a  disparity wherein more disadvantaged districts, often populated by minority students, face prolonged periods of virtual learning, potentially exacerbating existing educational inequities.
 Second, for such groups, the consequences of a lack of in-person instruction are more severe.

### 2024-02-14 paper/paper.qmd
Improved Figure 2

@@
             position = position_dodge(width = 0.9), 
-            vjust = -0.5, size = 3) +
+            vjust = -0.5, size = 2.75) +
   theme_minimal() +

### 2024-02-14 paper/paper.qmd
Improved Figure 2

@@
 Due to the US featuring the second-highest number of school closures, @tbl-daysclosed specifically depicts the top 5 nations in an attempt to evidence the US’ large number of closures relative to the rest of the world.
-In order to generate this figure, we employed the same cleaned dataset
+In order to generate this figure, we employed the same cleaned dataset used to create @fig-daysclosed.
+In this particular case, we simply grouped the data by country and summed the number of instances where a country registered a Covid Tracker score of 2 or 3 and reported a snippet of the generated table detailing each country and the number of school closures it faced in the aforementioned time frame.
 
@@
             position = position_dodge(width = 0.9), 
-            vjust = -0.5, size = 3) +
+            vjust = -0.5, size = 2.75) +
   labs(x = "Quantile", y = "Average Days Virtual") +

### 2024-02-14 scripts/00-simulate_data.R
Simulate Data

@@ -1,13 +1,13 @@
 #### Preamble ####
-# Purpose: Simulates various data sets 
+# Purpose: Simulates 3 data sets 
 # Author: Krishiv Jain, Julia Kim, Abbass Sleiman
 # Date: 12 February 2024
-# Contact: 
+# Contact: krishiv.jain@mail.utoronto.ca, abbass.sleiman@mail.utoronto.ca, juliaym.kim@mail.utoronto.ca
 # License: MIT
+# Pre-requisites: none
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### SIMULATE DATA ####
 
@@ -51,6 +51,4 @@ simulated_data2$broadband_usage |> class() == "numeric"
 is.wholenumber <- function(x, tol = .Machine$double.eps^0.5) abs(x - round(x)) < tol
 is.wholenumber(simulated_data2$white_students)
 is.wholenumber(simulated_data2$black_students)
-
-print("hello")
 

### 2024-02-14 scripts/00-simulate_data.R
Changes

@@ -46,7 +46,7 @@ simulated_data2$white_students |> class() == "numeric"
 simulated_data2$black_students |> class() == "numeric"
 simulated_data2$broadband_usage |> class() == "numeric"
 
-## Check that first and third columns only have whole numbers ##
+## Check that the columns only have whole numbers ##
 #Based on: https://stackoverflow.com/q/3476782/23271634
 is.wholenumber <- function(x, tol = .Machine$double.eps^0.5) abs(x - round(x)) < tol
 is.wholenumber(simulated_data2$white_students)

### 2024-02-14 scripts/03-test_data.R

@@ -1,15 +1,25 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Testing our data sets 
+# Author: Krishiv Jain, Julia Kim, Abbass Sleiman
+# Date: 12 February 2024
+# Contact: krishiv.jain@mail.utoronto.ca, abbass.sleiman@mail.utoronto.ca, juliaym.kim@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Downloaded the data files through 01-download_data.R
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
-#### Test data ####
+#### TESTING DATA FOR FIGURE 2 ####
+
+##Check the minimum number is equal, or greater than, 0 ##
+#Based on: https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html#simulate
+broadband_data$`COUNTY ID` |> min() >= 0
+
+##Check the class of the column is numeric##
+broadband_data$`COUNTY ID` |> class() == "numeric"
+race_data$enrollment |> class() == "numeric"
+
+
+
+

### 2024-02-14 scripts/00-simulate_data.R
Added information

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Simulates 3 data sets 
 # Author: Krishiv Jain, Julia Kim, Abbass Sleiman
-# Date: 12 February 2024
+# Date: 14 February 2024
 # Contact: krishiv.jain@mail.utoronto.ca, abbass.sleiman@mail.utoronto.ca, juliaym.kim@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: none

### 2024-02-14 scripts/01-download_data.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
+# Purpose: Downloads the required raw data to use in data cleaning
 # Author: Krishiv Jain, Julia Kim, Abbass Sleiman
-# Date: 12 February 2024
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Date: 14 February 2024
+# Contact: krishiv.jain@mail.utoronto.ca, abbass.sleiman@mail.utoronto.ca, juliaym.kim@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Follow instructions in README to download data on race enrollment
 
 
 #### Workspace setup ####

### 2024-02-14 scripts/02-data_cleaning.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the various raw data sets that have been used prior to analysis and creation of figures
+# Author: Krishiv Jain, Julia Kim, Abbass Sleiman
+# Date: 14 February 2024
+# Contact: krishiv.jain@mail.utoronto.ca, abbass.sleiman@mail.utoronto.ca, juliaym.kim@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: run 01-download_data.R, and download the relevant data as outlined in the README. 
 
 #### Workspace setup ####
 library(tidyverse)
@@ -17,6 +16,7 @@ library(here)
 library(haven)
 library(labelled)
 
+#### FIGURE 1 DATA CLEANING - REGION DATA ####
 
 #### Clean region data ####
 raw_region_data <- read_csv("data/raw_data/region_data.csv")
@@ -52,31 +52,7 @@ cleaned_region_data <- country_region_data[cleaned_region_data, on = "country_na
 
 cleaned_region_data <- as.data.frame(cleaned_region_data)
 
-
-#### Clean test score data ####
-raw_test_score_data <- read_csv("data/raw_data/scores_lm_demographics.csv")
-
-cleaned_test_score_data <- raw_test_score_data |>
-  janitor::clean_names() |>
-  select(
-    share_inperson,
-    subject,
-    change_2019_2021,
-    change_2018_2019,
-    change_2017_2018,
-    enrollment,
-    share_enroll_white,
-    share_enroll_black,
-    share_enroll_hispanic
-  )
-
-#### Save data ####
-fwrite(cleaned_region_data, "data/analysis_data/cleaned_region_data.csv", row.names = FALSE)
-write_csv(cleaned_test_score_data, "data/analysis_data/cleaned_test_score_data.csv")
-
-
 #### FIGURE 2 DATA CLEANING - AVERAGE VIRTUAL DAYS BY CHARACTERISTIC ####
-
 
 # CLEANING BROADBAND RAW DATA #
 
[…]

### 2024-02-14 scripts/03-test_data.R

@@ -4,7 +4,7 @@
 # Date: 12 February 2024
 # Contact: krishiv.jain@mail.utoronto.ca, abbass.sleiman@mail.utoronto.ca, juliaym.kim@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Downloaded the data files through 01-download_data.R
+# Pre-requisites: Downloaded the data files through 01-download_data.R and through the instructions in the README
 
 
 #### Workspace setup ####

### 2024-02-14 scripts/01-download_data.R
Changes Made

@@ -13,32 +13,6 @@ library(tidyverse)
 library(arrow)
 
 
-#### DATASETS FOR FIGURE 2 ####
-
-## Download Data sets ##
-
-zip_file <- "/Users/krishiv/Documents/New Folder STA302/nces_district_enrollment_2018_2020.csv.zip"
-# Unzip the file
-data <- unzip(zip_file)
-race_data <- read_csv(data[1], col_types = cols())
-
-broadband_data <-
-  read_csv(
-    file = "data/raw_data/broadband_data_2020October.csv",
-    show_col_types = FALSE
-  )
-
-shares_data <-
-  read_csv(
-    file = "data/raw_data/District_Overall_Shares.csv",
-    show_col_types = FALSE
-  )
-
-county_district_data <-
-  read_dta(
-    file = "data/raw_data/nces_district_directory_2018.dta",
-  )
-
 #### DATASETS FOR FIGURE 3 ####
 
 ## Download Data ##

### 2024-02-14 scripts/02-data_cleaning.R

@@ -52,6 +52,7 @@ cleaned_region_data <- country_region_data[cleaned_region_data, on = "country_na
 
 cleaned_region_data <- as.data.frame(cleaned_region_data)
 
+
 #### FIGURE 2 DATA CLEANING - AVERAGE VIRTUAL DAYS BY CHARACTERISTIC ####
 
 # CLEANING BROADBAND RAW DATA #
@@ -81,17 +82,17 @@ broadband_data <- broadband_data |>
 
 ## Read in the raw data ##
 
-zip_file <- "/Users/krishiv/Documents/New Folder STA302/nces_district_enrollment_2018_2020.csv.zip"
-# Unzip the file
-data <- unzip(zip_file)
-race_data <- read_csv(data[1], col_types = cols())
+race_data <- read_dta(
+  file = "/Users/krishiv/Documents/New Folder STA302/Raw/nces_district_enrollment_2018_2020.dta")
 
-#Only keeping data on total for each race
+#Only keeping data for the year 2020, and for total for each race
 race_data$grade <- as_factor(race_data$grade)
 race_data$race <- as_factor(race_data$race)
-## The number 99 represents the value for Total
-race_data <- race_data[race_data$grade == "99", ] 
-race_data <- race_data[!race_data$race == "99", ]
+race_data$year <- as_factor(race_data$year)
+
+race_data <- subset(race_data, year == "2020")
+race_data <- subset(race_data, grade == "Total")
+race_data <- subset(race_data, race != "Total")
 race_data$leaid <- as.numeric(race_data$leaid)
 
 race_data <- race_data |>
@@ -116,7 +117,7 @@ combined_data <- combined_data |>
 
 
 # White Share #
-white_share <- combined_data[combined_data$race == "1", ]
+white_share <- combined_data[combined_data$race == "White", ]
 
 ## Creating Quantiles 
 white_share <- white_share |>
@@ -128,7 +129,7 @@ white_share <- white_share |>
 
 
 # Black Share #
-black_share <- combined_data[combined_data$race == "2", ]
+black_share <- combined_data[combined_data$race == "Black", ]
 
 ## Creating Quantiles 
 black_share <- black_share |>
@@ -139,7 +140,7 @@ black_share <- black_share |>
   mutate(QUANTILE_LABEL = ifelse(QUANTILE == 1, "Low", "High"))
 
 # Asian Share #
[…]

### 2024-02-14 paper/paper.qmd
Made edits to the Data & results section

@@
 (3) School closures contributed significantly to the decline in students' pass rates in mathematics and ELA in the 2020-2021 school year.
-Changes in ELA scores were smaller than mathematics scores, but significantly larger in districts with larger populations of students who are Black, Hispanic, English Language Learners (ELL) or eligible for free and reduced price lunch (FRPL).
+Changes in ELA scores were smaller than mathematics scores, but significantly larger in districts with larger populations of students who are Black or Hispanic.
 
@@
 
-This dataset is obtained from the Oxford COVID-19 Policy Tracker, a project that collected information on COVID-19 policy measures for the years 2020, 2021 and 2022 [@Hale].
-For 185 countries, the dataset assigns a daily Tracker score for each day between January 1st, 2020, and December 31st, 2022.
-Note that a Tracker score is defined as an integer value between 0 and 3, with a value of 2 or 3 denoting a school closure [@Jack_Oster_2023].
+This dataset is made available by the Oxford COVID-19 Policy Tracker, a project that collected information on COVID-19 policy measures in 185 countries for the years 2020, 2021 and 2022 [@Hale].
+Data were collected by a team of over 1500 volunteers at Oxford's Blavatnik School of Government from publicly available sources-- such as government press releases, briefings, international organisation reports, and credible news articles.
+For 185 countries, this dataset assigns a daily Tracker score between January 1st, 2020, and December 31st, 2022.
+This daily Tracker score is a composite integer measure of nine response metrics that evaluate the stringency of a country's COVID-19 response [@Hale]; in particular, a value of 2 or 3 denotes a school closure [@Jack_Oster_2023].
 
@@
 
-This dataset is a csv version of `scores_lm_demographics.dta` obtained from the final dataset found in the data repository for “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@TestScore].
-This dataset contains extensive information on various school districts across the aforementioned 11 states, including information on the shares of students by race, the share of schooling done in-person, and changes in average test scores in both Math and ELA from the previous year across the years 2018-2019 and 2021-2022 (no information is present regarding the year 2020 as all standardised assessments were cancelled due to the pandemic).
+This dataset is a `.csv` version of `scores_lm_demographics.dta`, obtained from the replication package of “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2], published in the American Economic Association’s *AER: Insights* [@citeAEA].
+Data are obtained from the Departments of Education of the aforementioned 11 US states, each of whom collect data from constituent schools, school boards and school authorities [@DeptsEd].
+The dataset contains extensive information on school districts across these 11 states, including shares of students by race, shares of schooling done in-person, and changes in average test scores in both Mathematics and ELA from the previous year across the years 2018-2019 and 2021-2022.
+Note no information on test scores are available for 2020, as all standardised assessments were cancelled due to the pandemic.
 
@@
 
-@fig-daysclosed depicts the average number of school closures by region, as defined by the World Bank, between the start of January 2020 and the end of December 2021.
-In particular, it employs data on 185 countries, each of which is assigned its particular region, and provides the average number of school closures for nations in each region between the aforementioned time frame.
+@fig-daysclosed shows the average number of school closures by region between the start of January 2020 and the end of December 2021.
+The Oxford COVID-19 Policy Tracker [@Hale] assigns a score to each of the 185 countries and the World Bank [@worldbank2023] provides a one-to-one correspondence between the country and the broader region to which it belongs: sub-Saharan Africa, Europe and Central Asia, and so forth.
+Details on how this figure was achieved follow.
 
-In order to achieve this, we first created the dataset `country_region.csv` which assigns each of the 185 countries present in the primary dataset, `region_data.csv`, its respective region.
-This was done since `region_data.csv` did not feature each nation's region, and as such, by creating the `country_region.csv` dataset we were able to 'merge' the two sets of information so that the final product featured all information regarding the Covid Tracker score of each country one each day, as well as the region the country is in.
+Since `region_data.csv` did not feature the region to which each of the 185 countries belonged, we created the dataset `country_region.csv`.
+This assigned to each country its corresponding region, as defined by the World Bank [@worldbank2023].
+In doing so, we could have information both on the COVID-19 Tracker score of each country for each day, as well as the region in which the country is located.
 
-We initially cleaned the data in `region_data.csv` by omitting information from the year 2022 in a bid to replicate and examine the internal validity of the work by Jack and Oster who also omitted the year 2022 from their figure [@Jack_Oster_2023].
-From there, only the columns of interest were kept which detailed the country name, (empty) region name, date, and Covid Tracker score.
-We also found a minor spelling error of the Faroe Islands which were incorrectly spelled as Faeroe Islands which we also amended in the cleaning process.
-From here, we simply merged the cleaned `region_data.csv` with the regions listed in `country_region.csv` in order fill in the empty region names present in the original dataset.
+We followed the workflow of Jack and Oster [@Jack_Oster_2023], by likewise omitting in `regions.csv` all information from the year 2022.
+Only columns of interest to the analysis were then kept, including the country name, (empty) region name, date, and COVID-19 Tracker score.
+We also identified and amended a minor spelling error in the name of `Faroe Islands`, originally misspelled as `Faeroe Islands`.
+Thereafter, we merged the cleaned `region_data.csv` with the regions listed in `country_region.csv` in order fill in the empty region names present in the original dataset.
 
-With the cleaned dataset, we were able to create the figure detailing the average days closed by region by first grouping the cleaned data by region name and country, then summing the number of instances where a Tracker score of 2 or 3 was present (as this defines a school closure as per Jack and Oster's work [@Jack_Oster_2023]).
-From there, we calculated the mean number of days closed by region by computing the average number of days closed for all nations in a given region.
+We regrouped the cleaned data by region name and country, summed the number of instances where a Tracker score of 2 or 3 was present (as this defines a school closure, as per Jack and Oster [-@Jack_Oster_2023]).
+We then calculated the mean number of days closed by region by computing the average number of days closed for all countries in a given region.
 
-Then, in an attempt to garner a deeper understanding of how the US compares to other nations with regards to their COVID-19 schooling policies and measures, we employ @tbl-daysclosed which provides a snippet of the top 5 countries by number of school closures between the start of January 2020 and the end of December 2021.
-Due to the US featuring the second-highest number of school closures, @tbl-daysclosed specifically depicts the top 5 nations in an attempt to evidence the US’ large number of closures relative to the rest of the world.
-In order to generate this figure, we employed the same cleaned dataset used to create @fig-daysclosed.
-In this particular case, we simply grouped the data by country and summed the number of instances where a country registered a Covid Tracker score of 2 or 3 and reported a snippet of the generated table detailing each country and the number of school closures it faced in the aforementioned time frame.
+To gain an understanding of how COVID-19 schooling measures implemented in the United States compared with those elsewhere in the world, we created @tbl-daysclosed.
+This table provides a snippet of the top 5 countries with the highest number of school closures in 2020-2021, featuring the US in second place.
+We used the same cleaned dataset as before, regrouped data by country, summed the number of instances where a country registered a COVID-19 Tracker score of 2 or 3 and isolated the top 5 countries where these numbers were the largest.
 
@@
 
-The purpose of Figures \ref{fig-broadband} and \ref{fig-race} is to explore the correlations between certain district and county characteristics, and the average number of virtual school days for the respective district or county.
-Specifically, we look at broandband usage by county, and the shares of four races (White, Black, Asian, Hispanic) by district.
-For each county or district, we assign "high" or "low" depending on if their level for the characteristics being explored is above or below their state's median, respectively.
-By doing so, we allow for the results to be driven by a variation within states, as opposed to variation across states.
+Figures \ref{fig-broadband} and \ref{fig-race} explore correlations between the average number of school closures with two county- and district-level characteristics, these being county-level broadband usage and district-level race shares of four major ethnic classes-- White, Black, Asian and Hispanic.
+For both demographic characteristics, we followed Jack and Oster's [-@Jack_Oster_2023] work, by assigning to each county or district a quantile of "High" or "Low", depending on whether its levels for said characteristic were above or below the state's median, respectively.
+By doing so, we allowed the results to be driven by a variation within states, as opposed to variation across states.
 
-We start by using `nces_district_enrollment_2018_2020.csv.zip`.
-As previously mentioned, this data set splits the total enrollment into various categories.
-We start by converting the columns into the numeric class as appropriate.
-Some enrollment cells did not have a value, indicating that data was not collected for that specific metric.
-These occurred a handful of times for certain races within certain districts.
-These NAs were replaced with 0s.
-For our paper, we are concerned specifically with race.
-Thus, for each district, we calculate the total number of White, Black, Asian, and Hispanic students enrolled.
-Given the structure of the data, this is done by summing the total enrollment per race for Male and Female for each district.
-Next the total enrollment for the whole district was calculated, before then calculating the share of total enrollment that each race comprises.
+We drew on the `nces_district_enrollment_2018_2020.csv.zip` dataset, which reports the total student enrollment by grade, sex and ethnic class.
+A handful of enrollment cells had no value, which were subsequently replaced by 0s.
+Being specifically concerned with race data, we calculated for each district the total number of White, Black, Asian, and Hispanic students enrolled.
+We then separated data according to race, classifying districts as "High" or "Low", depending on whether their race share was above or below their state's median.
+Thereafter, we matched each district with those contained in `District_Overall_Shares.csv`, so as to obtain information on its average number of days closed.
+We found there was some discrepancy, with the number of districts in `nces_district_enrollment_2018_2020.csv.zip` being larger than that in `District_Overall_Shares.csv`, which we resolved by dropping all instances of districts not present in both datasets.
+After merging these two datasets, we averaged the number of virtual days across districts, classified in the "High" and "Low" quantiles.
+This resulted in four data sets, one for each race considered.
 
-The data above was then separated into different tables for each race.
-For each race, we then classified the district as either "High" or "Low" depending on if their share was above or below their respective state's median.
-Using this data, we were now interested in the number of virtual days that each of these districts had.
-This information was available in the `District_Overall_Shares.csv` data set.
-Given that the US average number of school days per year is 180, the percentage for share_virtual was multiplied by 180 for each district.
+Here, we differed from the methodology employed by Jack and Oster [-@Jack_Oster_2023] in one specific way.
+In their workflow, Jack and Oster [-@Jack_Oster_2023] also weighted the average number of days of virtual school by total district enrollment.
+In this way, districts with larger enrollments had greater impact on the overall average than those with smaller enrollments.
+In our analysis, we omitted such weighting, instead treating each district equally, regardless of size.
+This offered a more balanced view of the educational landscape, without overemphasising larger districts.
 
-Next, the aforementioned data for each race that separated the districts into quantiles, and the data for the number of virtual days per district were merged.
-This results in some NAs being produced since the data set on race had more districts than the data on the number of virtual days.
-Given the lack of data, all NAs were droppped.
-Finally, the number of virtual days for the "High" quantile and the "Low" quantile were averaged.
-This results in four data sets, one for each race considered.
-
-To calculate the information regarding broadband, we started with the `broadband_data_2020October.csv` data set.
-Only columns that were necessary were kept, and the columns were converted to the numeric class as appropriate.
-Each county was then classified as either "High" or "Low" depending on if their share was above or below their respective state's median.
-A single county contains multiple districts, and since our data regarding the number of virtual days was based on district, the data was averaged across districts for each county.
-`nces_district_directory_2018.dta` provided information on which county each district belonged to, and was merged with the previous data that calculated the average number of virtual days for each district, before then calculating the average number of virtual days for each county.
-Finally, we average the number of virtual days for the counties labelled "High" and "Low."
+To address broadband usage, we drew on `broadband_data_2020October.csv` and `nces_district_directory_2018.dta`.
+With the former, we obtained the broadband usage across all US districts; with the latter, we regrouped all districts belonging to each US county and averaged their broadband usages.
+We then assigned to each county a quantile of "High" or "Low", according to whether their broadband usage was above or below their respective state's median.
+As before, we used `District_Overall_Shares.csv` to determine the average number of days in virtual schooling for all counties labelled as "High" and "Low."
 
@@
 
+@fig-mathscoresbyonline and @fig-elascoresbyonline explore the relationship between the share of in-person learning and change in test scores in standardised tests in Mathematics and ELA respectively.
+In particular, they examine changes in test scores across 3 years (2021, 2019, and 2018) from the year prior (excepting the case of 2021, where changes are relative to 2019).
+
+To achieve this, we made use of the `scores_lm_demographics.dta` dataset.
+However, we first converted the dataset into a `.csv` file, `scores_lm_demographics.csv`, to be used in the cleaning and analysis processes.
+From there, we cleaned the data by only selecting the columns of interest, those being the share of in-person learning, the subject of the test, the changes across each of the three years of interest, the number of students enrolled in each school district, and the shares of each of the three races of interest (White, Black, Asian and Hispanic).
+To generate the aforementioned figures, we first calculated the total number of students enrolled across all school districts.
+We then filtered by subject, so as to deal with one subject at a time when creating the two figures.
+We proceeded by defining four in-person categories of 0-25%, 25-50%, 50-75%, and 75-100%, after which we mutated our filtered data by assigning each school district one of the four categories.
+We then proceeded to group the data by year (one of the three previously mentioned), and by in-person category so that we were able to calculated the weighted average change in test scores for each in-person category in each year.
+Finally, we ungrouped the data to calculate the overall, and thus un-weighted, average change in test scores for each of the three years.
+This was repeated for both Mathematics and ELA test scores by simply changing the filtering of the data to only include one of the two.
+
+@fig-mathscoresrace, @fig-elascoresrace examine these test score changes from a different lens.
+Instead of considering the share of in-person learning, it explores the possibility of a systematic difference in the changes in test scores based on the relative share of various races.
+In particular, the figures examine the correlation between changes in test scores and the relative quantile share of White, Black, and Hispanic students which is one of "Low", "Middle" or "High".
+As before, this is also done for each of the three years of interest for each of the three races.
+
+To generate this graph, we once again employed the cleaned `scores_lm_demographics.csv` file as was used to generate @fig-mathscoresbyonline and @fig-elascoresbyonline.
+We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the three quantiles, "Low", "Middle", and "High", for each of the three races.
+From there, we grouped the data by year and quantile for each of the three races, then calculated the weighted average change in test scores for each subject and quantile, across all races and years.
+From there, we simply combined the summary statistics for each of the races and their respective quantiles, and showcased them in the figures, differentiating by race through shape, and year through color.
+
 # Results
-Data from the Oxford COVID-19 Policy Tracker [@Hale] and World Bank [@worldbank2023] were used to determine the average number of school closures by regions worldwide between January 2020-December 2021.
-We reconstruct this result in Figure \ref{fig-daysclosed} and extract the top 5 countries with the highest average number of closures in Table \ref{tbl-daysclosed}.
-Figure \ref{fig-daysclosed} shows that North America had the highest at 535 days, which is around 73% of the two-year period, whilst sub-Saharan Africa had the least at 300 days, or around 38% of the two-year period.
-Thus, countries with the longest closures spent more than twice the amount of time in virtual schooling compared to those with the shortest closures.
+
+## Extent of School Closures in the United States and the World
 
@@
 
-In studying individual countries, Table \ref{tbl-daysclosed} shows that the United States faced the second highest number of closures worldwide during this two-year period, with a mean number of 667 days.
-This is, in fact, significantly higher than the mean number of closures worldwide, determined to be $356 \pm 175$ days.
-Thus, relative to the global picture, the extent of school closures in North America and, in particular, the United States appears to be significantly more prolonged.
+Data from the Oxford COVID-19 Policy Tracker [@Hale] and World Bank [@worldbank2023] were used to determine the average number of school closures by regions worldwide between January 2020-December 2021.
+We reconstruct this result in Figure \ref{fig-daysclosed} and extract the top 5 countries with the highest average number of closures in Table \ref{tbl-daysclosed}.
+Figure \ref{fig-daysclosed} shows that North America had the highest at 535 days, which is around 73% of the two-year period, whilst sub-Saharan Africa had the least at 300 days, or around 38% of the two-year period.
+Thus, countries with the longest closures spent more than twice the amount of time in virtual schooling compared to those with the shortest closures.
 
@@
 
-Moreover, data from CSDH [@citeraw1], NCES [@citeraw2] and Microsoft [@kahan2020usbroadband] were used to delve deeper and analyse correlations between the average number of virtual schools days, and certain demographic characteristics, and Figures \ref{fig-broadband} and \ref{fig-race} were created.
-As discussed previously, Figure \ref{fig-broadband} shows the average number of virtual days for counties that were classified as "Low" and those classified as "High," whilst Figure \ref{fig-race} shows the average for districts.
-The classification of districts and counties was explained in @sec-datacleaning2.
+In studying individual countries, Table \ref{tbl-daysclosed} shows that the United States faced the second highest number of closures worldwide during this two-year period, with a mean number of 667 days.
+This is, in fact, significantly higher than the mean number of closures worldwide, determined to be $356 \pm 175$ days.
+Thus, relative to the global picture, the extent of school closures in North America and, in particular, the United States appears to be significantly more prolonged.
 
-We built upon the research done by Jack and Oster [-@Jack_Oster_2023] in their paper by firstly utilising a different methodology.
-Jack and Oster had weighted their results by total district enrollment, thus, districts with larger enrollments will have a greater impact on the overall average than districts with smaller enrollments.
-In our paper, we do not weight it by enrollment, which allowed us to treat each district equally, regardless of its size.
-This offers a more balanced view of the educational landscape without overemphasising larger districts.
-We also enriched the analysis on the average virtual days by race by also considering the shares of White and Asian students, with the goal of better analysing the nuanced impact of racial demographics.
+## Average Number of School Closures by Local Demographic Characteristics
+
+Data from CSDH [@citeraw1], NCES [@citeraw2] and Microsoft [@kahan2020usbroadband] were used to determine correlations between the average number of virtual schools days, and certain demographic characteristics.
+We reconstruct these results in Figures \ref{fig-broadband} and  \ref{fig-race}.
+These show the average number of virtual days for counties or districts that have "High" or "Low" levels of broadband usage and various race shares, respectively.
+Note that we enriched Jack and Oster's [-@Jack_Oster_2023] analysis on race by also considering the shares of White and Asian students, so as to better understand the nuanced impact of racial demographics.
 Moreover, it is important to note that Jack and Oster did not mention their methodololgy for finding the virtual days for each county, given that data was only available for district.
@@
 This result is quite different from the one obtained by Jack and Oster [-@Jack_Oster_2023], whereby they found that the average for "Low" counties was 55 days, and "High" counties was 48 days.
-Thus, not only are the number of days for the quantitles different, but our analysis found that the counties with lower broadband had less virtual days.
+Thus, not only are the number of days for the quantiles different, but our analysis found that the counties with lower broadband had less virtual days.
 The discrepancy in data can arise due to numerous reasons.
@@
 
-Finally, data from ...
-was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021.
-We again reconstruct and extend the data...
-
-[ADD DETAIL].
-
-Panels A and B show the scores in mathematics and in ELA, respectively. [EXPLAIN FIGURE & SYMBOLS]
-
-Consistent with Jack and Oster [-@Jack_Oster_2023], our analysis shows a significant decline in pass rates from the 2018-2019 to the 2020-2021 school year.
-In particular, pass rates in mathematics and ELA declined by 12.8 and 6.8 percentage points, respectively.
-The discrepancy between these two subjects is consistent with much of the current economic literature, which shows mathematics scores to be more sensitive to schooling differences [@betts2011effect; @angrist].
-
-... Thus, we find that in-person learning has significantly higher benefits for districts with larger shares of Black and Hispanic students.
+## Standardised Test Assessment Scores
 
@@
 #| fig-cap: "Test score by percent online (change)"
+#| fig-pos: H
 
@@
 ```
+
+Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@TestScore] was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021.
+
+[ADD DETAIL].
+
+Panels A and B show the scores in mathematics and in ELA, respectively. [EXPLAIN FIGURE & SYMBOLS]
+
+Consistent with Jack and Oster [-@Jack_Oster_2023], our analysis shows a significant decline in pass rates from the 2018-2019 to the 2020-2021 school year.
+In particular, pass rates in mathematics and ELA declined by 12.8 and 6.8 percentage points, respectively.
+The discrepancy between these two subjects is consistent with much of the current economic literature, which shows mathematics scores to be more sensitive to schooling differences [@betts2011effect; @angrist].
+
+... Thus, we find that in-person learning has significantly higher benefits for districts with larger shares of Black and Hispanic students.
 
@@
 ```{r}
-#| label: fig-testscoresela
+#| label: fig-elascoresrace
 #| echo: false
@@
 (3) During the 2020-2021 school year, students' pass rates on standardised assessments declined by 12.8 percentage points in mathematics and 6.8 in ELA.
-Declines were more severe in more disadvantaged districts, *i.e.*, those with higher proportions of racial minorities, ELL and FRPL students.
+Declines were more severe in more disadvantaged districts, *i.e.*, those with higher proportions of racial minorities.
 
@@
 
-Moreover, stratifying test assessment scores by district-level race, ELL and FRPL shares may be problematic.
+Moreover, stratifying test assessment scores by district-level race may be problematic.
 The underperformance of vulnerable populations in relation to more privileged populations may reinforce discriminatory notions about their intellectual ability.
@@
 
-What is more, Jack et al.'s [-@Jack2] standardised assessments data excludes information about the corresponding broadband usage and unemployment rates by district.
-It instead includes data of the corresponding shares of ELL and FRPL students by district.
-This discrepancy prevents us from telling a full story as to how the pass rates of schools located in districts with lower broadband usage and employment rates, known to face more days of school closed than the national average, were affected.
-We also question whether the shares of FRPL students are a good estimator of the shares of students with low socioeconomic status.
+What is more, Jack et al.
+[-@Jack_Oster_2] standardised assessments data excludes information about the corresponding broadband usage and test scores of Asians by district.
+It instead includes data of the corresponding shares of ELL and FRPL students by district, two demographic characteristics we did not consider in our analysis.
+This discrepancy prevents us from telling a full story as to how the pass rates of schools located in districts with lower broadband usage and higher shares of Asian minorities, the former of which is known to face more days of school closed than the national average, were affected.
+We raise a question of whether the shares of FRPL students were a good estimator of the shares of students with low socioeconomic status.
 Though FRPL enrollment are widely used in education research as an indicator of student poverty, there is emerging literature that it serves as a poor proxy for poverty [@Fazlul2023].
@@
 [-@Fazlul2023] show that FRPL rates greatly exceed what would be expected from stated income thresholds for program participation by 35 to 50%.
-This suggests that the shares of FRPL students per district may not be the most optimal estimator of student poverty, and that more insightful conclusions could have been obtained in examining instead, for instance, the shares of students in low-income households per district.
+This suggests that the shares of FRPL students per district may not be the most optimal estimator of student poverty in the Jack et al.
+[-@Jack_Oster_2] paper, and that more insightful conclusions could have been obtained in examining instead, for instance, the shares of students in low-income households per district.
 

### 2024-02-14 scripts/02-data_cleaning.R
Make Changes

@@ -165,7 +165,7 @@ hispanic_share <- hispanic_share |>
 
 shares_data <-
   read_csv(
-    file = "/Users/krishiv/Downloads/302 Paper 2/193523-V1/Raw/District_Overall_Shares.csv",
+    file = "data/raw_data/District_Overall_Shares.csv",
     show_col_types = FALSE
   )
 
@@ -178,7 +178,7 @@ shares_data$NCESDistrictID <- as.numeric(shares_data$NCESDistrictID)
 
 county_district_data <-
   read_dta(
-    file = "/Users/krishiv/Downloads/302 Paper 2/193523-V1/Raw/nces_district_directory_2018.dta",
+    file = "data/raw_data/nces_district_directory_2018.dta",
   )
 
 county_district_data <- select(county_district_data, leaid, county_code)

### 2024-02-14 scripts/02-data_cleaning.R
Added another variable to one of the datasets

@@ -275,7 +275,8 @@ cleaned_test_score_data <- raw_test_score_data |>
     enrollment,
     share_enroll_white,
     share_enroll_black,
-    share_enroll_hispanic
+    share_enroll_hispanic,
+    state
   )
 
 #### Save data ####

### 2024-02-14 paper/paper.qmd
Amended Paper
Updated 2 of the figures and their labels

@@
 ggplot(combined_summary_data, aes(x = weighted_avg_change_pass * 100, 
-                                                    y = quantile_level, color = year_group, shape = race)) +
+                                                    y = quantile_level, shape = year_group, color = race)) +
   geom_point(size = 2.85, position = position_jitter(height = 0.1)) + 
@@
        title = "Average Change in Pass Rate by Race and Quantile") +
-  scale_color_discrete(labels = c("Spring 2018", "Spring 2019", "Spring 2021")) +
-  labs(color = "Year Category", shape = "Race") +
+  scale_color_discrete(labels = c("Black", "Hispanic", "White")) +
+  scale_shape_discrete(labels = c("Spring 2018", "Spring 2019", "Spring 2021")) +
+  labs(shape = "Year Category", color = "Race") +
   theme_minimal()
@@
 ggplot(combined_summary_data, aes(x = weighted_avg_change_pass * 100, 
-                                                   y = quantile_level, color = year_group, shape = race)) +
+                                                   y = quantile_level, shape = year_group, color = race)) +
   geom_point(size = 2.85, position = position_jitter(height = 0.1)) + 

### 2024-02-14 scripts/02-data_cleaning.R

@@ -275,8 +275,7 @@ cleaned_test_score_data <- raw_test_score_data |>
     enrollment,
     share_enroll_white,
     share_enroll_black,
-    share_enroll_hispanic,
-    state
+    share_enroll_hispanic
   )
 
 #### Save data ####

### 2024-02-14 paper/paper.qmd
Recommitted newest updats

@@
 
-To address broadband usage, we drew on `broadband_data_2020October.csv` and `nces_district_directory_2018.dta`.
-With the former, we obtained the broadband usage across all US districts; with the latter, we regrouped all districts belonging to each US county and averaged their broadband usages.
+Next, we drew on `broadband_data_2020October.csv` and `nces_district_directory_2018.dta` to determine correlations of days spent in virtual schooling with broadband usage.
+With the former dataset, we obtained the broadband usage across all US districts; with the latter, we regrouped all districts belonging to each US county and averaged their broadband usages.
 We then assigned to each county a quantile of "High" or "Low", according to whether their broadband usage was above or below their respective state's median.
-As before, we used `District_Overall_Shares.csv` to determine the average number of days in virtual schooling for all counties labelled as "High" and "Low."
+Jack and Oster [-@Jack_Oster_2023] did not mention their methodology to find the number of virtual days for each county, given that data were available only at the district-level.
+To remedy this, we simply regrouped the districts in `District_Overall_Shares.csv` into their respective counties and averaged the number of virtual days across all districts for each county labelled as "High" and "Low."
 
@@
 Note that we enriched Jack and Oster's [-@Jack_Oster_2023] analysis on race by also considering the shares of White and Asian students, so as to better understand the nuanced impact of racial demographics.
-Moreover, it is important to note that Jack and Oster did not mention their methodololgy for finding the virtual days for each county, given that data was only available for district.
-As previously mentioned, we found this metric by averaging across the districts found in each county.
 
@@
 #| message: false
-#| fig-cap: "Average days in virtual school by county broadband usage"
+#| fig-cap: "Average days in virtual school by county broadband usage."
 #| fig-pos: H
@@
 
-Figure \ref{fig-broadband} shows that the average number of virtual days for counties that were on the lower end of broadband usage for their respective states was 20 days, whilst the average number of virtual days for the "High" counties was 24 days.
-This result is quite different from the one obtained by Jack and Oster [-@Jack_Oster_2023], whereby they found that the average for "Low" counties was 55 days, and "High" counties was 48 days.
-Thus, not only are the number of days for the quantiles different, but our analysis found that the counties with lower broadband had less virtual days.
-The discrepancy in data can arise due to numerous reasons.
-Firstly, we did not weight the data by enrollment.
-Secondly, we neglected the cells without any data, whereas Jack and Oster may have dealt with these in a different manner.
-Lastly, their method of finding average virtual days for a county may be different.
-The observed differences in virtual learning days between counties with varying broadband usage levels highlight potential disparities in access to and the usage of online education resources.
-This suggests that regions with lower broadband usage may face additional challenges in facilitating effective virtual learning experiences for students.
+Figure \ref{fig-broadband} shows the average number of days with school closed in counties with "Low" and "High" broadband usage to be 20 and 24, respectively.
+Note this result significantly differs to the one obtained by Jack and Oster [-@Jack_Oster_2023], who determined the average for "Low" and "High" counties to be 55 and 48 days, respectively.
+Moreover, our numbers point to an opposite trend-- that counties with lower broadband usage had fewer virtual days.
+The discrepancy in data can arise due to a number of important reasons.
+First, we did not weight the data by enrollment.
+Second, whilst we chose to neglect all cells with missing data, Jack and Oster [-@Jack_Oster_2023] may have approached this problem in a different manner, which they did not document.
+Lastly, our methods to find the average number of virtual days for a county may differ to theirs.
+As noted previously, we regrouped districts into counties, averaging across the number of virtual days for districts into counties, whereas Jack and Oster [-@Jack_Oster_2023] left no note to document their own approach.
+
+Our conclusions still point to the fact that potential disparities in access to and the usage of online education resources exist.
+The observed differences in virtual learning days with the level of broadband usage suggests that regions with less technological preparedness may face additional challenges in accessing effective virtual learning experiences.
 
@@
 #| message: false
-#| fig-cap: "Average days in virtual school by district-level race shares"
+#| fig-cap: "Average days in virtual school by district-level race shares."
 #| fig-pos: H
@@
 
-Figure \ref{fig-race} shows that the average number of virtual days for the districts classified as having a "High" share of black students spent 52 days in virtual schooling, and the "Low" districts spent 27 days.
-Jack and Oster [-@Jack_Oster_2023] found the number to be 56 days and 36 days respective.
-Our results for Hispanic students show that "High" districts had an average of 47 virtual days, and "Low" districts had an average of 30 virtual days.
-Jack and Oster found 53 days and 43 days respectively.
-Thus, our results are consistent with Jack and Oster in that we also observed that districts with a higher share of black students and a higher share of Hispanic students spent more days in virtual schooling.
-We find a larger discrepancy between "High" and "Low" district for both shares, primarily driven by the lower number of virtual days we calculated for the "Low" districts.
+Figure \ref{fig-race} shows how the average number of days with school closed in districts vary "Low" and "High" shares of Black, Hispanic, Asian and White students.
+For Black students, these numbers were 52 and 27, respectively, differing slightly to those from Jack and Oster [-@Jack_Oster_2023] who determined 56 and 36 days, respectively.
+For Hispanic students, we found an average of 47 and 30 days, respectively, again differing to those from the original paper, which reported 53 and 43 days, respectively.
+In spite of the numerical differences, our results point to conclusions consistent with those from Jack and Oster [-@Jack_Oster_2023], who also observed districts with higher shares of Black and Hispanic students to spend more of the 2020-2021 school year in virtual schooling.
 
 We extended Jack and Oster's research by also looking at the shares of White and Asian students.
-We found that districts with "High" shares of white students had an average of 55 days virtual, whilst the "Low" districts had 23 virtual days.
-For Asian students, we found "High" districts had an average of 40 days virtual, whilst "Low" districts had an average of 38 days virtual.
-This variation can be considered insignificant.
+We found that districts with "High" and "Low" shares of White students had an average of 55 and 23 days in virtual schooling, respectively.
+Likewise, we found that districts with "High" and "Low" shares of Asian students had average of 40 and 38 days in virtual schooling, respectively.
+These results point to the following: White students appear to be further enfranchised by having greater access to in-person learning, in contrast to historically and currently disadvantaged Black and Hispanic students.
+No such conclusions can be drawn for Asian students, for whom the variation in the number of virtual days between "High" and "Low" districts is too small to be considered.
 
-Taken together, in-person education was inequitably distributed across demographic characteristics, with more disadvantaged districts spending more time in virtual schooling [@Jack_Oster_2023].
-In particular, districts with less technological preparedness and higher shares of minorities  were further disenfranchised by less access to in-person education.
+Taken together, in-person education was inequitably distributed across demographic characteristics, with racially disadvantaged districts spending more time in virtual schooling [@Jack_Oster_2023].
+By contrast, districts with less technological preparedness spent less time in virtual schooling, which may arise as a consequence of a lack of ability to provide quality on-line learning resources.
+For these differing reasons, both groups can be said to have been further disenfranchised by the pandemic.
 This pattern likely reinforced educational inequities between vulnerable and more privileged groups.

### 2024-02-14 paper/paper.qmd
Add files via upload

@@
 
-Our paper seeks to assess the robustness and generalisability of Jack and Oster's work. We successfully replicate and extend three of its major research claims:
+Our paper seeks to assess the robustness and generalisability of Jack and Oster's work. Excepting one aspect noted here, we successfully replicate and extend three of its major research claims:
 
-(1) With respect to the world, the United States faced the second highest number of days of schoolclosed between January 2020 to December 2021, with a mean number of days of 667.
+(1) With respect to the world, the United States faced the second highest number of days of school closed between January 2020 to December 2021, with a mean number of days of 667.
 
@@
 Changes in ELA scores were smaller than mathematics scores, but significantly larger in districts with larger populations of students who are Black or Hispanic.
+
+The only main discrepancy between our analysis and the original paper is in the second research claim, where we found districts with lower broadband usage to in fact spend less of the school year in virtual schooling.
+We accounted for factors which may have produced this discrepancy, and concluded it to be a consequence of their lack of technological preparedness.
 
@@
 The authors also compare the average change in pass rates in mathematics and ELA with the number of days of in-person schooling in Spring 2021 versus Spring 2018-2019.
-Our paper has successfully replicated and extended an important part of three of their major findings:
+With one exception of note, our paper has successfully replicated and extended an important part of three of their major findings:
 
@@
 In fact, it falls second only to Azerjiban, which recorded an average of 669 days.
+
 (2) Access to in-person education was unequal by demographic characteristics.
-More disadvantaged districts, *i.e.*, those with higher proportions of racial minorities and lower broadband usage spent more days in virtual schooling.
+In particular, disadvantaged districts with higher proportions of racial minorities spent more days in virtual schooling.
+In contrast to Jack and Oster [-@Jack_Oster_2023], districts with lower broadband usage were found in our analysis to spend less time in virtual schooling, likely due to their diminished ability to deliver quality online resources.
+
 (3) During the 2020-2021 school year, students' pass rates on standardised assessments declined by 12.8 percentage points in mathematics and 6.8 in ELA.
@@
 As noted by Jack and Oster [-@Jack_Oster_2023], it can be seen that the equity impacts are two-fold.
-First, schools (and students) with lower resources are less likely to have access to in-person instruction.
-The significant differences in virtual schooling days across districts categorized by racial demographics underscore systemic inequalities in access to in-person education.
-Our findings reveal that districts with higher proportions of Black and Hispanic students spent substantially more time in virtual schooling compared to those with lower proportions.
-This highlights a  disparity wherein more disadvantaged districts, often populated by minority students, face prolonged periods of virtual learning, potentially exacerbating existing educational inequities.
-Second, for such groups, the consequences of a lack of in-person instruction are more severe.
+First, schools (and students) of more vulnerable racial backgrounds -- especially, Black and Hispanic -- are less likely to have access to in-person instruction.
+Second, for such groups, the consequences of a lack of in-person instruction on academic performance are more severe.
 This may be due to a smaller investment by such schools in effective remote learning programs or due to the challenges disadvantages students face at home, such as less reliable Internet connection or fewer community resources.
 Accordingly, while COVID-19 school closures imposed learning loss costs on students as a whole, they affected most negatively those who were already most vulnerable.
-This exacerbates the already large inequality gap.
+This exacerbates the already large inequality gap in educational outcomes.
 

### 2024-02-14 paper/paper.qmd
Updated paper
Updated the results section and amended some of the figures. Also updated one of the cleaned datasets to include an additional column

@@
 
-@fig-mathscoresbyonline and @fig-elascoresbyonline explore the relationship between the share of in-person learning and change in test scores in standardised tests in Mathematics and ELA respectively.
-In particular, they examine changes in test scores across 3 years (2021, 2019, and 2018) from the year prior (excepting the case of 2021, where changes are relative to 2019).
+@fig-mathscoresbyonline and @fig-elascoresbyonline explore the relationship between the share of in-person learning and change in pass rates in standardised tests in Mathematics and ELA respectively.
+In particular, they examine changes in test pass rates across 3 years (2021, 2019, and 2018) from the year prior (excepting the case of 2021, where changes are relative to 2019).
 
@@
 However, we first converted the dataset into a `.csv` file, `scores_lm_demographics.csv`, to be used in the cleaning and analysis processes.
-From there, we cleaned the data by only selecting the columns of interest, those being the share of in-person learning, the subject of the test, the changes across each of the three years of interest, the number of students enrolled in each school district, and the shares of each of the three races of interest (White, Black, Asian and Hispanic).
+From there, we cleaned the data by only selecting the columns of interest, those being the share of in-person learning, the subject of the test, the changes across each of the three years of interest, the number of students enrolled in each school district, the state each schooling district is in, and the shares of each of the three races of interest (White, Black, Asian and Hispanic).
 To generate the aforementioned figures, we first calculated the total number of students enrolled across all school districts.
@@
 We proceeded by defining four in-person categories of 0-25%, 25-50%, 50-75%, and 75-100%, after which we mutated our filtered data by assigning each school district one of the four categories.
-We then proceeded to group the data by year (one of the three previously mentioned), and by in-person category so that we were able to calculated the weighted average change in test scores for each in-person category in each year.
-Finally, we ungrouped the data to calculate the overall, and thus un-weighted, average change in test scores for each of the three years.
-This was repeated for both Mathematics and ELA test scores by simply changing the filtering of the data to only include one of the two.
+We then proceeded to group the data by year (one of the three previously mentioned), and by in-person category so that we were able to calculated the weighted average change in test pass rates for each in-person category in each year.
+Finally, we ungrouped the data to calculate the overall, and thus un-weighted, average change in test pass rates for each of the three years.
+This was repeated for both Mathematics and ELA test pass rates by simply changing the filtering of the data to only include one of the two.
 
-@fig-mathscoresrace, @fig-elascoresrace examine these test score changes from a different lens.
-Instead of considering the share of in-person learning, it explores the possibility of a systematic difference in the changes in test scores based on the relative share of various races.
-In particular, the figures examine the correlation between changes in test scores and the relative quantile share of White, Black, and Hispanic students which is one of "Low", "Middle" or "High".
+@fig-mathscoresrace, @fig-elascoresrace examine these test pass rate changes from a different lens.
+Instead of considering the share of in-person learning, it explores the possibility of a systematic difference in the changes in test pass rates based on the relative share of various races.
+In particular, the figures examine the correlation between changes in test pass rates and the relative quantile share of White, Black, and Hispanic students which is one of "Low" or "High".
 As before, this is also done for each of the three years of interest for each of the three races.
@@
 To generate this graph, we once again employed the cleaned `scores_lm_demographics.csv` file as was used to generate @fig-mathscoresbyonline and @fig-elascoresbyonline.
-We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the three quantiles, "Low", "Middle", and "High", for each of the three races.
-From there, we grouped the data by year and quantile for each of the three races, then calculated the weighted average change in test scores for each subject and quantile, across all races and years.
-From there, we simply combined the summary statistics for each of the races and their respective quantiles, and showcased them in the figures, differentiating by race through shape, and year through color.
+We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the two quantiles, "Low" and "High", for each of the three races relative to the average shares in each of the 11 states.
+From there, we grouped the data by year and quantile for each of the three races, then calculated the weighted average change in test pass rates for each subject and quantile, across all races and years.
+From there, we simply combined the summary statistics for each of the races and their respective quantiles, and showcased them in the figures, differentiating by race through color, and year through shape.
 
@@
 #| warning: false 
-#| fig-cap: "Test score by percent online (change)"
+#| fig-cap: "Enrollment-weighted average change in pass rates in Math standardised tests by the percent of in-person learning."
 #| fig-pos: H
@@
 #| warning: false 
-#| fig-cap: "Test score by percent online (change)"
+#| fig-cap: "Enrollment-weighted average change in pass rates in ELA standardised tests by the percent of in-person learning."
 # Calculate the total number of enrollments overall
@@
 
-# Filter for Math
+# Filter for ELA
 filtered_test_data <- cleaned_test_score_data |>
@@
 Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@TestScore] was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021.
-
-[ADD DETAIL].
-
-Panels A and B show the scores in mathematics and in ELA, respectively. [EXPLAIN FIGURE & SYMBOLS]
-
+Both @fig-mathscoresbyonline and @fig-elascoresbyonline both provide information on the change in pass rates in Math and ELA standardised tests from the previous year, respectively, taking into account the share of in-person learning done by various school districts and across the three years of interest, each indicated by its respective color.
 Consistent with Jack and Oster [-@Jack_Oster_2023], our analysis shows a significant decline in pass rates from the 2018-2019 to the 2020-2021 school year.
-In particular, pass rates in mathematics and ELA declined by 12.8 and 6.8 percentage points, respectively.
+We see that in Spring 2021, there is a clear fall in the pass rates overall in both subject areas from 2019 (note that there were no standardised assessmments in 2020), though this fall is much more pronounced in Math than ELA (-12.8 percentage points compared to the -6.8 percentage points, respectively).
 The discrepancy between these two subjects is consistent with much of the current economic literature, which shows mathematics scores to be more sensitive to schooling differences [@betts2011effect; @angrist].
 
-... Thus, we find that in-person learning has significantly higher benefits for districts with larger shares of Black and Hispanic students.
+We also see evidence that a lack of in-person learning has a detrimental effect on student's learning, as seen by the positive correlation between the share of in-person learning and the average change in pass rates in both Math and ELA in Spring 2021.
+One can note the lack of significant change and correlations between in-person learning and changes in pass rates for both subjects in Spring 2019 and Spring 2018, possibly due to schooling districts with lower shares of in-person learning being better equipped for this learning style given that this was prior to the pandemic, meaning schools were less likely to have been forced to switch to online or hybrid schooling, and instead were able to do so on their own accord.
 
@@
 #| message: false
-#| fig-cap: "Update"
+#| fig-cap: "Enrollment-weighted average change in pass rates in Math standardised test scores by the quantile share of White, Black, and Hispanic students"
 # Filter for Math
@@
 white_share <- filtered_test_data |>
-  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_white, enrollment)
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_white, enrollment, state)
 
@@
 black_share <- filtered_test_data |>
-  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_black, enrollment)
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_black, enrollment, state)
 
@@
 hispanic_share <- filtered_test_data |>
-  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_hispanic, enrollment)
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_hispanic, enrollment, state)
 
@@
 white_share <- white_share |>
-  mutate(quantile = ntile(share_enroll_white, 3)) |>
+  group_by(state) |>
+  mutate(quantile = ntile(share_enroll_white, 2)) |>
   mutate(quantile_level = case_when(
     quantile == 1 ~ "Low",
-    quantile == 2 ~ "Middle",
-    quantile == 3 ~ "High"
+    quantile == 2 ~ "High"
   ))
@@
 black_share <- black_share |>
-  mutate(quantile = ntile(share_enroll_black, 3)) |>
+  group_by(state) |>
+  mutate(quantile = ntile(share_enroll_black, 2)) |>
   mutate(quantile_level = case_when(
     quantile == 1 ~ "Low",
-    quantile == 2 ~ "Middle",
-    quantile == 3 ~ "High"
+    quantile == 2 ~ "High"
   ))
@@
 hispanic_share <- hispanic_share |>
-  mutate(quantile = ntile(share_enroll_hispanic, 3)) |>
+  group_by(state) |>
+  mutate(quantile = ntile(share_enroll_hispanic, 2)) |>
   mutate(quantile_level = case_when(
     quantile == 1 ~ "Low",
-    quantile == 2 ~ "Middle",
-    quantile == 3 ~ "High"
+    quantile == 2 ~ "High"
   ))
@@
   scale_x_continuous(limits = c(-17, 3)) +
-  scale_y_discrete(limits = c("Low", "Middle", "High")) +
+  scale_y_discrete(limits = c("Low", "High")) +
   labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Quantile Level",
@@
 #| message: false
-#| fig-cap: "Update"
-# Filter for Math
+#| fig-cap: "Enrollment-weighted average change in pass rates in ELA standardised test scores by the quantile share of White, Black, and Hispanic students"
+# Filter for ELA
 filtered_test_data <- cleaned_test_score_data |>
@@
 ```
+
+In line with some of our previous discussions, we looked towards building upoing Jack and Oster's work by examining the potential systematic disparities between relative student racial compositions and the average percentage point change in test pass rates.
+In particular, both @fig-mathscoresrace and @fig-elascoresrace provide information on the changes in test pass rates across the three years of interest from the year prior as a function of the race quantiles that each schooling district belonged to for each of the share of White, Black, and Hispanic students.
+By grouping the test score data by state then calculating the average share of each of the three races mentioned, we were able to assign each schooling district a value of "High" or "Low" for each of the three races, detailing whether the particular schooling district had a share of students of a particular race greater than, or lower than, the median share across the 11 states, respectively.
+The figures distinguish between the year and race in question by shape and color, respectively.
+
+By examining both figures, we find evidence that schooling districts with a relatively higher portion of either Black or Hispanic students featured greater drops in test pass rates on average, in both subjects, relative to schooling districts with lower portions of Black or Hispanic students in Spring 2021.
+Since we have established in the previous Results section that schooling districts with relatively higher shares of Black or Hispanic students typically had a higher number of virtual days than schooling districts with relatively lower shares, we effectively find evidence that in-person learning has greater benefits for districts with larger shares of Black and Hispanic students.
 

### 2024-02-14 paper/paper.qmd
Updated citation
Updated a citation in the qmd and paper

@@
 
-Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@TestScore] was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021.
+Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2] was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021.
 Both @fig-mathscoresbyonline and @fig-elascoresbyonline both provide information on the change in pass rates in Math and ELA standardised tests from the previous year, respectively, taking into account the share of in-person learning done by various school districts and across the three years of interest, each indicated by its respective color.

### 2024-02-14 scripts/00-simulate_data.R
Added simulations for figure 1 and 3
Simulated the dataset for figures 1 and 3 in the paper, respectively, and included tests for both

@@ -15,10 +15,49 @@ set.seed(555) #random seed
 
 ## DATASET 1 ##
 
+# Define the countries and their respective regions
+countries <- c("USA", "UK", "Germany", "South Korea", "Ethiopia")
+regions <- c("North America", "Europe and Central Asia", "Europe and Central Asia", "East Asia and Pacific", "Sub-Saharan Africa")
 
+# Create a data frame to store the simulated data
+simulated_data1 <- data.frame(
+  country = character(),
+  region = character(),
+  date = as.Date(character()),
+  covid_tracker_score = integer()
+)
 
+# Generate random dates between March 1st and December 31st, 2020
+start_date <- as.Date("2020-03-01")
+end_date <- as.Date("2020-12-31")
+all_dates <- seq(start_date, end_date, by = "day")
 
+# For each country, generate 10 unique random dates and assign covid tracker scores
+for (i in seq_along(countries)) {
+  country_dates <- sample(all_dates, size = 10, replace = FALSE)
+  country <- rep(countries[i], length(country_dates))
+  region <- rep(regions[i], length(country_dates))
+  covid_tracker_score <- sample(0:3, size = length(country_dates), replace = TRUE)
+  
+  # Append the data to the simulated data frame
+  simulated_data1 <- bind_rows(simulated_data1, data.frame(country, region, date = country_dates, covid_tracker_score))
+}
 
+### TESTS ###
+
+# Check that the covid score is a value between 0 and 3 inclusive
+simulated_data1$covid_tracker_score |> min() >= 0
+simulated_data1$covid_tracker_score |> max() <= 3
+
+# Check that there are 5 countries present in the dataset
+test_country1 <- simulated_data1$country %in% c("USA", "UK", "Germany", "South Korea", "Ethiopia")
+all(test_country)
+
+# Verify that each column type is as it should
+simulated_data1$country |> class() == "character"
+simulated_data1$region |> class() == "character"
+simulated_data1$date |> class() == "Date"
+simulated_data1$covid_tracker_score |> class() == "integer"
 
 ## DATASET 2 - local characteristics for districts ##
 
@@ -52,3 +91,40 @@ is.wholenumber <- function(x, tol = .Machine$double.eps^0.5) abs(x - round(x)) <
 is.wholenumber(simulated_data2$white_students)
 is.wholenumber(simulated_data2$black_students)
 
+## DATASET 3 ##
+
+# Define the number of schools
+num_schools <- 1000
+
[…]

### 2024-02-14 paper/paper.qmd
Updated figure
In the quarto file, Figure 7 was updated to have a smaller x-axis scale

@@
   scale_y_discrete(limits = c("Low", "High")) +
-  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Quantile Level",
-       title = "Average Change in Pass Rate by Race and Quantile") +
+  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Quantile Level") +
   scale_color_discrete(labels = c("Black", "Hispanic", "White")) +
@@
   geom_vline(xintercept = 0, color = "darkgrey") +
-  scale_x_continuous(limits = c(-17, 3)) +
+  scale_x_continuous(limits = c(-10, 3)) +
   scale_y_discrete(limits = c("Low", "High")) +
-  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Quantile Level",
-       title = "Average Change in Pass Rate by Race and Quantile") +
+  labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Quantile Level") +
   scale_color_discrete(labels = c("Black", "Hispanic", "White")) +

### 2024-02-14 scripts/03-test_data.R
Added tests
Added tests for the cleaned data that generates the regiond data and test pass rate data

@@ -9,6 +9,32 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(here)
+
+#### Read Data ####
+cleaned_region_data <- read_csv(here("data/analysis_data/cleaned_region_data.csv"))
+cleaned_test_score_data <- read_csv(here("data/analysis_data/cleaned_test_score_data.csv"))
+
+#### TESTING DATA FOR FIGURE ON REGIONS ####
+# Check that there are exactly 185 unique countries present in the dataset
+length(unique(cleaned_region_data$country_name)) == 185
+
+# Check that there are exactly 7 regions to which a country can belong to
+length(unique(cleaned_region_data$region_name)) == 7
+
+# Check that there are exactly 731 unique days (2 years - 2020 was a leap year) in the dataset
+length(unique(cleaned_region_data$date)) == 731
+
+# Check that the covid scores are between 0 and 3 inclusive
+cleaned_region_data$covid_score |> min() == 0
+cleaned_region_data$covid_score |> max() == 3
+
+# Verify that each column is of the appropriate class
+cleaned_region_data$country_name |> class() == "character"
+cleaned_region_data$region_name |> class() == "character"
+cleaned_region_data$date |> class() == "Date"
+cleaned_region_data$covid_score |> class() == "numeric"
+
 
 #### TESTING DATA FOR FIGURE 2 ####
 
@@ -21,5 +47,37 @@ broadband_data$`COUNTY ID` |> class() == "numeric"
 race_data$enrollment |> class() == "numeric"
 
 
+#### TESTING DATA FOR FIGURES ON TEST SCORES ####
+# Check that there are exactly 21 unique states to which a school district can belong
+length(unique(cleaned_test_score_data$state)) == 21
 
+# Check that enrollment is a positive value
+cleaned_test_score_data$enrollment |> min() >= 0
+
+# Check that the changes in test pass rates are between -1 and 1 inclusive
+na.omit(cleaned_test_score_data$change_2017_2018) |> min() >= -1
+na.omit(cleaned_test_score_data$change_2017_2018) |> max() <= 1
+
+na.omit(cleaned_test_score_data$change_2018_2019) |> min() >= -1
+na.omit(cleaned_test_score_data$change_2018_2019) |> max() <= 1
+
+na.omit(cleaned_test_score_data$change_2019_2021) |> min() >= -1
+na.omit(cleaned_test_score_data$change_2019_2021) |> max() <= 1
+
[…]

### 2024-02-14 paper/paper.qmd
Fixed error
Paper mentioned 11 states however the dataset was actually on 21 states.

@@
     abstract: "School closures due to the COVID-19 pandemic have raised significant concerns about the consequences on student learning and achievement gaps.
-This paper replicates a data analysis of the scope of school closures in the United States in the 2020-2021 school year, the inequitable distribution of such closures by demographic characteristics and the resultant declines in pass rates on standardised tests in mathematics and English Language Arts (ELA) of students in grades 3-8 across 11 states.
+This paper replicates a data analysis of the scope of school closures in the United States in the 2020-2021 school year, the inequitable distribution of such closures by demographic characteristics and the resultant declines in pass rates on standardised tests in mathematics and English Language Arts (ELA) of students in grades 3-8 across 21 states.
 We apply secondary research regarding the scope of school closures in the Netherlands in same year and the declines in national examination scores in reading, spelling and mathematics of Dutch students in grades 4-7.
@@
 Jack and Oster [-@Jack_Oster_2023] also found that the duration of school closures varies with local demographic characteristics, with more disadvantaged districts facing more prolonged closures.
-The study population was grade 3 to 8 students across 11 major American states, being Colorado (CO), Connecticut (CT), Massachusetts (MA), Minnesota (MN), Mississippi (MI), Ohio (OH), Rhode Island (RI), Virginia (VA), Wisconsin (WI), West Virginia (WV) and Wyoming (WY).
+The study population was grade 3 to 8 students across 21 major American states, being Arkansas (AR), Colorado (CO), Connecticut (CT), Georgia (GA), Idaho (ID), Kansas (KS), Louisiana (LA), Massachusetts (MA), Minnesota (MN), Mississippi (MS), Missouri (MO), New Hampshire (NH), Ohio (OH), Pennsylvania (PA), Rhode Island (RI), South Carolina (SC), South Dakota (SD), Virginia (VA), Wisconsin (WI), West Virginia (WV) and Wyoming (WY).
 The estimand was the impact of COVID-19 closures on academic performance.
@@
 This dataset is a `.csv` version of `scores_lm_demographics.dta`, obtained from the replication package of “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2], published in the American Economic Association’s *AER: Insights* [@citeAEA].
-Data are obtained from the Departments of Education of the aforementioned 11 US states, each of whom collect data from constituent schools, school boards and school authorities [@DeptsEd].
-The dataset contains extensive information on school districts across these 11 states, including shares of students by race, shares of schooling done in-person, and changes in average test scores in both Mathematics and ELA from the previous year across the years 2018-2019 and 2021-2022.
+Data are obtained from the Departments of Education of the aforementioned 21 US states, each of whom collect data from constituent schools, school boards and school authorities [@DeptsEd].
+The dataset contains extensive information on school districts across these 21 states, including shares of students by race, shares of schooling done in-person, and changes in average test scores in both Mathematics and ELA from the previous year across the years 2018-2019 and 2021-2022.
 Note no information on test scores are available for 2020, as all standardised assessments were cancelled due to the pandemic.
@@
 To generate this graph, we once again employed the cleaned `scores_lm_demographics.csv` file as was used to generate @fig-mathscoresbyonline and @fig-elascoresbyonline.
-We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the two quantiles, "Low" and "High", for each of the three races relative to the average shares in each of the 11 states.
+We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the two quantiles, "Low" and "High", for each of the three races relative to the average shares in each of the 21 states.
 From there, we grouped the data by year and quantile for each of the three races, then calculated the weighted average change in test pass rates for each subject and quantile, across all races and years.
@@
 
-Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2] was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021.
+Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2] was used to examine changes in district-level pass rate data from 21 state standardised assessments, taken in the spring of 2018, 2019 and 2021.
 Both @fig-mathscoresbyonline and @fig-elascoresbyonline both provide information on the change in pass rates in Math and ELA standardised tests from the previous year, respectively, taking into account the share of in-person learning done by various school districts and across the three years of interest, each indicated by its respective color.
@@
 In particular, both @fig-mathscoresrace and @fig-elascoresrace provide information on the changes in test pass rates across the three years of interest from the year prior as a function of the race quantiles that each schooling district belonged to for each of the share of White, Black, and Hispanic students.
-By grouping the test score data by state then calculating the average share of each of the three races mentioned, we were able to assign each schooling district a value of "High" or "Low" for each of the three races, detailing whether the particular schooling district had a share of students of a particular race greater than, or lower than, the median share across the 11 states, respectively.
+By grouping the test score data by state then calculating the average share of each of the three races mentioned, we were able to assign each schooling district a value of "High" or "Low" for each of the three races, detailing whether the particular schooling district had a share of students of a particular race greater than, or lower than, the median share across the 21 states, respectively.
 The figures distinguish between the year and race in question by shape and color, respectively.
@@
 
-The analysis by Jack and Oster seeks to define the scope of COVID-19 school closures in the United States with respect to the global picture, and explore the correlation between the number of days of school closed with various demographic characteristics of 11 of its major states.
+The analysis by Jack and Oster seeks to define the scope of COVID-19 school closures in the United States with respect to the global picture, and explore the correlation between the number of days of school closed with various demographic characteristics of 21 of its major states.
 The authors also compare the average change in pass rates in mathematics and ELA with the number of days of in-person schooling in Spring 2021 versus Spring 2018-2019.

### 2024-02-14 paper/paper.qmd
Add files via upload

--- 2024-02-14 paper/paper.qmd
@@
 author: "Krishiv Jain, Julia Kim, Abbass Sleiman"
-thanks: "Code and data are available at: [https://github.com/AbbassSleiman/COVID19-US-School-Closures](https://github.com/AbbassSleiman/COVID19-US-School-Closures); Replication on Social Science Reproduction platform available at: [https://www.socialsciencereproduction.org/reproductions/8aab4425-63ad-47bc-93ef-82076d6e49cc/index](https://www.socialsciencereproduction.org/reproductions/8aab4425-63ad-47bc-93ef-82076d6e49cc/index)"
+thanks: "Code and data are available at: [https://github.com/AbbassSleiman/COVID19-US-School-Closures](https://github.com/AbbassSleiman/COVID19-US-School-Closures); Replication on Social Science Reproduction platform available at: [https://doi.org/10.48152/ssrp-9vc2-gp37](https://doi.org/10.48152/ssrp-9vc2-gp37)"
 date: "February 15, 2024"
@@
 
-@fig-mathscoresbyonline and @fig-elascoresbyonline explore the relationship between the share of in-person learning and change in pass rates in standardised tests in Mathematics and ELA respectively.
-In particular, they examine changes in test pass rates across 3 years (2021, 2019, and 2018) from the year prior (excepting the case of 2021, where changes are relative to 2019).
+@fig-mathscoresbyonline and @fig-elascoresbyonline explore the relationship between the share of in-person learning and change in test scores in standardised tests in Mathematics and ELA respectively.
+In particular, they examine changes in test scores across 3 years (2021, 2019, and 2018) from the year prior (excepting the case of 2021, where changes are relative to 2019).
 
@@
 However, we first converted the dataset into a `.csv` file, `scores_lm_demographics.csv`, to be used in the cleaning and analysis processes.
-From there, we cleaned the data by only selecting the columns of interest, those being the share of in-person learning, the subject of the test, the changes across each of the three years of interest, the number of students enrolled in each school district, the state each schooling district is in, and the shares of each of the three races of interest (White, Black, Asian and Hispanic).
+From there, we cleaned the data by only selecting the columns of interest, those being the share of in-person learning, the subject of the test, the changes across each of the three years of interest, the number of students enrolled in each school district, and the shares of each of the three races of interest (White, Black, Asian and Hispanic).
 To generate the aforementioned figures, we first calculated the total number of students enrolled across all school districts.
@@
 We proceeded by defining four in-person categories of 0-25%, 25-50%, 50-75%, and 75-100%, after which we mutated our filtered data by assigning each school district one of the four categories.
-We then proceeded to group the data by year (one of the three previously mentioned), and by in-person category so that we were able to calculated the weighted average change in test pass rates for each in-person category in each year.
-Finally, we ungrouped the data to calculate the overall, and thus un-weighted, average change in test pass rates for each of the three years.
-This was repeated for both Mathematics and ELA test pass rates by simply changing the filtering of the data to only include one of the two.
+We then proceeded to group the data by year (one of the three previously mentioned), and by in-person category so that we were able to calculated the weighted average change in test scores for each in-person category in each year.
+Finally, we ungrouped the data to calculate the overall, and thus un-weighted, average change in test scores for each of the three years.
+This was repeated for both Mathematics and ELA test scores by simply changing the filtering of the data to only include one of the two.
 
-@fig-mathscoresrace, @fig-elascoresrace examine these test pass rate changes from a different lens.
-Instead of considering the share of in-person learning, it explores the possibility of a systematic difference in the changes in test pass rates based on the relative share of various races.
-In particular, the figures examine the correlation between changes in test pass rates and the relative quantile share of White, Black, and Hispanic students which is one of "Low" or "High".
+@fig-mathscoresrace, @fig-elascoresrace examine these test score changes from a different lens.
+Instead of considering the share of in-person learning, it explores the possibility of a systematic difference in the changes in test scores based on the relative share of various races.
+In particular, the figures examine the correlation between changes in test scores and the relative quantile share of White, Black, and Hispanic students which is one of "Low", "Middle" or "High".
 As before, this is also done for each of the three years of interest for each of the three races.
@@
 To generate this graph, we once again employed the cleaned `scores_lm_demographics.csv` file as was used to generate @fig-mathscoresbyonline and @fig-elascoresbyonline.
-We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the two quantiles, "Low" and "High", for each of the three races relative to the average shares in each of the 11 states.
-From there, we grouped the data by year and quantile for each of the three races, then calculated the weighted average change in test pass rates for each subject and quantile, across all races and years.
-From there, we simply combined the summary statistics for each of the races and their respective quantiles, and showcased them in the figures, differentiating by race through color, and year through shape.
+We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the three quantiles, "Low", "Middle", and "High", for each of the three races.
+From there, we grouped the data by year and quantile for each of the three races, then calculated the weighted average change in test scores for each subject and quantile, across all races and years.
+From there, we simply combined the summary statistics for each of the races and their respective quantiles, and showcased them in the figures, differentiating by race through shape, and year through color.
 
@@
 #| warning: false 
-#| fig-cap: "Enrollment-weighted average change in pass rates in Math standardised tests by the percent of in-person learning."
+#| fig-cap: "Test score by percent online (change)"
 #| fig-pos: H
@@
 #| warning: false 
-#| fig-cap: "Enrollment-weighted average change in pass rates in ELA standardised tests by the percent of in-person learning."
+#| fig-cap: "Test score by percent online (change)"
 # Calculate the total number of enrollments overall
@@
 
-# Filter for ELA
+# Filter for Math
 filtered_test_data <- cleaned_test_score_data |>
@@
 
-Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2] was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021.
-Both @fig-mathscoresbyonline and @fig-elascoresbyonline both provide information on the change in pass rates in Math and ELA standardised tests from the previous year, respectively, taking into account the share of in-person learning done by various school districts and across the three years of interest, each indicated by its respective color.
+Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@TestScore] was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021.
+
+[ADD DETAIL].
+
+Panels A and B show the scores in mathematics and in ELA, respectively. [EXPLAIN FIGURE & SYMBOLS]
+
 Consistent with Jack and Oster [-@Jack_Oster_2023], our analysis shows a significant decline in pass rates from the 2018-2019 to the 2020-2021 school year.
-We see that in Spring 2021, there is a clear fall in the pass rates overall in both subject areas from 2019 (note that there were no standardised assessmments in 2020), though this fall is much more pronounced in Math than ELA (-12.8 percentage points compared to the -6.8 percentage points, respectively).
+In particular, pass rates in mathematics and ELA declined by 12.8 and 6.8 percentage points, respectively.
 The discrepancy between these two subjects is consistent with much of the current economic literature, which shows mathematics scores to be more sensitive to schooling differences [@betts2011effect; @angrist].
 
-We also see evidence that a lack of in-person learning has a detrimental effect on student's learning, as seen by the positive correlation between the share of in-person learning and the average change in pass rates in both Math and ELA in Spring 2021.
-One can note the lack of significant change and correlations between in-person learning and changes in pass rates for both subjects in Spring 2019 and Spring 2018, possibly due to schooling districts with lower shares of in-person learning being better equipped for this learning style given that this was prior to the pandemic, meaning schools were less likely to have been forced to switch to online or hybrid schooling, and instead were able to do so on their own accord.
+... Thus, we find that in-person learning has significantly higher benefits for districts with larger shares of Black and Hispanic students.
 
@@
 #| message: false
-#| fig-cap: "Enrollment-weighted average change in pass rates in Math standardised test scores by the quantile share of White, Black, and Hispanic students"
+#| fig-cap: "Update"
 # Filter for Math
@@
 white_share <- filtered_test_data |>
-  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_white, enrollment, state)
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_white, enrollment)
 
@@
 black_share <- filtered_test_data |>
-  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_black, enrollment, state)
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_black, enrollment)
 
@@
 hispanic_share <- filtered_test_data |>
-  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_hispanic, enrollment, state)
+  select(change_2019_2021, change_2018_2019, change_2017_2018, share_enroll_hispanic, enrollment)
 
@@
 white_share <- white_share |>
-  group_by(state) |>
-  mutate(quantile = ntile(share_enroll_white, 2)) |>
+  mutate(quantile = ntile(share_enroll_white, 3)) |>
   mutate(quantile_level = case_when(
     quantile == 1 ~ "Low",
-    quantile == 2 ~ "High"
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
   ))
@@
 black_share <- black_share |>
-  group_by(state) |>
-  mutate(quantile = ntile(share_enroll_black, 2)) |>
+  mutate(quantile = ntile(share_enroll_black, 3)) |>
   mutate(quantile_level = case_when(
     quantile == 1 ~ "Low",
-    quantile == 2 ~ "High"
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
   ))
@@
 hispanic_share <- hispanic_share |>
-  group_by(state) |>
-  mutate(quantile = ntile(share_enroll_hispanic, 2)) |>
+  mutate(quantile = ntile(share_enroll_hispanic, 3)) |>
   mutate(quantile_level = case_when(
     quantile == 1 ~ "Low",
-    quantile == 2 ~ "High"
+    quantile == 2 ~ "Middle",
+    quantile == 3 ~ "High"
   ))
@@
   scale_x_continuous(limits = c(-17, 3)) +
-  scale_y_discrete(limits = c("Low", "High")) +
+  scale_y_discrete(limits = c("Low", "Middle", "High")) +
   labs(x = "Average Change in Pass Rate (Percentage Points)", y = "Quantile Level",
@@
 #| message: false
-#| fig-cap: "Enrollment-weighted average change in pass rates in ELA standardised test scores by the quantile share of White, Black, and Hispanic students"
-# Filter for ELA
+#| fig-cap: "Update"
+# Filter for Math
 filtered_test_data <- cleaned_test_score_data |>
@@
 ```
-
-In line with some of our previous discussions, we looked towards building upoing Jack and Oster's work by examining the potential systematic disparities between relative student racial compositions and the average percentage point change in test pass rates.
-In particular, both @fig-mathscoresrace and @fig-elascoresrace provide information on the changes in test pass rates across the three years of interest from the year prior as a function of the race quantiles that each schooling district belonged to for each of the share of White, Black, and Hispanic students.
-By grouping the test score data by state then calculating the average share of each of the three races mentioned, we were able to assign each schooling district a value of "High" or "Low" for each of the three races, detailing whether the particular schooling district had a share of students of a particular race greater than, or lower than, the median share across the 11 states, respectively.
-The figures distinguish between the year and race in question by shape and color, respectively.
-
-By examining both figures, we find evidence that schooling districts with a relatively higher portion of either Black or Hispanic students featured greater drops in test pass rates on average, in both subjects, relative to schooling districts with lower portions of Black or Hispanic students in Spring 2021.
-Since we have established in the previous Results section that schooling districts with relatively higher shares of Black or Hispanic students typically had a higher number of virtual days than schooling districts with relatively lower shares, we effectively find evidence that in-person learning has greater benefits for districts with larger shares of Black and Hispanic students.
 

### 2024-02-14 paper/paper.qmd
Updated introduction

--- 2024-02-14 paper/paper.qmd
@@
 In studying the scope of school closures across the United States (US), they reported that the country experienced, on average, one of the highest number of days of school closed between January 2020 to December 2021 worldwide [@Jack_Oster_2023].
-Jack and Oster [-@Jack_Oster_2023] also found that the duration of school closures varies with local demographic characteristics, with more disadvantaged districts facing more prolonged closures.
-The study population was grade 3 to 8 students across 21 major American states, being Arkansas (AR), Colorado (CO), Connecticut (CT), Georgia (GA), Idaho (ID), Kansas (KS), Louisiana (LA), Massachusetts (MA), Minnesota (MN), Mississippi (MS), Missouri (MO), New Hampshire (NH), Ohio (OH), Pennsylvania (PA), Rhode Island (RI), South Carolina (SC), South Dakota (SD), Virginia (VA), Wisconsin (WI), West Virginia (WV) and Wyoming (WY).
-The estimand was the impact of COVID-19 closures on academic performance.
-They found considerable declines in test scores during the 2020-2021 academic year, with declines larger in school districts with less in-person instruction [@Jack_Oster_2023].
+Jack and Oster [-@Jack_Oster_2023] also found that the duration of school closures varies with local demographic characteristics, with more disadvantaged districts facing more prolonged closures.They found considerable declines in test scores during the 2020-2021 academic year, with declines larger in school districts with less in-person instruction.
 On average, pass rates fell from 2019 to 2021 by an average of 12.8 percentage points in mathematics and 6.8 in English Language Arts (ELA) [@Jack_Oster_2023].
@@
 This dataset is a `.csv` version of `scores_lm_demographics.dta`, obtained from the replication package of “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2], published in the American Economic Association’s *AER: Insights* [@citeAEA].
-Data are obtained from the Departments of Education of the aforementioned 21 US states, each of whom collect data from constituent schools, school boards and school authorities [@DeptsEd].
+Data are obtained from the Departments of Education for the 21 major American states, being Arkansas (AR), Colorado (CO), Connecticut (CT), Georgia (GA), Idaho (ID), Kansas (KS), Louisiana (LA), Massachusetts (MA), Minnesota (MN), Mississippi (MS), Missouri (MO), New Hampshire (NH), Ohio (OH), Pennsylvania (PA), Rhode Island (RI), South Carolina (SC), South Dakota (SD), Virginia (VA), Wisconsin (WI), West Virginia (WV) and Wyoming (WY).
+Each state collects data from constituent schools, school boards and school authorities [@DeptsEd].
 The dataset contains extensive information on school districts across these 21 states, including shares of students by race, shares of schooling done in-person, and changes in average test scores in both Mathematics and ELA from the previous year across the years 2018-2019 and 2021-2022.

### 2024-02-15 paper/paper.qmd
Updated Discussion

@@
 
+Looking at @fig-race alongside @fig-mathscoresrace and @fig-elascoresrace provides insights into the impacts of virtual schooling.
+@fig-race demonstrated that districts with higher shares of Black and higher shares of Hispanic students spent more days in virtual schooling as opposed to states with lower shares of these two races.
+Whilst @fig-mathscoresrace and @fig-elascoresrace show that every race as a whole had lower pass rates in Spring 2021, the difference in pass rates amongst the different races has not significantly changed.
+This could be evidence that higher rates of virtual schooling did not have a negative impact on test scores, which would indicate that the decline in test scores seen in Spring 2021 was a result of other factors.
+However, it is important to note that, whilst both @fig-race and @fig-mathscoresrace and @fig-elascoresrace classify districts as being “High” or “Low” based on the shares they comprise of each respective race, Figure \ref{fig-race}’s dataset included data on 48 states, whereas @fig-mathscoresrace and @fig-elascoresrace only had data on 21 states.
+Moreover, @fig-mathscoresrace and @fig-elascoresrace weighted their results by the total district enrollment.
+This difference in methodology limits the ability to compare the results represented in the figures.
+
 Having replicated their work, we now turn to examine its relevance to the Netherlands.

### 2024-02-15 paper/paper.qmd
Update DOI of SSRP provided by Berkeley

@@
 In studying the scope of school closures across the United States (US), they reported that the country experienced, on average, one of the highest number of days of school closed between January 2020 to December 2021 worldwide [@Jack_Oster_2023].
-Jack and Oster [-@Jack_Oster_2023] also found that the duration of school closures varies with local demographic characteristics, with more disadvantaged districts facing more prolonged closures.They found considerable declines in test scores during the 2020-2021 academic year, with declines larger in school districts with less in-person instruction.
+Jack and Oster [-@Jack_Oster_2023] also found that the duration of school closures varies with local demographic characteristics, with more disadvantaged districts facing more prolonged closures.
+The study population is primarily grades 3 to 8 American students from 21 US states.
+The estimate which we intend to replicate is the impact of the pandemic on academic performance of these students on standardised assessments.
+Their findings suggest that considerable declines in test scores occurred during the 2020-2021 academic year, with declines larger in school districts with less in-person instruction.
 On average, pass rates fell from 2019 to 2021 by an average of 12.8 percentage points in mathematics and 6.8 in English Language Arts (ELA) [@Jack_Oster_2023].

### 2024-02-15 scripts/03-test_data.R
Finished Testing Data

@@ -40,12 +40,11 @@ cleaned_region_data$covid_score |> class() == "numeric"
 
 ##Check the minimum number is equal, or greater than, 0 ##
 #Based on: https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html#simulate
-broadband_data$`COUNTY ID` |> min() >= 0
+final_broadband_data$`BROADBAND USAGE` |> min() >= 0
 
 ##Check the class of the column is numeric##
-broadband_data$`COUNTY ID` |> class() == "numeric"
-race_data$enrollment |> class() == "numeric"
-
+final_broadband_data$QUANTILE_LABEL |> class() == "character"
+final_broadband_data$`BROADBAND USAGE` |> "numeric"
 
 #### TESTING DATA FOR FIGURES ON TEST SCORES ####
 # Check that there are exactly 21 unique states to which a school district can belong

### 2024-02-15 paper/paper.qmd
Added subtitle

@@
 ---
-title: "Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students: A replication analysis using data from the United States and a case study on the Netherlands"
+title: "Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students"
+subtitle: "A replication analysis using data from the United States and a case study on the Netherlands"
 author: "Krishiv Jain, Julia Kim, Abbass Sleiman"

### 2024-02-15 paper/paper.qmd
Amend the discussion and add in a subtitle

@@
 As noted by Jack and Oster [-@Jack_Oster_2023], it can be seen that the equity impacts are two-fold.
-First, schools (and students) of more vulnerable racial backgrounds -- especially, Black and Hispanic -- are less likely to have access to in-person instruction.
-Second, for such groups, the consequences of a lack of in-person instruction on academic performance are more severe.
+First, as shown in @fig-race, schools (and students) of more vulnerable racial backgrounds -- especially, Black and Hispanic -- are less likely to have access to in-person instruction.
+Second, as shown in @fig-mathscoresrace and @fig-elascoresrace, for such groups, the consequences of a lack of in-person instruction on academic performance are more severe.
+
 This may be due to a smaller investment by such schools in effective remote learning programs or due to the challenges disadvantages students face at home, such as less reliable Internet connection or fewer community resources.
@@
 This exacerbates the already large inequality gap in educational outcomes.
-
-Looking at @fig-race alongside @fig-mathscoresrace and @fig-elascoresrace provides insights into the impacts of virtual schooling.
-@fig-race demonstrated that districts with higher shares of Black and higher shares of Hispanic students spent more days in virtual schooling as opposed to states with lower shares of these two races.
-Whilst @fig-mathscoresrace and @fig-elascoresrace show that every race as a whole had lower pass rates in Spring 2021, the difference in pass rates amongst the different races has not significantly changed.
-This could be evidence that higher rates of virtual schooling did not have a negative impact on test scores, which would indicate that the decline in test scores seen in Spring 2021 was a result of other factors.
-However, it is important to note that, whilst both @fig-race and @fig-mathscoresrace and @fig-elascoresrace classify districts as being “High” or “Low” based on the shares they comprise of each respective race, Figure \ref{fig-race}’s dataset included data on 48 states, whereas @fig-mathscoresrace and @fig-elascoresrace only had data on 21 states.
-Moreover, @fig-mathscoresrace and @fig-elascoresrace weighted their results by the total district enrollment.
-This difference in methodology limits the ability to compare the results represented in the figures.
 
@@
 This considerable difficulty of separating the effect of school closures from other pandemic-related stressors may bias the results and so affect their validity.
-One way in which we have helped disentangle these factors is to stratify the test assessments data by race, ELL and FRPL shares per district.
-By means of this "restriction" technique, we could compare test scores between more homogeneous demographic subgroups and better control for racial and demographic differences that may have impacted student learning outcomes.
+One way in which we have helped disentangle these factors is to stratify the test assessments data by race shares per district.
+By means of this "restriction" technique, we could compare test scores between more homogeneous demographic subgroups and better control for racial differences that may have impacted student learning outcomes.
 
@@
 
-Lastly, the state-level assessment data is obtained from only eleven states of the United States, for which district-level data is available.
+Another important limitation is the discrepancy in the state information provided by the datasets and in the methodology used to analyse them.
+In particular, whilst the datasets to create @fig-race contained data on all 48 states, @fig-mathscoresrace and  @fig-elascoresrace had data on only 21 states.
+Moreover, the results in @fig-mathscoresrace and @fig-elascoresrace were calculated by weighting the averages by total district enrollment, whereas no such weightage was performed for @fig-race.
+These such differences limit our ability to compare the results represented in the figures.
+
+Lastly, the state-level assessment data is obtained from 21 states of the United States, for which district-level data is available.
 This data set may not be representative of the academic performance of American students as a whole for two reasons.
@@
 Certainly, they cannot capture the ways in which students learned that were not directly given in the assessment.
-Second, the sample of eleven states may be too small to be generalisable.
+Second, Jack and Oster [@Jack_Oster_2023] gave no justification for their choice of these 21 states in particular, and it may be the case that the sample is not representative of the United States as a whole.
 Indeed, Parolin and Kee [-@parolin] showed that wide geographic disparities existed in school closures across the country: those concentrated on the West Coast faced declines of \>75% in-person visits to schools, whereas those in the Midwest faced declines of \<25%.
+It remains to examine whether these 21 states form a representative sample of the wide range of school closures across the country.
 Both of these factors put into question the validity and generalisability of the state-assessment data, and could present a valuable direction for future work.

### 2024-02-15 paper/paper.qmd

@@
 The data consists of broadband usage percentages at the US county-level in October 2020, obtained from anonymised data Microsoft collects.
-In less technical terms, this means that every time a device receives an update from or connects to a Microsoft service, Microsoft servers make an estimate of its throughput speed and determine its location at the zip-code level [@kahan2020usbroadband].
-After making such measurements, noise is added to data aggregations, preventing leakage about specific individuals in the dataset and ensuring differential privacy.
+According to Kahan [-@kahan2020usbroadband], in less technical terms, this means that every time a device receives an update from or connects to a Microsoft service, Microsoft servers make an estimate of its throughput speed and determine its location at the zip-code level.
+In using the Federal Communications Commission definition of broadband, being 25 megabits per second per download [@FCC], a count is then made of the number of devices that connect to the Internet at broadband speed per zip code.
+After making such measurements, noise is added to data aggregations using the SmartNoise platform, thereby preventing leakage about specific individuals in the dataset and ensuring differential privacy.
 
@@
 What is more, Jack et al.
-[-@Jack_Oster_2] standardised assessments data excludes information about the corresponding broadband usage and test scores of Asians by district.
-It instead includes data of the corresponding shares of ELL and FRPL students by district, two demographic characteristics we did not consider in our analysis.
+[-@Jack_Oster_2] standardised assessments data excludes information about the corresponding broadband usage and test scores of Asian students by district.
+It instead includes data of the corresponding shares of English Language Learners (ELL) and students eligible for Free and Reduced Price Lunch (FRPL) by district, two demographic characteristics we did not consider in our analysis.
 This discrepancy prevents us from telling a full story as to how the pass rates of schools located in districts with lower broadband usage and higher shares of Asian minorities, the former of which is known to face more days of school closed than the national average, were affected.
-We raise a question of whether the shares of FRPL students were a good estimator of the shares of students with low socioeconomic status.
+As an aside, we might also question whether the shares of FRPL students were a good estimator of the shares of students with low socioeconomic status in Jack et al.
+[-@Jack_Oster_2]'s paper.
 Though FRPL enrollment are widely used in education research as an indicator of student poverty, there is emerging literature that it serves as a poor proxy for poverty [@Fazlul2023].

### 2024-02-15 paper/paper.qmd
Add more about measurement of broadband

@@
 This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" GitHub Repository [@kahan2020usbroadband].
-The data consists of broadband usage percentages at the US county-level in October 2020, obtained from anonymised data Microsoft collects.
-According to Kahan [-@kahan2020usbroadband], in less technical terms, this means that every time a device receives an update from or connects to a Microsoft service, Microsoft servers make an estimate of its throughput speed and determine its location at the zip-code level.
+According to Kahan [-@kahan2020usbroadband], data consists of broadband usage percentages at the US county-level in October 2020, obtained from anonymised data Microsoft collects.
+In less technical terms, this means that every time a device receives an update from or connects to a Microsoft service, Microsoft servers make an estimate of its throughput speed and determine its location at the zip-code level.
 In using the Federal Communications Commission definition of broadband, being 25 megabits per second per download [@FCC], a count is then made of the number of devices that connect to the Internet at broadband speed per zip code.
-After making such measurements, noise is added to data aggregations using the SmartNoise platform, thereby preventing leakage about specific individuals in the dataset and ensuring differential privacy.
+After making such measurements, noise is added to data aggregations using the open-source SmartNoise platform, thereby preventing leakage about specific individuals in the dataset and ensuring differential privacy.
 

### 2024-02-15 paper/paper.qmd
Amended paper
Updated some of the information in the data section

@@
 To generate this graph, we once again employed the cleaned `scores_lm_demographics.csv` file as was used to generate @fig-mathscoresbyonline and @fig-elascoresbyonline.
-We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the two quantiles, "Low" and "High", for each of the three races relative to the average shares in each of the 21 states.
+We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the two quantiles, "Low" and "High", for each of the three races relative to the average shares across all school districts.
 From there, we grouped the data by year and quantile for each of the three races, then calculated the weighted average change in test pass rates for each subject and quantile, across all races and years.
@@
 white_share <- white_share |>
-  group_by(state) |>
   mutate(quantile = ntile(share_enroll_white, 2)) |>
@@
 black_share <- black_share |>
-  group_by(state) |>
   mutate(quantile = ntile(share_enroll_black, 2)) |>
@@
 hispanic_share <- hispanic_share |>
-  group_by(state) |>
   mutate(quantile = ntile(share_enroll_hispanic, 2)) |>

### 2024-02-15 paper/paper.qmd
Updated abstract
Made minor adjustment to the wording for clarity

@@
     abstract: "School closures due to the COVID-19 pandemic have raised significant concerns about the consequences on student learning and achievement gaps.
-This paper replicates a data analysis of the scope of school closures in the United States in the 2020-2021 school year, the inequitable distribution of such closures by demographic characteristics and the resultant declines in pass rates on standardised tests in mathematics and English Language Arts (ELA) of students in grades 3-8 across 21 states.
+This paper replicates a data analysis of the scope of school closures in the United States in the 2020-2021 school year, the inequitable distribution of such closures by demographic characteristics, and the resultant declines in pass rates on standardised tests in mathematics and English Language Arts (ELA) done by students in grades 3-8 across 21 states.
 We apply secondary research regarding the scope of school closures in the Netherlands in same year and the declines in national examination scores in reading, spelling and mathematics of Dutch students in grades 4-7.

### 2024-02-15 paper/paper.qmd
Add files via upload

@@
 For each district and for each of the years 2018, 2019 and 2020, it reports the total student enrollment, split by grade (ranging from Kindergarten to Grade 12), sex (Male and Female), and ethnic class (American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races).
-The data is collected via surveys and supplied by state agencies to NCES [@USDeptCommerce].
+Thanks to partnerships with state education authorities and organisations, NCES is authorised to collected data by conducting numerous surveys with public schools and local education agencies [@Encyclopedia_2024].
+Its National Forum on Education Statistics then collects, processes and reports elementary and local education statistics [@Encyclopedia_2024].
 
@@
 
-We extended Jack and Oster's research by also looking at the shares of White and Asian students.
+We extended Jack and Oster [-@Jack_Oster_2023]'s research by also looking at the shares of White and Asian students.
 We found that districts with "High" and "Low" shares of White students had an average of 55 and 23 days in virtual schooling, respectively.

### 2024-02-15 scripts/01-download_data.R
Updated preamble
Added additional information regarding the pre-requisites required to run the code

@@ -4,7 +4,10 @@
 # Date: 14 February 2024
 # Contact: krishiv.jain@mail.utoronto.ca, abbass.sleiman@mail.utoronto.ca, juliaym.kim@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Follow instructions in README to download data on race enrollment
+# Pre-requisites: In order to run this code, scores_lm_demographics.dta must be downloaded in advance.
+# This can be done either by downloading the file directly from data/raw_data in this paper's repository,
+# or by downloading directly from Jack and Oster's replication package at 
+# https://www.openicpsr.org/openicpsr/project/193523/version/V1/view
 
 
 #### Workspace setup ####

### 2024-02-15 paper/paper.qmd
fix minor spelling error

@@
 For each district and for each of the years 2018, 2019 and 2020, it reports the total student enrollment, split by grade (ranging from Kindergarten to Grade 12), sex (Male and Female), and ethnic class (American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races).
-Thanks to partnerships with state education authorities and organisations, NCES is authorised to collected data by conducting numerous surveys with public schools and local education agencies [@Encyclopedia_2024].
+Thanks to partnerships with state education authorities and organisations, NCES is authorised to collect such data by conducting numerous surveys with public schools and local education agencies [@Encyclopedia_2024].
 Its National Forum on Education Statistics then collects, processes and reports elementary and local education statistics [@Encyclopedia_2024].
@@
 Data are obtained from the Departments of Education for the 21 major American states, being Arkansas (AR), Colorado (CO), Connecticut (CT), Georgia (GA), Idaho (ID), Kansas (KS), Louisiana (LA), Massachusetts (MA), Minnesota (MN), Mississippi (MS), Missouri (MO), New Hampshire (NH), Ohio (OH), Pennsylvania (PA), Rhode Island (RI), South Carolina (SC), South Dakota (SD), Virginia (VA), Wisconsin (WI), West Virginia (WV) and Wyoming (WY).
-Each state collects data from constituent schools, school boards and school authorities [@DeptsEd].
+Each state collects data via surveys from constituent schools, school boards and school authorities [@DeptsEd].
 The dataset contains extensive information on school districts across these 21 states, including shares of students by race, shares of schooling done in-person, and changes in average test scores in both Mathematics and ELA from the previous year across the years 2018-2019 and 2021-2022.

### 2024-02-15 scripts/99-replications.R
Updated preamble
Added additional information regarding the purpose of this script.

@@ -1,8 +1,9 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
+# Purpose: Replicated graphs from Jack and Oster's paper titled "COVID-19, School Closures, and
+# Outcomes" found at https://www.aeaweb.org/articles?id=10.1257/jep.37.4.51. In particular, we aimed
+# to replicate Figure 1, Figure 2, and Figure 4, as denoted in their paper.
 # Author: Krishiv Jain, Julia Kim, Abbass Sleiman
 # Date: 12 February 2024 
-# Contact: 
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-02-15 paper/paper.qmd
Add info about measurement to data section
Add info about measurement to data, amended smartnoise citation

@@
 For each district, it provides information as to the county and state to which they belong, and their NCES district ID.
+Note that unique NCES ID numbers are automatically assigned to districts upon being reported to the US Department of Education by their state education agency via the platform EDFacts [@citeraw2].
 
@@
 In using the Federal Communications Commission definition of broadband, being 25 megabits per second per download [@FCC], a count is then made of the number of devices that connect to the Internet at broadband speed per zip code.
-After making such measurements, noise is added to data aggregations using the open-source SmartNoise platform, thereby preventing leakage about specific individuals in the dataset and ensuring differential privacy.
+After making such measurements, noise is added to data aggregations using the open-source SmartNoise platform, thereby preventing leakage about specific individuals in the dataset and ensuring differential privacy [@SmartNoise_2023].
 

### 2024-02-15 paper/paper.qmd
Updated quarto file
Added additional information in the results section

@@
 Thus, countries with the longest closures spent more than twice the amount of time in virtual schooling compared to those with the shortest closures.
+
+One should note that @fig-daysclosed differs slightly from Jack and Oster's [@Jack_Oster_2023] with regards to the values for Europe and Central Asia, and East Asia and Pacific.
+Upon further analysis, we found that, unlike in our analysis, Jack and Oster omit the data from Taiwan when generating their figure, hence why their value for East Asia and Pacific, 342, differs from our value of 334.
+They do not cite a reason for this in their paper, however, hence why we have decided to keep in as part of our analysis to gain a more thorough picture given the data at our disposal.
+As for the slight variance between our calculated value for Europe and Central Asia and Jack and Oster's, 308 and 309 respectively, we found that this disparity could not be attributed to any one particular reason.
+When examining the raw data directly, we found that the value calculated for the average number of days closed for nations in Europe and Central Asia agreed with our value of 308, and thus the reason for the disparity is unclear.
 

### 2024-02-15 paper/paper.qmd
Update SSRP DOI links.

--- 2024-02-15 paper/paper.qmd
@@
 author: "Krishiv Jain, Julia Kim, Abbass Sleiman"
-thanks: "Code and data are available at: [https://github.com/AbbassSleiman/COVID19-US-School-Closures](https://github.com/AbbassSleiman/COVID19-US-School-Closures); Replication on Social Science Reproduction platform available at: [https://doi.org/10.48152/ssrp-9vc2-gp37](https://doi.org/10.48152/ssrp-9vc2-gp37)"
+thanks: "Code and data are available at: [https://github.com/AbbassSleiman/COVID19-US-School-Closures](https://github.com/AbbassSleiman/COVID19-US-School-Closures); Minimal and Full Replication on Social Science Reproduction platform available at [https://doi.org/10.48152/ssrp-qvfh-0r62](https://doi.org/10.48152/ssrp-qvfh-0r62) and  [https://doi.org/10.48152/ssrp-9vc2-gp37](https://doi.org/10.48152/ssrp-9vc2-gp37), respectively."
 date: "February 15, 2024"

### 2024-02-15 paper/paper.qmd
fix doi ssrp links

--- 2024-02-15 paper/paper.qmd
@@
 author: "Krishiv Jain, Julia Kim, Abbass Sleiman"
-thanks: "Code and data are available at: [https://github.com/AbbassSleiman/COVID19-US-School-Closures](https://github.com/AbbassSleiman/COVID19-US-School-Closures); Replication on Social Science Reproduction platform available at: [https://doi.org/10.48152/ssrp-9vc2-gp37](https://doi.org/10.48152/ssrp-9vc2-gp37)"
+thanks: "Code and data are available at: [https://github.com/AbbassSleiman/COVID19-US-School-Closures](https://github.com/AbbassSleiman/COVID19-US-School-Closures); Minimal and Full Replication on Social Science Reproduction platform available at [https://doi.org/10.48152/ssrp-9vc2-gp37](https://doi.org/10.48152/ssrp-9vc2-gp37) and  [https://doi.org/10.48152/ssrp-qvfh-0r62](https://doi.org/10.48152/ssrp-qvfh-0r62), respectively."
 date: "February 15, 2024"

### 2024-02-15 paper/paper.qmd
Final Edits

@@
 
+Looking at @fig-race alongside @fig-mathscoresrace and @fig-elascoresrace provides insights into the impacts of virtual schooling.
 As noted by Jack and Oster [-@Jack_Oster_2023], it can be seen that the equity impacts are two-fold.
@@
 Second, as shown in @fig-mathscoresrace and @fig-elascoresrace, for such groups, the consequences of a lack of in-person instruction on academic performance are more severe.
+We can see how the the districts with a higher share of black and Hispanic students had more virtual days, and also had large decrease in their test scores relative to the districts with lower shares.
+On the other hand, the districts with a high share of white students had less virtual school days, and had a smaller decrease in their pass rates relative to the districts with lower shares.
 

### 2024-02-18 paper/paper.qmd
Fixed Typos

@@
 Consistent with Jack and Oster [-@Jack_Oster_2023], our analysis shows a significant decline in pass rates from the 2018-2019 to the 2020-2021 school year.
-We see that in Spring 2021, there is a clear fall in the pass rates overall in both subject areas from 2019 (note that there were no standardised assessmments in 2020), though this fall is much more pronounced in Math than ELA (-12.8 percentage points compared to the -6.8 percentage points, respectively).
+We see that in Spring 2021, there is a clear fall in the pass rates overall in both subject areas from 2019 (note that there were no standardised assessments in 2020), though this fall is much more pronounced in Math than ELA (-12.8 percentage points compared to the -6.8 percentage points, respectively).
 The discrepancy between these two subjects is consistent with much of the current economic literature, which shows mathematics scores to be more sensitive to schooling differences [@betts2011effect; @angrist].
@@
 
-In line with some of our previous discussions, we looked towards building upoing Jack and Oster's work by examining the potential systematic disparities between relative student racial compositions and the average percentage point change in test pass rates.
+In line with some of our previous discussions, we looked towards building upon Jack and Oster's work by examining the potential systematic disparities between relative student racial compositions and the average percentage point change in test pass rates.
 In particular, both @fig-mathscoresrace and @fig-elascoresrace provide information on the changes in test pass rates across the three years of interest from the year prior as a function of the race quantiles that each schooling district belonged to for each of the share of White, Black, and Hispanic students.
@@
 (1) Between January 2020 and December 2021, the United States experienced the second-highest number of days of school closed worldwide, with an average of 667 days.
-In fact, it falls second only to Azerjiban, which recorded an average of 669 days.
+In fact, it falls second only to Azerbaijan, which recorded an average of 669 days.
 
@@
 Second, as shown in @fig-mathscoresrace and @fig-elascoresrace, for such groups, the consequences of a lack of in-person instruction on academic performance are more severe.
-We can see how the the districts with a higher share of black and Hispanic students had more virtual days, and also had large decrease in their test scores relative to the districts with lower shares.
+We can see how the districts with a higher share of black and Hispanic students had more virtual days, and also had large decrease in their test scores relative to the districts with lower shares.
 On the other hand, the districts with a high share of white students had less virtual school days, and had a smaller decrease in their pass rates relative to the districts with lower shares.
